### 2021-02-02 ms.Rmd
Sorting out references and markdown structure

---
title: "Methods and Results"
author: 
date: "`r Sys.Date()`"
bibliography: refs.bib
csl: science.csl
output: 
  bookdown::html_document2:
    code_folding: hide
    number_sections: no
    toc: yes
    toc_depth: 6
    toc_float: yes
    bibliography: refs.bib
  bookdown::word_document2:
    toc: no
    toc_depth: 6
    number_sections: true
    reference_docx: template.docx
editor_options: 
  chunk_output_type: console
---

### 2021-02-02 ms.Rmd
Setting up

@@
       toc_float: yes
-    bibliography: refs.bib
     bookdown::word_document2:

### 2021-02-02 R/func.R
Added a species list in data, a new function for replacing species names, and a phylogeny script to begein building the phylogeny for the dataset. Added project file for rendering as it's much easier in RStudio - often

@@ -1,0 +1,17 @@
+
+##########################################
+# Author: D.W.A. Noble
+# Email: daniel.noble@anu.edu.au
+# Functions used through scripts
+##########################################
+
+#' @title replace_names
+#' @description Function aids in string matching and replacement. In other words, when you have a phylogeny you often need to replace synonymns. This function helps you do this quickly on a dataset that has repeated names. 
+#' @param string This is the main character vector that you wish to substitute values. (i.e., the main column in data)
+#' @param match This is a list of unique values contained within your 'string' column of your data frame.
+#' @param replace These are the replacement names for the unique values within your column. 'match' and 'replace' should be the same lengths given this maps 1:1 the name in the data to the new name you want to replace it with.
+
+replace_names <- function(string, match, replace){
+	string_replaced <-replace[match(string, match)]
+	return(string_replaced)
+}

### 2021-02-02 R/phylogeny.R

@@ -1,0 +1,41 @@
+
+##########################################################
+# Author: D.W.A Noble
+# Purpose: Script for building and finding taxa in the
+# dataset to create a phylogenetic tree for the 
+# phylogenetic covariance matrix
+##########################################################
+
+# Libraries 
+	pacman::p_load(rotl, tidyverse, ape, phytools, readxl)
+
+# Datasets; it's in excel and has two sheets, so will use readxl package. We need sheet one
+
+	data <- read_excel("./data/Data_MA.xlsx", sheet = 1)
+
+# Extract the species list, clear whitespace, have a look at unique names
+
+	spp <- data %>% pull(species) %>% trimws()
+
+# Get some summary stats:
+	# How many species?
+		length(unique(spp)) #38
+
+	# What are the unique species; note that Calopteryx doesn't have a species binomial classification
+		species_names <- unique(spp)
+
+# Lets use ROTL to find taxa, and possible synonymns
+		matching <- tnrs_match_names(species) 
+		spp_match <- matching %>% pull(unique_name)
+
+# Now that we have the list of most up-to-date names from ROTL, we can do a few things to get a phylogeny. First, export list for TimeTree
+		write(spp_match, "./phylogeny/spp_list")
+
+# Now grab the tree based on taxonomy and molecular data
+		tree <-  tol_induced_subtree(matching$ott_id)
+		plot(tree, cex = 0.8)
+
+# Replace the species names in data with the matched names in ROTL so that when a covariance matrix is made the node names match exactly to the names in data. 
+data <- data %>%
+			mutate(species=replace_names(species, species_names, spp_match))
+

### 2021-02-03 R/phylogeny.R
Added tree file, cleaned up and ready; matches names in data. New data file export in csv

@@ -39,3 +39,14 @@
 data <- data %>%
 			mutate(species=replace_names(species, species_names, spp_match))
 
+###########################################################
+# Branch lengths and VCV matrix
+###########################################################
+# Create branch lengths for tree using Grafen's method
+tree_bl <- compute.brlen(tree, method = "Grafen", power = 1)
+
+# Fix tip labels
+tree_bl$tip.label <- gsub("_", " ", gsub("_ott.+", "", tree_bl$tip.label))
+
+write.tree(tree_bl, "./phylogeny/tree")
+write.csv(data, "./data/meta_data.csv")

### 2021-02-27 ms.Rmd
New style file in yaml header

@@
   bibliography: refs.bib
-  csl: science.csl
+  csl: pnas.csl
   output: 

### 2021-03-04 R/phylogeny.R
Added some small code updates and phylogeny

@@ -8,6 +8,7 @@
 
 # Libraries 
 	pacman::p_load(rotl, tidyverse, ape, phytools, readxl)
+	source("./R/func.R")
 
 # Datasets; it's in excel and has two sheets, so will use readxl package. We need sheet one
 
@@ -25,7 +26,7 @@
 		species_names <- unique(spp)
 
 # Lets use ROTL to find taxa, and possible synonymns
-		matching <- tnrs_match_names(species) 
+		 matching <- tnrs_match_names(species_names)  
 		spp_match <- matching %>% pull(unique_name)
 
 # Now that we have the list of most up-to-date names from ROTL, we can do a few things to get a phylogeny. First, export list for TimeTree

### 2021-03-04 ms.Rmd
data_prep script added and beginning results

@@
 ---
+
+```{r loaddata, echo = FALSE, results = "hide"}
+  data <- read.csv("./data/meta_data.csv")
+
+  # Summary statistics for the results
+  inverts <- data %>% 
+             mutate(insect = ifelse(class %in% c("Insecta", "Gastropoda", "Malacostraca", "Arachnida", "Clitellata (Phylum Annelida)",  "Secernentea (Phylum Nematoda)"), 1,0))
+```
+
+# Results
+
+Overall, we collected effect sizes for a total of `r length(unique(data$species))` species from `r length(unique(data$study))` studies.
+Unsurprisingly, invertebrates (classes: Insecta, Gastropoda, Malacostraca, Arachnida, Clitellata and Secernentea) made up most of the data (`r (table(inverts$insect)[2] / sum(table(inverts$insect)))*100`%), reflecting the fact that overt sexual conflict is more common in these groups.

### 2021-03-04 R/data_prep.R

@@ -1,0 +1,17 @@
+##########################################################
+# Author: D.W.A Noble
+# Purpose: Script for cleaning and preping data
+##########################################################
+
+# Load data written from phylogeny script. 
+	data <- read.csv("./data/meta_data.csv")
+	str(data)
+
+# Convert all se to SD
+
+	data <- data %>%
+			mutate(sd_T = ifelse(Err_T_Type == "se", Err_T*sqrt(N_T), Err_T),
+				   sd_C = ifelse(Err_C_Type == "se", Err_C*sqrt(N_C), Err_C))
+
+# Explore mean and variance relationships
+	plot(log(X_T) ~ log(sd_T), data = data)

### 2021-03-04 R/phylogeny.R
Fixed code to remove row.names write

@@ -50,4 +50,4 @@ tree_bl <- compute.brlen(tree, method = "Grafen", power = 1)
 tree_bl$tip.label <- gsub("_", " ", gsub("_ott.+", "", tree_bl$tip.label))
 
 write.tree(tree_bl, "./phylogeny/tree")
-write.csv(data, "./data/meta_data.csv")
+write.csv(data, "./data/meta_data.csv", row.names = FALSE)

### 2021-03-23 R/data_prep.R
checking main excel data file to go through all notes listed and to have a check of studies and data pulled from these studies. Adding some code to explore data further. Also added code to load packages"

@@ -3,6 +3,10 @@
 # Purpose: Script for cleaning and preping data
 ##########################################################
 
+# Libraries
+pacman::p_load(tidyverse, metafor, brms)
+
+
 # Load data written from phylogeny script. 
 	data <- read.csv("./data/meta_data.csv")
 	str(data)
@@ -11,7 +15,15 @@
 
 	data <- data %>%
 			mutate(sd_T = ifelse(Err_T_Type == "se", Err_T*sqrt(N_T), Err_T),
-				   sd_C = ifelse(Err_C_Type == "se", Err_C*sqrt(N_C), Err_C))
+				   sd_C = ifelse(Err_C_Type == "se", Err_C*sqrt(N_C), Err_C),
+				   obs  = 1:n())
 
 # Explore mean and variance relationships
+	# Treatment groups		
 	plot(log(X_T) ~ log(sd_T), data = data)
+
+	# Control: Seems like a clear outlier at row 1; checked and looks to be correct. 
+	plot(log(X_C) ~ log(sd_C), data = data)
+	with(data, text(obs, y = log(X_C)+0.5, x=log(sd_C)+0.05, cex = 0.85)) 
+
+# 

### 2021-03-23 R/data_prep.R
Cleaning data, checking and exploring

@@ -6,13 +6,11 @@
 # Libraries
 pacman::p_load(tidyverse, metafor, brms)
 
-
 # Load data written from phylogeny script. 
 	data <- read.csv("./data/meta_data.csv")
 	str(data)
 
 # Convert all se to SD
-
 	data <- data %>%
 			mutate(sd_T = ifelse(Err_T_Type == "se", Err_T*sqrt(N_T), Err_T),
 				   sd_C = ifelse(Err_C_Type == "se", Err_C*sqrt(N_C), Err_C),
@@ -26,4 +24,29 @@ pacman::p_load(tidyverse, metafor, brms)
 	plot(log(X_C) ~ log(sd_C), data = data)
 	with(data, text(obs, y = log(X_C)+0.5, x=log(sd_C)+0.05, cex = 0.85)) 
 
-# 
+# Explore a bit more of how much data we have across various moderators
+	data %>% 
+	select_if(is.factor) %>% 
+	select(-c(notes, Dependency_decisions, journal, pg, author, estimated.increase.in.harm, Err_C_Type, Err_T_Type, C_flipped, source)) %>% 
+	glimpse %>% summary(.)
+
+# From this it is quite clear that there is not too much use in Parental Care as most don't have care. Most of the data is a direct measure of fitness, which is good. Most data are from oviparous, but sensible split possibly.
+
+# Explore species level data
+	spp_data <- data.frame(data %>%
+	group_by(species) %>% 
+	summarise(Parental.care = unique(Parental.care),
+			  Gestation     = unique(Gestation),
+			  Sperm.compet  = unique(Sperm.compet),
+			  SCR.SCI 		= unique(SCR.SCI),
+			  treatment     = unique(treatment)) )
+
+	spp_data %>% summary()
+
+
+# Generate Effect Sizes - Going to use SMDH (Hedges g with heteroscedasticity correction)
+data <- escalc(m1i = X_C, sd1i =sd_C, n1i = N_C, m2i= X_T, sd2i= sd_T, n2i= N_T, data = data, append = TRUE, measure = "SMDH", var.names=c("SMDH","v_SMDHq"))
+
+# Clean data up a bit. We don't need all columns
+data <- data %>% 
[…]

### 2021-03-23 R/data_prep.R
Fixing up issues in raw data excel file. Renerated phylogeny, species lis and cleaned datafile

@@ -4,7 +4,7 @@
 ##########################################################
 
 # Libraries
-pacman::p_load(tidyverse, metafor, brms)
+pacman::p_load(tidyverse, metafor, brms, latex2exp)
 
 # Load data written from phylogeny script. 
 	data <- read.csv("./data/meta_data.csv")
@@ -50,3 +50,13 @@ data <- escalc(m1i = X_C, sd1i =sd_C, n1i = N_C, m2i= X_T, sd2i= sd_T, n2i= N_T,
 # Clean data up a bit. We don't need all columns
 data <- data %>% 
 select(study, author, year, class, order, family, genus, species, variable, fitness.estimate, treatment, estimated.increase.in.harm, X_C, sd_C, N_C, X_T, sd_T, N_T, SMDH, v_SMDHq, SME_index, Male.measure, Female.measure, SCR.SCI, Sperm.compet, Harm_type, Parental.care , Gestation, depend, shared.control, source)
+
+# Have a look. Does look like clear evidence for publication bias though. 
+ggplot(data, aes(x = SMDH, y = 1 / sqrt(v_SMDHq), xmin = -10, xmax = 28)) +
+geom_point() +
+labs(x = "SMDH", y = TeX("Precision ($\\frac{1}{\\sqrt{v}}$)")) 
+
+# Find outlier data.There is a clear outlier, which is study 047. I've got to the original paper and noticed data was extracted from boxplot. SD values were very small for the mean data, suggesting data entry. I re-extracted from raw data which was also presented and SD's are much more sensible and way different from original extraction and conversion from box plot.
+data %>% filter(SMDH >=10)
+
+

### 2021-03-23 R/phylogeny.R

@@ -20,7 +20,7 @@
 
 # Get some summary stats:
 	# How many species?
-		length(unique(spp)) #38
+		length(unique(spp)) #33
 
 	# What are the unique species; note that Calopteryx doesn't have a species binomial classification
 		species_names <- unique(spp)

### 2021-03-24 R/data_prep.R
Data exploration

@@ -43,7 +43,6 @@ pacman::p_load(tidyverse, metafor, brms, latex2exp)
 
 	spp_data %>% summary()
 
-
 # Generate Effect Sizes - Going to use SMDH (Hedges g with heteroscedasticity correction)
 data <- escalc(m1i = X_C, sd1i =sd_C, n1i = N_C, m2i= X_T, sd2i= sd_T, n2i= N_T, data = data, append = TRUE, measure = "SMDH", var.names=c("SMDH","v_SMDHq"))
 
@@ -51,12 +50,48 @@ data <- escalc(m1i = X_C, sd1i =sd_C, n1i = N_C, m2i= X_T, sd2i= sd_T, n2i= N_T,
 data <- data %>% 
 select(study, author, year, class, order, family, genus, species, variable, fitness.estimate, treatment, estimated.increase.in.harm, X_C, sd_C, N_C, X_T, sd_T, N_T, SMDH, v_SMDHq, SME_index, Male.measure, Female.measure, SCR.SCI, Sperm.compet, Harm_type, Parental.care , Gestation, depend, shared.control, source)
 
-# Have a look. Does look like clear evidence for publication bias though. 
-ggplot(data, aes(x = SMDH, y = 1 / sqrt(v_SMDHq), xmin = -10, xmax = 28)) +
-geom_point() +
-labs(x = "SMDH", y = TeX("Precision ($\\frac{1}{\\sqrt{v}}$)")) 
+# Have a look. Does look like clear evidence for publication bias. 
+ggplot(data, aes(x = SMDH, y = 1 / sqrt(v_SMDHq), xmin = -6, xmax = 6)) +
+geom_point(aes(colour = class)) +
+labs(x = "SMDH", 
+	 y = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$"),
+	 colour = "Class") +
+scale_color_grey() + 
+#scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9")) + 
+theme_bw() 
 
 # Find outlier data.There is a clear outlier, which is study 047. I've got to the original paper and noticed data was extracted from boxplot. SD values were very small for the mean data, suggesting data entry. I re-extracted from raw data which was also presented and SD's are much more sensible and way different from original extraction and conversion from box plot.
 data %>% filter(SMDH >=10)
[…]

### 2021-03-24 R/phylogeny.R

@@ -20,7 +20,7 @@
 
 # Get some summary stats:
 	# How many species?
-		length(unique(spp)) #33
+		length(unique(spp)) #32
 
 	# What are the unique species; note that Calopteryx doesn't have a species binomial classification
 		species_names <- unique(spp)

### 2021-03-27 ms.Rmd
checking main excel data file to go through all notes listed and to have a check of studies and data pulled from these studies. Adding some code to explore data further. Also added code to load packages"
Updated phylogeny, data prep and fit some preliminary models

--- 2021-02-27 ms.Rmd
@@
 ---
+
+```{r loadpackages, echo = FALSE, results = "hide"}
+  pacman::p_load(tidyverse, metafor, brms)
+
+```
+```{r loaddata, echo = FALSE, results = "hide"}
+  # Tree
+      data <- read.csv("./data/meta_data.csv")
+      data <- data %>% 
+              mutate(species2 = species)
+
+  # Bring in and prune tree
+       tree <- read.tree("./phylogeny/tree")
+       tree$tip.label <- gsub("_", " ", tree$tip.label)
+  phylogeny <- vcv(tree, corr=TRUE)
+
+  # Summary statistics for the results
+  inverts <- data %>% 
+             mutate(insect = ifelse(class %in% c("Insecta", "Gastropoda", "Malacostraca", "Arachnida", "Clitellata (Phylum Annelida)",  "Secernentea (Phylum Nematoda)"), 1,0))
+
+model <- rma.mv(SMDH ~ 1, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|variable, ~1|species), test = "t", data = data)
+
+model <- rma.mv(lnRR ~ 1, V = data$v_lnRR, random = list(~1|study, ~1|obs, ~1|variable, ~1|species), test = "t", data = data)
+
+model <- rma.mv(SMDH ~ 1, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|variable, ~1|species, ~1|species2), R = list(species = phylogeny), test = "t", data = data)
+
+model <- rma.mv(SMDH ~ SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
+
+model <- rma.mv(lnRR ~ SSD_lnRR, V =  data$v_lnRR, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
+
+model <- rma.mv(SMDH ~ Harm_type-1, V = data$v_SMDH, random = list(~1|study, ~1|species, ~1|obs), R = list(species = phylogeny), test = "t", data = data)
+robust(model, cluster = data$study)
+
+model <- rma.mv(lnRR ~ Harm_type, V = data$v_lnRR, random = list(~1|study, ~1|species, ~1|obs), R = list(species = phylogeny), test = "t", data = data)
+robust(model, cluster = data$study)
+
+model <- rma.mv(SMDH ~ Harm_type + SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
+robust(model, cluster = data$study)
+
+```
+
+# Results
+
+Overall, we collected effect sizes for a total of `r length(unique(data$species))` species from `r length(unique(data$study))` studies.
+Unsurprisingly, invertebrates (classes: Insecta, Gastropoda, Malacostraca, Arachnida, Clitellata and Secernentea) made up most of the data (`r (table(inverts$insect)[2] / sum(table(inverts$insect)))*100`%).

### 2021-03-27 R/data_prep.R

@@ -30,8 +30,11 @@ pacman::p_load(tidyverse, metafor, brms, latex2exp)
 	select(-c(notes, Dependency_decisions, journal, pg, author, estimated.increase.in.harm, Err_C_Type, Err_T_Type, C_flipped, source)) %>% 
 	glimpse %>% summary(.)
 
-# From this it is quite clear that there is not too much use in Parental Care as most don't have care. Most of the data is a direct measure of fitness, which is good. Most data are from oviparous, but sensible split possibly.
+# From this it is quite clear that there is not too much use in Parental Care as most don't have care. Most of the data is a direct measure of fitness, which is good. Most data are from oviparous, but sensible split possibly. We can actually reclassify ovoviviparous to oviparous
 
+	data <- data %>%
+			mutate(Gestation = ifelse(Gestation == "ovoviviparous", "oviparous", as.character(Gestation)))
+	table(data$Gestation)
 # Explore species level data
 	spp_data <- data.frame(data %>%
 	group_by(species) %>% 
@@ -44,14 +47,15 @@ pacman::p_load(tidyverse, metafor, brms, latex2exp)
 	spp_data %>% summary()
 
 # Generate Effect Sizes - Going to use SMDH (Hedges g with heteroscedasticity correction)
-data <- escalc(m1i = X_C, sd1i =sd_C, n1i = N_C, m2i= X_T, sd2i= sd_T, n2i= N_T, data = data, append = TRUE, measure = "SMDH", var.names=c("SMDH","v_SMDHq"))
+data <- escalc(m1i = X_C, sd1i =sd_C, n1i = N_C, m2i= X_T, sd2i= sd_T, n2i= N_T, data = data, append = TRUE, measure = "SMDH", var.names=c("SMDH","v_SMDH"))
+data <- escalc(m1i = X_C, sd1i =sd_C, n1i = N_C, m2i= X_T, sd2i= sd_T, n2i= N_T, data = data, append = TRUE, measure = "ROM", var.names=c("lnRR","v_lnRR"))
 
 # Clean data up a bit. We don't need all columns
 data <- data %>% 
[…]

### 2021-03-27 R/phylogeny.R

@@ -49,5 +49,6 @@ tree_bl <- compute.brlen(tree, method = "Grafen", power = 1)
 # Fix tip labels
 tree_bl$tip.label <- gsub("_", " ", gsub("_ott.+", "", tree_bl$tip.label))
 
+plot(tree_bl, use.edge = TRUE)
 write.tree(tree_bl, "./phylogeny/tree")
 write.csv(data, "./data/meta_data.csv", row.names = FALSE)

### 2021-03-27 ms.Rmd
UPdated some results

@@
 
+  parity <- data %>% group_by(species) %>% summarise(parity = unique(Gestation)) %>% group_by(parity) %>% summarise(n=n())
+
+# Models
   model <- rma.mv(SMDH ~ 1, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|variable, ~1|species), test = "t", data = data)
@@
 
+  model <- rma.mv(SMDH ~ Gestation + SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
+  robust(model, cluster = data$study)
+
+  # Note that for gestation, these data on viviparous species are restricted completely to fish only, and indirect measurements.
+So, confounded.
+It's hard to know what is the driving factor...could be parity mode, but could be also due to all being fish, or even just that they are indirect measures, also, only 7 studies.
+  model <- rma.mv(lnRR ~ Gestation - 1, V = data$v_lnRR, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
+  robust(model, cluster = data$study)
+
+## Have a look at SSD data in relation to the key moderators
+  ggplot(data, aes(y = SSD_lnRR, x = Harm_type)) + geom_violin() + geom_point()
+  ggplot(data, aes(y = SSD_lnRR, x = Gestation)) + geom_violin() + geom_point()
+
 ```
@@
 Unsurprisingly, invertebrates (classes: Insecta, Gastropoda, Malacostraca, Arachnida, Clitellata and Secernentea) made up most of the data (`r (table(inverts$insect)[2] / sum(table(inverts$insect)))*100`%).
+We obtained `r table(data$Harm_type)[2]` effect sizes where manipulations resulted in changes in direct harm (e.g., XX), whereas `r table(data$Harm_type)[3]` effects came from studies on species that manipulated indirect harm to females.
+From a total of `r table(data$Harm_type)[1]` effect sizes it was clear that females received both direct and indirect harm from male matings.
+
+Overall, we obtained `r table(data$Gestation)[1]` from `r parity[1,2]` oviparous species, and `r table(data$Gestation)[2]` from `r parity[2,2]`viviparous species.
+Unfortunately, viviparous species were all fish species with indirect female harm.
+As such, we analysed only 'harm type' and an index of sexual size dimorphism.

### 2021-03-29 ms.Rmd
Adding loading of metaAidR for I2
Updated bad writing

@@
 ```{r loadpackages, echo = FALSE, results = "hide"}
-  pacman::p_load(tidyverse, metafor, brms)
+  pacman::p_load(tidyverse, metafor, brms, metaAidR)
 
@@
   model <- rma.mv(SMDH ~ 1, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|variable, ~1|species), test = "t", data = data)
+
+  I2(model, v = data$v_SMDH, phylo = FALSE)
 
@@
 Unsurprisingly, invertebrates (classes: Insecta, Gastropoda, Malacostraca, Arachnida, Clitellata and Secernentea) made up most of the data (`r (table(inverts$insect)[2] / sum(table(inverts$insect)))*100`%).
-We obtained `r table(data$Harm_type)[2]` effect sizes where manipulations resulted in changes in direct harm (e.g., XX), whereas `r table(data$Harm_type)[3]` effects came from studies on species that manipulated indirect harm to females.
-From a total of `r table(data$Harm_type)[1]` effect sizes it was clear that females received both direct and indirect harm from male matings.
+We obtained `r table(data$Harm_type)[2]` effect sizes from manipulations on species that resulted in direct harm (e.g., XX), whereas `r table(data$Harm_type)[3]` effects came from studies on species that manipulated indirect harm to females (e.g., mating rate and harassment).
+A total of `r table(data$Harm_type)[1]` effect sizes were from experiment where females received both direct and indirect harm from male matings.
 
-Overall, we obtained `r table(data$Gestation)[1]` from `r parity[1,2]` oviparous species, and `r table(data$Gestation)[2]` from `r parity[2,2]`viviparous species.
-Unfortunately, viviparous species were all fish species with indirect female harm.
-As such, we analysed only 'harm type' and an index of sexual size dimorphism.
+Across all species, `r table(data$Gestation)[1]` effects were from `r parity[1,2]` oviparous species, and `r table(data$Gestation)[2]` effects were from `r parity[2,2]` viviparous species.
+Unfortunately, effect sizes from viviparous species were all take from studies on fish species with indirect male harm.
+As such, we analyzed only 'harm type' and an index of sexual size dimorphism.

### 2021-03-29 ms.Rmd
Added chunk options

@@
 ---
+```{r setup, include=FALSE}
+  knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
+  ## numbers >= 10^5 will be denoted in scientific notation,      ## numbers >= 10^5 will be denoted in scientific notation,
+    ## and rounded to 2 digits      ## and rounded to 2 digits
+    options(digits = 2)
+```
 

### 2021-03-29 ms.Rmd
just updating to render docs

--- 2021-03-29 ms.Rmd
@@
   output: 
+    bookdown::word_document2:
+      toc: no
+      toc_depth: 6
+      number_sections: true
+      reference_docx: template.docx
     bookdown::html_document2:
@@
       toc_float: yes
-    bookdown::word_document2:
-      toc: no
-      toc_depth: 6
-      number_sections: true
-      reference_docx: template.docx
   editor_options: 
@@
 ---
+```{r setup, include=FALSE}
+  knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
+  ## numbers >= 10^5 will be denoted in scientific notation,      ## numbers >= 10^5 will be denoted in scientific notation,
+    ## and rounded to 2 digits      ## and rounded to 2 digits
+    options(digits = 2)
+```
 
 ```{r loadpackages, echo = FALSE, results = "hide"}
-  pacman::p_load(tidyverse, metafor, brms, metaAidR)
+  pacman::p_load(tidyverse, metafor, brms, metaAidR, ape, phytools, metaAidR)
 
@@
 
-  model <- rma.mv(lnRR ~ 1, V = data$v_lnRR, random = list(~1|study, ~1|obs, ~1|variable, ~1|species), test = "t", data = data)
-
   model <- rma.mv(SMDH ~ 1, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|variable, ~1|species, ~1|species2), R = list(species = phylogeny), test = "t", data = data)
@@
 
-  model <- rma.mv(lnRR ~ SSD_lnRR, V =  data$v_lnRR, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
-
   model <- rma.mv(SMDH ~ Harm_type-1, V = data$v_SMDH, random = list(~1|study, ~1|species, ~1|obs), R = list(species = phylogeny), test = "t", data = data)
-  robust(model, cluster = data$study)
-
-  model <- rma.mv(lnRR ~ Harm_type, V = data$v_lnRR, random = list(~1|study, ~1|species, ~1|obs), R = list(species = phylogeny), test = "t", data = data)
   robust(model, cluster = data$study)
@@
 It's hard to know what is the driving factor...could be parity mode, but could be also due to all being fish, or even just that they are indirect measures, also, only 7 studies.
-  model <- rma.mv(lnRR ~ Gestation - 1, V = data$v_lnRR, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
-  robust(model, cluster = data$study)
 

### 2021-03-29 ms.Rmd
Writing

@@
 ```{r loadpackages, echo = FALSE, results = "hide"}
-  pacman::p_load(tidyverse, metafor, brms, metaAidR, ape, phytools, metaAidR)
+  pacman::p_load(tidyverse, metafor, brms, metaAidR, ape, phytools, metaAidR, orchaRd)
 
@@
 # Models
-  model <- rma.mv(SMDH ~ 1, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|variable, ~1|species), test = "t", data = data)
+  model1.1 <- rma.mv(SMDH ~ 1, V = data$v_SMDH, random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)
 
-  I2(model, v = data$v_SMDH, phylo = FALSE)
+hetero_table <-  I2(model1.1, v = data$v_SMDH, phylo = FALSE)
 
-  model <- rma.mv(SMDH ~ 1, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|variable, ~1|species, ~1|species2), R = list(species = phylogeny), test = "t", data = data)
+  model1.2 <- rma.mv(SMDH ~ 1, V = data$v_SMDH, random = list(~1|study, ~1|variable, ~1|species, ~1|species2, ~1|obs), R = list(species = phylogeny), test = "t", data = data)
 
-  model <- rma.mv(SMDH ~ SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
+hetero_table_phylo <-  I2(model1.2, v = data$v_SMDH, phylo = "species")
 
-  model <- rma.mv(SMDH ~ Harm_type-1, V = data$v_SMDH, random = list(~1|study, ~1|species, ~1|obs), R = list(species = phylogeny), test = "t", data = data)
-  robust(model, cluster = data$study)
+  model1.3 <- rma.mv(SMDH ~ SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
 
-  model <- rma.mv(SMDH ~ Harm_type + SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
-  robust(model, cluster = data$study)
+  model1.4 <- rma.mv(SMDH ~ Harm_type-1, V = data$v_SMDH, random = list(~1|study, ~1|species, ~1|obs), R = list(species = phylogeny), test = "t", data = data)
+  robust(model1.4, cluster = data$study)
 
-  model <- rma.mv(SMDH ~ Gestation + SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
-  robust(model, cluster = data$study)
+  model1.5 <- rma.mv(SMDH ~ Harm_type + SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
+  robust(model1.5, cluster = data$study)
+
+  model1.6 <- rma.mv(SMDH ~ Gestation + SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
+  robust(model1.6, cluster = data$study)
 
@@
 As such, we analyzed only 'harm type' and an index of sexual size dimorphism.
+
+#### Manipulating direct and indirect female harm negatively impacts female fitness
+
+Experimentally manipulating female harm resulted in a strong decrease in female fitness overall (i.e., positive effect size with control group females having higher fitness than treatment groups: `r model1.1$beta`, 95% CI: `r model1.1$ci.lb` to `r model1.1$ci.ub`, $n_{effects}$ = `r model1.1$k.all`, $n_{study}$ = `r model1.1$s.nlevels[1]`).
+Even when accouting for sampling variance there was high effect size heterogeneity ($I^2_{Total}$ = `r hetero_table$I2_Est.[nrow(hetero_table)]`, 95% CI: `r hetero_table[nrow(hetero_table), "2.5% CI"]` to `r hetero_table[nrow(hetero_table), "97.5% CI"]`) with most variance being the result of between study ($I^2_{Study}$ = `r hetero_table$I2_Est.[1]`, 95% CI: `r hetero_table[1, "2.5% CI"]` to `r hetero_table[1, "97.5% CI"]`) and between species ($I^2_{Species}$ = `r hetero_table$I2_Est.[3]`, 95% CI: `r hetero_table[3, "2.5% CI"]` to `r hetero_table[3, "97.5% CI"]`) effects.
+The trait type and phylogeny explained much less variation overall ($I^2_{Trait}$ = `r hetero_table$I2_Est.[2]`, 95% CI: `r hetero_table[2, "2.5% CI"]` to `r hetero_table[2, "97.5% CI"]`; $I^2_{Phylogeny}$ = `r hetero_table_phylo$I2_Est.[5]`, 95% CI: `r hetero_table_phylo[5, "2.5% CI"]` to `r hetero_table_phylo[5, "97.5% CI"]`).

### 2021-03-29 ms.Rmd
Dealing with publication bias problems for overall model. Testing with precisoon, and also effective sample size. N_eff makes more sense on the correction using the intercept

@@
               mutate(species2 = species)
+      data$n_eff <- with(data, (N_C*N_T) / (N_C+N_T))
 
@@
 hetero_table <-  I2(model1.1, v = data$v_SMDH, phylo = FALSE)
+
+# Publication bias. Based on funnel plot, it looks like pub bias. Correct effect
+  model1.1_pub <- rma.mv(SMDH ~ sqrt(1/n_eff), V = data$v_SMDH, random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)
 
@@
 ## Have a look at SSD data in relation to the key moderators
-  ggplot(data, aes(y = SSD_lnRR, x = Harm_type)) + geom_violin() + geom_point()
-  ggplot(data, aes(y = SSD_lnRR, x = Gestation)) + geom_violin() + geom_point()
+  #ggplot(data, aes(y = SSD_lnRR, x = Harm_type)) + geom_violin() + geom_point()
+  #ggplot(data, aes(y = SSD_lnRR, x = Gestation)) + geom_violin() + geom_point()
 
@@
 The trait type and phylogeny explained much less variation overall ($I^2_{Trait}$ = `r hetero_table$I2_Est.[2]`, 95% CI: `r hetero_table[2, "2.5% CI"]` to `r hetero_table[2, "97.5% CI"]`; $I^2_{Phylogeny}$ = `r hetero_table_phylo$I2_Est.[5]`, 95% CI: `r hetero_table_phylo[5, "2.5% CI"]` to `r hetero_table_phylo[5, "97.5% CI"]`).
+
+```{r funnel, fig.height=4.5, fig.width=4.5}
+funnel(model1.1, yaxis="seinv", digits = 2, las = 1)
+```

### 2021-03-29 R/data_prep.R
Just checking study/speceis corrspondance

@@ -67,6 +67,9 @@ theme_bw()
 # Find outlier data.There is a clear outlier, which is study 047. I've got to the original paper and noticed data was extracted from boxplot. SD values were very small for the mean data, suggesting data entry. I re-extracted from raw data which was also presented and SD's are much more sensible and way different from original extraction and conversion from box plot.
 data %>% filter(SMDH >=10) # NOTE: Outlier fixed. Raw data re-extracted as it was not correct.
 
+# What is the correspondence between study and species
+stdy_spp <- data.frame(data %>% group_by(species) %>% summarise(n_stdy = length(unique(study))))
+stdy_spp %>% filter(n_stdy > 1) %>% nrow(.) # Most species from one study but still 9 species across more than one study so should be able to decouple effects
 #####
 # What are effect sizes per groups looking like
 

### 2021-03-30 ms.Rmd
Adding some fany tabling, but needs fixing

@@
               mutate(species2 = species)
-      data$n_eff <- with(data, (N_C*N_T) / (N_C+N_T))
+      data$n_eff <- with(data, (4*(N_C*N_T)) / (N_C+N_T))
 
@@
 ```
+
+```{r pretty_table}
+table.model.r.gt <- table.model.r %>% 
+                             gt() %>% 
+          cols_label(n=md("**n**"),
+             k=md("**k**"),
+             mean=md("**Meta-analytic mean**"),
+             CI=md("**95% CI**"),
+             PI=md("**95% PI**"),
+             I2_obsID=md("***I*<sup>2</sup><sub>residual</sub>\n(%)**"),
+             I2_paperID=md("***I*<sup>2</sup><sub>study</sub>\n(%)**"),
+             I2_nonphylo=md("***I*<sup>2</sup><sub>non-phylogeny</sub>\n(%)**"),
+             I2_phylo=md("***I*<sup>2</sup><sub>phylogeny</sub>\n(%)**"),
+             I2_total=md("***I*<sup>2</sup><sub>total</sub>    \n(%)**"),
+             )                     %>%
+      cols_align(align = "center") %>%
+  tab_source_note(source_note = md("n = number of studies; k = number of effects; CI = confidence interval; PI = prediction interval; *I*<sup>2</sup> = heterogeneity")) #%>%
+# tab_options(table.width=770)
+```

### 2021-03-31 ms.Rmd
Adding some results

--- 2021-03-29 ms.Rmd
@@
       toc_depth: 6
-      number_sections: true
+      number_sections: false
       reference_docx: template.docx
@@
 ```{r loadpackages, echo = FALSE, results = "hide"}
-  pacman::p_load(tidyverse, metafor, brms, metaAidR, ape, phytools, metaAidR, orchaRd)
-
+  pacman::p_load(tidyverse, metafor, brms, metaAidR, ape, phytools, metaAidR, orchaRd, gt, kableExtra, flextable)
+  source("./R/func.R")
 ```
@@
 
-# Models
+###################
+# Multilevel Meta-analytic Models (intercept only), plus robust variace estimation test.
+###################
+
   model1.1 <- rma.mv(SMDH ~ 1, V = data$v_SMDH, random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)
+    robust <- robust(model1.1, cluster = data$study)
 
-hetero_table <-  I2(model1.1, v = data$v_SMDH, phylo = FALSE)
+  model1.2 <- rma.mv(SMDH ~ 1, V = data$v_SMDH, random = list(~1|study, ~1|variable, ~1|species, ~1|species2, ~1|obs), R = list(species2 = phylogeny), test = "t", data = data)
 
-  model1.2 <- rma.mv(SMDH ~ 1, V = data$v_SMDH, random = list(~1|study, ~1|variable, ~1|species, ~1|species2, ~1|obs), R = list(species = phylogeny), test = "t", data = data)
+  AIC(model1.2, model1.1) # Phylogeny explains very little variation; model without phylogeny better supported, even if slightly. Just keep species in model
 
-hetero_table_phylo <-  I2(model1.2, v = data$v_SMDH, phylo = "species")
+# Table 1: Effect, confidemce intervals, prediction intervals, heterogenity
+            table1 <- make_table(model1.1, data)
+      hetero_table <- I2(model1.1, v = data$v_SMDH)
+hetero_table_phylo <- I2(model1.2, v = data$v_SMDH, phylo = "species2")
 
-  model1.3 <- rma.mv(SMDH ~ SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
+###################
+# Publication bias. Based on funnel plot, it looks like pub bias. Correct effect as a sensitivity analysis
+###################
+
+     data$inv_n_eff <- with(data, (N_C + N_T) / (N_C * N_T))
+
+       model1.1_pub <- rma.mv(SMDH ~ sqrt(inv_n_eff), V = data$v_SMDH, random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)
+
+  model1.1_pub_full <- rma.mv(SMDH ~ sqrt(inv_n_eff) + SSD_lnRR + Harm_type, V = data$v_SMDH, random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)
+
+###################
+# Meta-regressions
+###################
+
+  model1.3 <- rma.mv(SMDH ~ SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)
+  robust(model1.3, cluster = data$study)
 
@@
 
-  model1.6 <- rma.mv(SMDH ~ Gestation + SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
-  robust(model1.6, cluster = data$study)
-
-  # Note that for gestation, these data on viviparous species are restricted completely to fish only, and indirect measurements.
-So, confounded.
-It's hard to know what is the driving factor...could be parity mode, but could be also due to all being fish, or even just that they are indirect measures, also, only 7 studies.
-
-## Have a look at SSD data in relation to the key moderators
-  ggplot(data, aes(y = SSD_lnRR, x = Harm_type)) + geom_violin() + geom_point()
-  ggplot(data, aes(y = SSD_lnRR, x = Gestation)) + geom_violin() + geom_point()
-
 ```
+# Methods
 
@@
 Unsurprisingly, invertebrates (classes: Insecta, Gastropoda, Malacostraca, Arachnida, Clitellata and Secernentea) made up most of the data (`r (table(inverts$insect)[2] / sum(table(inverts$insect)))*100`%).
-We obtained `r table(data$Harm_type)[2]` effect sizes from manipulations on species that resulted in direct harm (e.g., XX), whereas `r table(data$Harm_type)[3]` effects came from studies on species that manipulated indirect harm to females (e.g., mating rate and harassment).
+We obtained `r table(data$Harm_type)[2]` effect sizes from manipulations on species that resulted in direct harm (e.g., traumatic insemination), whereas `r table(data$Harm_type)[3]` effects came from studies on species that manipulated indirect harm to females (e.g., mating rate and harassment).
 A total of `r table(data$Harm_type)[1]` effect sizes were from experiment where females received both direct and indirect harm from male matings.
 
-Across all species, `r table(data$Gestation)[1]` effects were from `r parity[1,2]` oviparous species, and `r table(data$Gestation)[2]` effects were from `r parity[2,2]` viviparous species.
+Across all species, we obtained `r table(data$Gestation)[1]` effects from `r parity[1,2]` oviparous species, and `r table(data$Gestation)[2]` effects from `r parity[2,2]` viviparous species.
 Unfortunately, effect sizes from viviparous species were all take from studies on fish species with indirect male harm.
@@
 Experimentally manipulating female harm resulted in a strong decrease in female fitness overall (i.e., positive effect size with control group females having higher fitness than treatment groups: `r model1.1$beta`, 95% CI: `r model1.1$ci.lb` to `r model1.1$ci.ub`, $n_{effects}$ = `r model1.1$k.all`, $n_{study}$ = `r model1.1$s.nlevels[1]`).
-Even when accouting for sampling variance there was high effect size heterogeneity ($I^2_{Total}$ = `r hetero_table$I2_Est.[nrow(hetero_table)]`, 95% CI: `r hetero_table[nrow(hetero_table), "2.5% CI"]` to `r hetero_table[nrow(hetero_table), "97.5% CI"]`) with most variance being the result of between study ($I^2_{Study}$ = `r hetero_table$I2_Est.[1]`, 95% CI: `r hetero_table[1, "2.5% CI"]` to `r hetero_table[1, "97.5% CI"]`) and between species ($I^2_{Species}$ = `r hetero_table$I2_Est.[3]`, 95% CI: `r hetero_table[3, "2.5% CI"]` to `r hetero_table[3, "97.5% CI"]`) effects.
+This strong effect held even when accounting for within-study non-independence (Meta-analytic mean using Robust Variance Estimator: `r robust$beta`, 95% CI: `r robust$ci.lb` to `r robust$ci.ub`).
+However, visual inspection of funnel plot asymmetry suggested evidence for publication bias (i.e., missed effects sizes with low precision when female harm was worse in control treatments) (Figure \@ref(fig:funnel)).
+Evidence for publication bias was confirmed through the identification of a significant slope between effect size and effective sample size ($\beta$ = `r model1.1_pub$beta[2]`, 95% CI: `r model1.1_pub$ci.lb[2]` to `r model1.1_pub$ci.ub[2]`), and this held true when accounting for heterogenity using meta-regression models ($\beta$ =`r model1.1_pub_full$beta[2]`, 95% CI: `r model1.1_pub_full$ci.lb[2]` to `r model1.1_pub_full$ci.ub[2]`).
+Correcting for the possibility of missing studies resulted in the overall meta-analytic mean effect size being indistinguisable from zero (Corrected meta-analytic mean: `r model1.1_pub$beta[1]`, 95% CI: `r model1.1_pub$ci.lb[1]` to `r model1.1_pub$ci.ub[1]`).
+It is important recognise that the corrected meta-analytic mean is simply a sensitivity analysis, and we cannot know for certain whether there indeed are and how many, missing studies.
+
+When accouting for sampling variance there was high effect size heterogeneity ($I^2_{Total}$ = `r hetero_table$I2_Est.[nrow(hetero_table)]`, 95% CI: `r hetero_table[nrow(hetero_table), "2.5% CI"]` to `r hetero_table[nrow(hetero_table), "97.5% CI"]`) with most variance being the result of between study ($I^2_{Study}$ = `r hetero_table$I2_Est.[1]`, 95% CI: `r hetero_table[1, "2.5% CI"]` to `r hetero_table[1, "97.5% CI"]`) and between species ($I^2_{Species}$ = `r hetero_table$I2_Est.[3]`, 95% CI: `r hetero_table[3, "2.5% CI"]` to `r hetero_table[3, "97.5% CI"]`) effects.
 The trait type and phylogeny explained much less variation overall ($I^2_{Trait}$ = `r hetero_table$I2_Est.[2]`, 95% CI: `r hetero_table[2, "2.5% CI"]` to `r hetero_table[2, "97.5% CI"]`; $I^2_{Phylogeny}$ = `r hetero_table_phylo$I2_Est.[5]`, 95% CI: `r hetero_table_phylo[5, "2.5% CI"]` to `r hetero_table_phylo[5, "97.5% CI"]`).
+
+```{r funnel, fig.height=4.5, fig.width=4.5, fig.cap="Funnel plot of effect size as a function of precision (i.e., inverse of sampling standard error). 95% pseudoconfidence intervals are provuded."}
+funnel(model1.1, yaxis="seinv", digits = 2, las = 1)
+
+```
+```{r pretty_table}
+
+autonum <- officer::run_autonum(seq_id = "tab", pre_label = "Table 1", bkm_all = TRUE)
+ft <- flextable(table1)
+ft <- set_caption(ft,  caption = "Effect size", autonum = autonum)
+ft <- set_header_labels(ft, n = md("$n_{effects}$"),
+                    std = md("**n<sub>studies<sub>**"),
+                     spp = md("**n<sub>species<sub>**"),
+                  est = md("**Meta-analytic mean**"),
+                    CI = md("**95% CI**"),
+                    PI = md("**95% PI**"),
+              i2_stdy = md("***I*<sup>2</sup><sub>study</sub>\n(%)**"),
+            i2_trait = md("***I*<sup>2</sup><sub>trait</sub>\n(%)**"),
+           i2_species = md("***I*<sup>2</sup><sub>species</sub>\n(%)**"),
+             i2_tot = md("***I*<sup>2</sup><sub>total</sub>    \n(%)**"))
+ft
+
+```
+
+#### Negative effects on fitness depend on the type of harm done to females
+
+#### Female fitness is comproised more in species with male-biased sexual size dimorphism (SSD)

### 2021-03-31 R/func.R

@@ -15,3 +15,28 @@ replace_names <- function(string, match, replace){
 	string_replaced <-replace[match(string, match)]
 	return(string_replaced)
 }
+
+
+#' @title make_table
+#' @description Function takes a MLM intercept only metafor model and creates a table. 
+#' @param model Metafor intercept only model
+#' @param data The data frame
+
+make_table <- function(model, data){
+ hetero_table <-  metaAidR::I2(model, v = data$v_SMDH, phylo = FALSE)
+ estimates    <-  predict(model)
+ 
+  tmp <-  data.frame(  n = model$k,
+                       std = model$s.nlevels[1],
+                       spp = model$s.nlevels[3],
+                       est = round(estimates$pred, digits = 2), 
+                        CI = paste0(round(estimates$ci.lb, digits = 2), " to ", round(estimates$ci.ub, digits = 2)),
+                        PI = paste0(round(estimates$cr.lb, digits = 2), " to ", round(estimates$cr.ub, digits = 2)),
+                   i2_stdy = paste0(hetero_table[rownames(hetero_table)=="study",][1]*100, "%", " (", hetero_table[rownames(hetero_table)=="study",][2]*100, " - ", hetero_table[rownames(hetero_table)=="study",][3]*100, "%)" ), 
+                  i2_trait = paste0(hetero_table[rownames(hetero_table)=="variable",][1]*100, "%", " (", hetero_table[rownames(hetero_table)=="variable",][2]*100, " - ", hetero_table[rownames(hetero_table)=="variable",][3]*100, "%)" ), 
+                i2_species = paste0(hetero_table[rownames(hetero_table)=="species",][1]*100, "%", " (", hetero_table[rownames(hetero_table)=="species",][2]*100, " - ", hetero_table[rownames(hetero_table)=="species",][3]*100, "%)" ), 
+                    i2_tot = paste0(hetero_table[rownames(hetero_table)=="total",][1]*100, "%", " (", hetero_table[rownames(hetero_table)=="total",][2]*100, " - ", hetero_table[rownames(hetero_table)=="total",][3]*100, "%)" )
+  )
+  
+  return(tmp)
+}

### 2021-03-31 ms.Rmd
More results

@@
 ```{r loadpackages, echo = FALSE, results = "hide"}
-  pacman::p_load(tidyverse, metafor, brms, metaAidR, ape, phytools, metaAidR, orchaRd, gt, kableExtra, flextable)
+  pacman::p_load(tidyverse, metafor, brms, metaAidR, ape, phytools, metaAidR, orchaRd, gt, kableExtra, flextable, patchwork, latex2exp, ggarrange)
   source("./R/func.R")
@@
             table1 <- make_table(model1.1, data)
-      hetero_table <- I2(model1.1, v = data$v_SMDH)
+      hetero_table <- I2(model1.1, v = data$v_SMDH) # Same as orchaRd::i2_ml(model1.1)
 hetero_table_phylo <- I2(model1.2, v = data$v_SMDH, phylo = "species2")
@@
 
-  model1.3 <- rma.mv(SMDH ~ SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)
+  model1.3 <- rma.mv(SMDH ~ scale(SSD_lnRR), V = data$v_SMDH, random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)
   robust(model1.3, cluster = data$study)
+
+  r2_SSD=r2_ml(model1.3)
 
@@
 
-  model1.5 <- rma.mv(SMDH ~ Harm_type + SSD_lnRR, V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
+  r2_ml(model1.4)
+
+  model1.5 <- rma.mv(SMDH ~ Harm_type + scale(SSD_lnRR), V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
   robust(model1.5, cluster = data$study)
@@
 
-```{r funnel, fig.height=4.5, fig.width=4.5, fig.cap="Funnel plot of effect size as a function of precision (i.e., inverse of sampling standard error). 95% pseudoconfidence intervals are provuded."}
-funnel(model1.1, yaxis="seinv", digits = 2, las = 1)
+```{r funnel, fig.height=5, fig.width=16, fig.cap="A) Funnel plot of effect size as a function of precision (i.e., inverse of sampling standard error).
+B) orchaRd plot of the overall meta-analytic mean efect size, 95% confidnece intervals (thick black bars) and 95% prediction intervals (whiskers)"}
+p1 <- ggplot(data, aes(x = SMDH, y = 1 / sqrt(v_SMDH), xmin = -6, xmax = 6)) +
+geom_point(aes(colour = class)) +
+labs(x = "SMDH", 
+	 y = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$"),
+	 colour = "Class") +
+scale_color_grey() + 
+#scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9")) + 
+theme_bw()
+
+p2 <- orchard_plot(model1.1, mod = "Int", xlab = "SMDH") + scale_colour_manual(values = "grey") + scale_fill_manual(values = "red")
+
+p1 + p2 + plot_annotation(tag_levels = c('A', 'B'))
 
@@
 
-#### Female fitness is comproised more in species with male-biased sexual size dimorphism (SSD)
+#### Female fitness is less compromised in species with reversed sexual size dimorphism (SSD)
+
+Species where females are larger than males (i.e., negative SSD) are less impacted by sexual conflict compared to spcies where males and females are closer in size or males are larger (i.e., SSD > 0) (z-transformed $\beta_{SSD}$ = `r model1.3$beta[2]`, 95% CI = `r model1.3$ci.lb[2]` to `r model1.3$ci.ub[2]`, Figure \@ref(fig:SSD) , $R^2_{marginal}$ = `r r2_SSD[1]*100`% of effect size variation).
+
+```{r SSD, fig.width=6, fig.height=4.5}
+p3 = ggplot(data, aes(x = SSD_lnRR, y = SMDH, size = 1/sqrt(v_SMDH))) + 
+    geom_point() + 
+      theme_bw() + 
+  labs(x = "SSD", 
+	     y = "SMDH",
+	  size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$")) +
+	guides(size = guide_legend(direction = "vertical"))
+
+p3
+```

### 2021-04-30 ms.Rmd
Fixing code for one function. Adding stats methods. Need one more section fro results, few more paragrahs on methods

@@
   output: 
-    bookdown::word_document2:
-      toc: no
-      toc_depth: 6
-      number_sections: false
-      reference_docx: template.docx
     bookdown::html_document2:
@@
       toc_float: yes
+    bookdown::word_document2:
+      toc: no
+      toc_depth: 6
+      number_sections: false
+      reference_docx: template.docx
   editor_options: 
@@
 ```{r loadpackages, echo = FALSE, results = "hide"}
-  pacman::p_load(tidyverse, metafor, brms, metaAidR, ape, phytools, metaAidR, orchaRd, gt, kableExtra, flextable, patchwork, latex2exp, ggarrange)
+  pacman::p_load(tidyverse, metafor, brms, metaAidR, ape, phytools, metaAidR, orchaRd, gt, kableExtra, flextable, patchwork, latex2exp, MuMIn)
+eval(metafor:::.MuMIn)
 source("./R/func.R")
+
 ```
 ```{r loaddata, echo = FALSE, results = "hide"}
+################
 # Tree
+################
       data <- read.csv("./data/meta_data.csv")
@@
 
+  # Number of effects per study
+  n_eff_study <- data %>%
+                  group_by(study) %>%
+                  summarise(n = n())
+  n_eff_study <- range(n_eff_study$n)
+
 ###################
@@
 
-  model1.1 <- rma.mv(SMDH ~ 1, V = data$v_SMDH, random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)
-    robust <- robust(model1.1, cluster = data$study)
+  model1.1 <- rma.mv(SMDH ~ 1, V = data$v_SMDH, 
+                     random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)
+    robust <- robust(model1.1, cluster = data$study, vcov = "CR2")
 
-  model1.2 <- rma.mv(SMDH ~ 1, V = data$v_SMDH, random = list(~1|study, ~1|variable, ~1|species, ~1|species2, ~1|obs), R = list(species2 = phylogeny), test = "t", data = data)
+  model1.2 <- rma.mv(SMDH ~ 1, V = data$v_SMDH, 
+                     random = list(~1|study, ~1|variable, ~1|species, ~1|species2, ~1|obs), R = list(species2 = phylogeny), test = "t", data = data)
 
-  AIC(model1.2, model1.1) # Phylogeny explains very little variation; model without phylogeny better supported, even if slightly. Just keep species in model
+   aics <- AICc(model1.2, model1.1) # Phylogeny explains very little variation; model without phylogeny better supported, even if slightly. Just keep species in model
+  dAICc <- max(aics$AICc) - min(aics$AICc)
 
 # Table 1: Effect, confidemce intervals, prediction intervals, heterogenity
-            table1 <- make_table(model1.1, data)
-      hetero_table <- I2(model1.1, v = data$v_SMDH) # Same as orchaRd::i2_ml(model1.1)
-hetero_table_phylo <- I2(model1.2, v = data$v_SMDH, phylo = "species2")
+   hetero_table <- metaAidR::I2(model1.1, v = data$v_SMDH, obs = "obs") # Same as orchaRd::i2_ml(model1.1)    
+   hetero_table_phylo <- metaAidR::I2(model1.2, v = data$v_SMDH, phylo = "species2", obs = "obs") # Same as orchaRd::i2_ml(model1.1)    
+         table1 <- make_table(model1.1, heteroTable = hetero_table)
 
@@
 
-       model1.1_pub <- rma.mv(SMDH ~ sqrt(inv_n_eff), V = data$v_SMDH, random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)
+       model1.1_pub <- rma.mv(SMDH ~ sqrt(inv_n_eff), V = data$v_SMDH, 
+                              random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)
 
-  model1.1_pub_full <- rma.mv(SMDH ~ sqrt(inv_n_eff) + SSD_lnRR + Harm_type, V = data$v_SMDH, random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)
+  model1.1_pub_full <- rma.mv(SMDH ~ sqrt(inv_n_eff) + SSD_lnRR + Harm_type, V = data$v_SMDH, 
+                              random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)
 
@@
 
-  model1.3 <- rma.mv(SMDH ~ scale(SSD_lnRR), V = data$v_SMDH, random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)
+  model1.3 <- rma.mv(SMDH ~ scale(SSD_lnRR), V = data$v_SMDH, 
+                     random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)
   robust(model1.3, cluster = data$study)
@@
 
-  model1.4 <- rma.mv(SMDH ~ Harm_type-1, V = data$v_SMDH, random = list(~1|study, ~1|species, ~1|obs), R = list(species = phylogeny), test = "t", data = data)
+  model1.4 <- rma.mv(SMDH ~ Harm_type-1, V = data$v_SMDH, 
+                     random = list(~1|study, ~1|species, ~1|obs), R = list(species = phylogeny), test = "t", data = data)
   robust(model1.4, cluster = data$study)
@@
 
-  model1.5 <- rma.mv(SMDH ~ Harm_type + scale(SSD_lnRR), V = data$v_SMDH, random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
+  model1.5 <- rma.mv(SMDH ~ Harm_type + scale(SSD_lnRR), V = data$v_SMDH, 
+                     random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
   robust(model1.5, cluster = data$study)
@@
 # Methods
+
+#### Meta-analysis
+We analysed effect size data using the *metafor* (@Metafor - vers 2.4.0) package in R (@R - vers 4.0.5).
+To estimate the overall effect of male-harm on female fitness we first fit multi-level meta-analytic models (intercept only) (@nakagawa2012methodological).
+Overall, we collected between `r n_eff_study[1]` to `r n_eff_study[2]` effect sizes per study.
+To control for sources of non-independence, we included study and species-level random effects (@Noble2017).
+We also fit a model that included a species-level  random effect with a phylogenetic correlation matrix.
+However, a model containing only a species-level random effect variance was better supported than a model that estimated a phylogenetic variance ($\Delta_{AIC_{c}}$ = `r dAICc`).
+As such, we did not include phylogeny in our models.
+Study and species-level random effects cannot account for additional sources of within-study non-independence, such as effect sizes derived from common treatment groups or effect sizes derived from different traits measured on the same individuals (@Noble2017).
+We therefore applied robust variance estimators (RVEs) to correct standard errors from our models.
+RVEs have been shown to be robust estimators of standard errors from meta-analytic models when effect sizes within studies are not indpendent.
+In addition, one does not need to assume or specify how such effects are correlated  (@Song2021), making them easier to apply.
+
+Using our MLMA models we estimated effect size heterogenity as $I^2$ (@nakagawa2012methodological).
+$I^2_{study}$ and $I^2_{species}$ were the proportion of effect size variance over total variance as a result of between study and species effects, respectively.
+$I^2_{total}$ was calculated as the proportion of total effect size variance after accounting for, or removing, total sampling variance.
 
@@
 We obtained `r table(data$Harm_type)[2]` effect sizes from manipulations on species that resulted in direct harm (e.g., traumatic insemination), whereas `r table(data$Harm_type)[3]` effects came from studies on species that manipulated indirect harm to females (e.g., mating rate and harassment).
-A total of `r table(data$Harm_type)[1]` effect sizes were from experiment where females received both direct and indirect harm from male matings.
+A total of `r table(data$Harm_type)[1]` effect sizes were from experiments where females received both direct and indirect harm from male matings.
 
 Across all species, we obtained `r table(data$Gestation)[1]` effects from `r parity[1,2]` oviparous species, and `r table(data$Gestation)[2]` effects from `r parity[2,2]` viviparous species.
-Unfortunately, effect sizes from viviparous species were all take from studies on fish species with indirect male harm.
+Unfortunately, effect sizes from viviparous species were all taken from studies on fish species with indirect male harm.
 As such, we analyzed only 'harm type' and an index of sexual size dimorphism.
@@
 Correcting for the possibility of missing studies resulted in the overall meta-analytic mean effect size being indistinguisable from zero (Corrected meta-analytic mean: `r model1.1_pub$beta[1]`, 95% CI: `r model1.1_pub$ci.lb[1]` to `r model1.1_pub$ci.ub[1]`).
-It is important recognise that the corrected meta-analytic mean is simply a sensitivity analysis, and we cannot know for certain whether there indeed are and how many, missing studies.
+It is important recognise that the corrected meta-analytic mean is simply a sensitivity analysis.
+We cannot know for certain whether publication bias treuly exists, and if so, how many missing studies exist.
 
-When accouting for sampling variance there was high effect size heterogeneity ($I^2_{Total}$ = `r hetero_table$I2_Est.[nrow(hetero_table)]`, 95% CI: `r hetero_table[nrow(hetero_table), "2.5% CI"]` to `r hetero_table[nrow(hetero_table), "97.5% CI"]`) with most variance being the result of between study ($I^2_{Study}$ = `r hetero_table$I2_Est.[1]`, 95% CI: `r hetero_table[1, "2.5% CI"]` to `r hetero_table[1, "97.5% CI"]`) and between species ($I^2_{Species}$ = `r hetero_table$I2_Est.[3]`, 95% CI: `r hetero_table[3, "2.5% CI"]` to `r hetero_table[3, "97.5% CI"]`) effects.
+When accounting for sampling variance there was high effect size heterogeneity ($I^2_{Total}$ = `r hetero_table$I2_Est.[nrow(hetero_table)]`, 95% CI: `r hetero_table[nrow(hetero_table), "2.5% CI"]` to `r hetero_table[nrow(hetero_table), "97.5% CI"]`) with most variance being the result of between study ($I^2_{Study}$ = `r hetero_table$I2_Est.[1]`, 95% CI: `r hetero_table[1, "2.5% CI"]` to `r hetero_table[1, "97.5% CI"]`) and between species ($I^2_{Species}$ = `r hetero_table$I2_Est.[3]`, 95% CI: `r hetero_table[3, "2.5% CI"]` to `r hetero_table[3, "97.5% CI"]`) effects.
 The trait type and phylogeny explained much less variation overall ($I^2_{Trait}$ = `r hetero_table$I2_Est.[2]`, 95% CI: `r hetero_table[2, "2.5% CI"]` to `r hetero_table[2, "97.5% CI"]`; $I^2_{Phylogeny}$ = `r hetero_table_phylo$I2_Est.[5]`, 95% CI: `r hetero_table_phylo[5, "2.5% CI"]` to `r hetero_table_phylo[5, "97.5% CI"]`).
@@
 ft <- set_caption(ft,  caption = "Effect size", autonum = autonum)
-ft <- set_header_labels(ft, n = md("$n_{effects}$"),
+ft <- set_header_labels(ft, n = TeX("$n_{effects}$"),
                           std = md("**n<sub>studies<sub>**"),
@@
 
+Male harm type impacted the overall magnitude of effects.
+
 #### Female fitness is less compromised in species with reversed sexual size dimorphism (SSD)
@@
       theme_bw() + 
-  labs(x = "SSD", 
+  labs(x = "Sexual Size Dimorphism (SSD) Index", 
 	     y = "SMDH",
@@
 ```
+
+# References

### 2021-04-30 R/func.R

@@ -20,10 +20,10 @@ replace_names <- function(string, match, replace){
 #' @title make_table
 #' @description Function takes a MLM intercept only metafor model and creates a table. 
 #' @param model Metafor intercept only model
-#' @param data The data frame
+#' @param heteroTable The heterogenity table derived from metafor::I2
 
-make_table <- function(model, data){
- hetero_table <-  metaAidR::I2(model, v = data$v_SMDH, phylo = FALSE)
+make_table <- function(model,  heteroTable){
+ hetero_table <-  heteroTable
  estimates    <-  predict(model)
  
   tmp <-  data.frame(  n = model$k,

### 2021-05-01 ms.Rmd
Adding new figure for HarmType. Need to add in estimates and PIs etc, maybe just use orchard for it, but lets see

@@
 
+```{r maleharn, fig.width=6, fig.height=4.5}
+ggplot(data, aes(x = Harm_type, y = SMDH, size = 1/sqrt(v_SMDH), fill = Harm_type, colour = Harm_type)) + geom_violin(alpha = 0.2) + geom_point() + 
+  geom_jitter(width = 0.1) + 
+  theme_bw() + 
+		theme(legend.background = element_blank(),
+			           legend.key = element_blank()) + 
+  labs(x = "Harm Type", y = "SMDH", size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$")) +
+  scale_x_discrete(labels = c("Both", "Direct", "Indirect")) +
+  guides(size = guide_legend(override.aes = list(linetype = 0))) + 
+   scale_colour_discrete(guide = FALSE) +
+  scale_fill_discrete(guide = FALSE)
+```
 #### Female fitness is less compromised in species with reversed sexual size dimorphism (SSD)

### 2021-05-01 ms.Rmd
Added refs and also updated MS with some more methods details. Added some code to fix last figure, bbut needs work. Get Robust values and PIs. Working on getting predictions from MLMR models.

--- 2021-04-30 ms.Rmd
@@
   output: 
+    bookdown::word_document2:
+      toc: no
+      toc_depth: 6
+      number_sections: false
+      reference_docx: template.docx
     bookdown::html_document2:
@@
       toc_float: yes
-    bookdown::word_document2:
-      toc: no
-      toc_depth: 6
-      number_sections: false
-      reference_docx: template.docx
   editor_options: 
@@
 ```{r loadpackages, echo = FALSE, results = "hide"}
-  pacman::p_load(tidyverse, metafor, brms, metaAidR, ape, phytools, metaAidR, orchaRd, gt, kableExtra, flextable, patchwork, latex2exp, MuMIn)
+  pacman::p_load(tidyverse, metafor, brms, metaAidR, ape, phytools, metaAidR, orchaRd, gt, kableExtra, flextable, patchwork, latex2exp, MuMIn, equatiomatic, magrittr, data.table)
 eval(metafor:::.MuMIn)
@@
    hetero_table_phylo <- metaAidR::I2(model1.2, v = data$v_SMDH, phylo = "species2", obs = "obs") # Same as orchaRd::i2_ml(model1.1)    
-         table1 <- make_table(model1.1, heteroTable = hetero_table)
+         table1 <- make_table(robust, heteroTable = hetero_table)
 
@@
   model1.4 <- rma.mv(SMDH ~ Harm_type-1, V = data$v_SMDH, 
-                     random = list(~1|study, ~1|species, ~1|obs), R = list(species = phylogeny), test = "t", data = data)
+                     random = list(~1|study, ~1|species, ~1|obs), test = "t", data = data)
   robust(model1.4, cluster = data$study)
@@
 
+  # Model that contains harm type and SSD. Harmtype appears to have different variances, so I'll check whether it is safe to assume homogeneity of variance across groups
   model1.5 <- rma.mv(SMDH ~  Harm_type + scale(SSD_lnRR), V = data$v_SMDH, 
-                     random = list(~1|study, ~1|obs, ~1|species), R = list(species = phylogeny), test = "t", data = data)
-  robust(model1.5, cluster = data$study)
+                     random = list(~1|study, ~1|obs, ~1|species), test = "t", data = data)
+
+  model1.6 <- rma.mv(SMDH ~ Harm_type + scale(SSD_lnRR), V = data$v_SMDH, 
+                     random = list(~1|study, ~(1 + Harm_type)|obs, ~1|species), 
+                     rho = 0, struc = "HCS", test = "t", data = data)
+
+  # Compare AICc for each model
+    aicc_het <- AICc(model1.5, model1.6)
+  d_aicc_het <- max(aicc_het$AICc) - min(aicc_het$AICc) # Delta suggests homogeneity model better
+
+  # Check robustness of results using sandwich estimator
+  robust_model1.5 <- robust(model1.5, cluster = data$study, vcov = "CR2")
+  predict(robust_model1.5)
+
+  # Now reparameterize model
+  model1.5_2 <- rma.mv(SMDH ~ 0 + Harm_type + scale(SSD_lnRR), V = data$v_SMDH, 
+                     random = list(~1|study, ~1|obs, ~1|species), test = "t", data = data)
+
+  robust_model1.5_2 <- robust(model1.5_2, cluster = data$study, vcov = "CR2")
+
+  predict(robust_model1.5, newmods = newdata)
 
@@
 #### Meta-analysis
-We analysed effect size data using the *metafor* (@Metafor - vers 2.4.0) package in R (@R - vers 4.0.5).
-To estimate the overall effect of male-harm on female fitness we first fit multi-level meta-analytic models (intercept only) (@nakagawa2012methodological).
+We analysed effect size data using the *metafor* @Metafor (vers 2.4.0) package in R @R (vers 4.0.5).
+To estimate the overall effect of male-harm on female fitness we first fit multi-level meta-analytic models (intercept only) @nakagawa2012methodological.
 Overall, we collected between `r n_eff_study[1]` to `r n_eff_study[2]` effect sizes per study.
-To control for sources of non-independence, we included study and species-level random effects (@Noble2017).
-We also fit a model that included a species-level  random effect with a phylogenetic correlation matrix.
-However, a model containing only a species-level random effect variance was better supported than a model that estimated a phylogenetic variance ($\Delta_{AIC_{c}}$ = `r dAICc`).
+To control for sources of non-independence, we included study and species-level random effects @Noble2017.
+We also fit a model that included a species-level random effect with a phylogenetic correlation matrix derived using the Open Tree of Life Database @rotl.
+We used Grafen's method @Grafen to derive branch lengths using the R package *ape* @ape (vers 5.4.1).
+Overall, a model containing only a species-level random effect variance was better supported than a model that estimated a phylogenetic variance ($\Delta_{AIC_{c}}$ = `r dAICc`).
 As such, we did not include phylogeny in our models.
-Study and species-level random effects cannot account for additional sources of within-study non-independence, such as effect sizes derived from common treatment groups or effect sizes derived from different traits measured on the same individuals (@Noble2017).
-We therefore applied robust variance estimators (RVEs) to correct standard errors from our models.
-RVEs have been shown to be robust estimators of standard errors from meta-analytic models when effect sizes within studies are not indpendent.
-In addition, one does not need to assume or specify how such effects are correlated  (@Song2021), making them easier to apply.
+Study and species-level random effects cannot account for additional sources of within-study non-independence, such as effect sizes derived from common treatment groups or effect sizes derived from different traits measured on the same individuals @Noble2017.
+We therefore applied robust variance estimators (RVEs) to correct standard errors from our models and ensure that our results were robust.
+RVEs have been shown to be robust estimators of standard errors from meta-analytic models when effect sizes within studies are correlated.
+In addition, one does not need to assume or specify how such effects are correlated @Song2021; @NakagawaEcology, making them easier to apply.
 
-Using our MLMA models we estimated effect size heterogenity as $I^2$ (@nakagawa2012methodological).
+Using our MLMA models we estimated effect size heterogenity as $I^2$ @HigginsThompson; @nakagawa2012methodological.
 $I^2_{study}$ and $I^2_{species}$ were the proportion of effect size variance over total variance as a result of between study and species effects, respectively.
 $I^2_{total}$ was calculated as the proportion of total effect size variance after accounting for, or removing, total sampling variance.
+
+We explored drivers of effect size heterogenity using multi-level meta-regression (MLMR) models.
+Our models included fixed effects (i.e., moderators) that we *a priori* predicted would impact female fitness.
+More specifically, we predicted that the intensity of sexual selection and sexual conflict would impact how much harm males did to females.
+To test these predictions, we included an index of sexual size dimorphism (SSD), which involved taking the log transfomed ratio between male body size to female body size for the species (i.e.,  $log \left( \frac{Male_{body size}}{Female_{bodysize}} \right)$, hereafter referred to as SSD).
+Positive SSD values indicate species with larger males compared to females, whereas negative SSD values indicate speceis where females are larger than males.
+While this does not directly measure the intensity of sexual selection, it is a proxy for it, and has been used in numerous meta-analyses in the past (CITE).
+
+In addition to SSD, we also categorised effect sizes as having come from species with different types of male harm.
+These include species with direct male harm (i.e., species with traumatic insemination) as well as species with indirect male harm (i.e., species that harm females through harrassment).
+There are also a number of species where it is clear both direct and indirect forms of male harm exist.
+Given that MLMR models assume homogeneity of variances across the levels of categorical moderators, and this assumption appeared to violated when visually inspecting the data (Figure \@ref(fig:maleharm)), we also fit a model that assumed heterogeneous residual variance across the different levels of male harm type moderator (i.e., different residual variance for 'Both', 'Direct' and 'Indirect' male harm type).
+We compared this model to a homogeneous variance model using $AIC_{c}$.
+Overall, the heterogeneous variance model did not improve overall fit ($\Delta_{AIC_{c}}$ = `r d_aicc_het`), and so, we report on the model assuming homogeneity of variance.
+
+#### Publication Bias
+
+Publication bias results when studies with lower statistical power that find opposite patterns to the predicted effects (i.e., male harm increases female fitnes) go unpublished.
+This can result in effects being upwardly biased overall.
+Evidence for publication bias can be roughly detected by inspecting a funnel plot for funnel asymmetry.
+However, any asymmetry identified may simply be the result of high effect size heterogenity.
+As such, to more formally test for publication bias we used a new method that relies on fitting a MLMR model accounting for all the moderators available to explain variation in effects (i.e., all random and fixed effects).
+Using this model, we also include effect size sampling variance as a moderator @NakagawaPubBias.
+This apporach has the benefit of being a formal way to both statistically test for publication bias (while accounting for as much effect size heterogeneity as possible) and correcting for it; providing a sensitivity analysis on how the effect is expected to change if we were to hypothetically observe the missing effects @NakagawaPubBias.
+It is still important to note that this corrected overall mean should be interpreted with caution.
+We can never know exactly how many studies, if any, are missing.
+As such, these shoud be viewed as a sensitivity analysis.
 
@@
 ```
+
 ```{r pretty_table}
@@
 ft <- set_caption(ft,  caption = "Effect size", autonum = autonum)
-ft <- set_header_labels(ft, n = TeX("$n_{effects}$"),
-                          std = md("**n<sub>studies<sub>**"),
-                          spp = md("**n<sub>species<sub>**"),
-                          est = md("**Meta-analytic mean**"),
-                           CI = md("**95% CI**"),
-                           PI = md("**95% PI**"),
-                      i2_stdy = md("***I*<sup>2</sup><sub>study</sub>\n(%)**"),
-                     i2_trait = md("***I*<sup>2</sup><sub>trait</sub>\n(%)**"),
-                   i2_species = md("***I*<sup>2</sup><sub>species</sub>\n(%)**"),
-                       i2_tot = md("***I*<sup>2</sup><sub>total</sub>    \n(%)**"))
-ft
+ft %>%
+  compose(part = "header", j = "n", value = as_paragraph("n", as_sub("effects"))) %>%
+  compose(part = "header", j = "std", value = as_paragraph("n", as_sub("studies"))) %>%
+  compose(part = "header", j = "spp", value = as_paragraph("n", as_sub("species"))) %>%
+  compose(part = "header", j = "est", value = as_paragraph("Meta-analytic mean")) %>%
+  compose(part = "header", j = "CI", value = as_paragraph("95% CI")) %>%
+  compose(part = "header", j = "PI", value = as_paragraph("95% PI")) %>%
+  compose(part = "header", j = "i2_stdy", value = as_paragraph("I", as_sup("2"), as_sub("study"))) %>%
+  compose(part = "header", j = "i2_trait", value = as_paragraph("I", as_sup("2"), as_sub("trait"))) %>%
+  compose(part = "header", j = "i2_species", value = as_paragraph("I", as_sup("2"), as_sub("species"))) %>%
+  compose(part = "header", j = "i2_tot", value = as_paragraph("I", as_sup("2"), as_sub("total")))
 
@@
 
+```{r maleharm, fig.width=6, fig.height=4.5}
+
+ggplot(data, aes(x = Harm_type, y = SMDH, size = 1/sqrt(v_SMDH), fill = Harm_type, colour = Harm_type)) + geom_violin(alpha = 0.2) + geom_point() + 
+  geom_jitter(width = 0.1) + 
+   	#ggplot2::geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR),  height = 0, show.legend = FALSE, size = 0.5, alpha = 0.6) +
+	  	# 95 %CI: branches
+	  #	ggplot2::geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL),  height = 0, show.legend = FALSE, size = 1.2) +
+	  #	ggplot2::geom_vline(xintercept = 0, linetype = 2, colour = "black", alpha = alpha) + 
+      theme_bw() + 
+		theme(legend.background = element_blank(),
+			           legend.key = element_blank()) + 
+  labs(x = "Harm Type", y = "SMDH", size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$")) +
+  scale_x_discrete(labels = c("Both", "Direct", "Indirect")) +
+  guides(size = guide_legend(override.aes = list(linetype = 0))) + 
+   scale_colour_discrete(guide = FALSE) +
+  scale_fill_discrete(guide = FALSE) + 
+  #ggplot2::annotate('text', x = (max(data$yi) + (max(data$yi)*0.10)), y = (seq(1, group_no, 1)+0.3), label= paste("italic(k)==", mod_table$K), parse = TRUE, hjust = "right", size = 3.5)
+```
+
 #### Female fitness is less compromised in species with reversed sexual size dimorphism (SSD)
@@
 
-```{r SSD, fig.width=6, fig.height=4.5}
+```{r SSD, fig.width=6, fig.height=4.5, fig.cap="Sex dimorphism"}
 p3 = ggplot(data, aes(x = SSD_lnRR, y = SMDH, size = 1/sqrt(v_SMDH))) + 

### 2021-05-01 R/func.R
New function for PI's and also updated Ms to make this work so we have them for plotting

@@ -40,3 +40,20 @@ make_table <- function(model,  heteroTable){
   
   return(tmp)
 }
+
+pred_interval <- function(model, tval){
+
+  test.stat <- abs(tval)
+  
+    sigmas <- sum(model$sigma2)
+        PI <- test.stat * sqrt(model$se^2 + sigmas)
+  
+    tmp <- data.frame (Est = model$beta,
+                        SE = model$se,
+                        lwr.CI = model$ci.lb,
+                         up.CI = model$ci.ub,
+                        lower.PI = model$beta - PI,
+                        upper.PI = model$beta + PI)
+  
+  return(tmp)
+}

### 2021-05-03 R/func.R
Added in a new p-value function to make it a little prettier

@@ -57,3 +57,12 @@ pred_interval <- function(model, tval){
   
   return(tmp)
 }
+
+
+p_value <- function(x){
+  if(x <= 0.0001) {tmp = "< 0.0001"}
+  if(x <= 0.001 & x >= 0.0001) {tmp ="< 0.001"}
+  if(x <= 0.01 & x >= 0.001) {tmp ="< 0.01"}
+  if(x >= 0.01) {tmp = round(x, digits =2)}
+  return(tmp)
+}

### 2021-05-03 ms.Rmd
New function for PI's and also updated Ms to make this work so we have them for plotting
Added final touches to first draft, one more ref

@@
 eval(metafor:::.MuMIn)
-source("./R/func.R")
 
@@
 ################
+source("./R/func.R")  
       data <- read.csv("./data/meta_data.csv")
       data <- data %>% 
-              mutate(species2 = species)
+              mutate(species2 = species, 
+                     zSSD = scale(SSD_lnRR))
 
@@
 
-  model1.3 <- rma.mv(SMDH ~ scale(SSD_lnRR), V = data$v_SMDH, 
-                     random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)
-  robust(model1.3, cluster = data$study)
+  # Marginalised model. Just easier to get slope
+  model1.3 <- rma.mv(SMDH ~ zSSD, V = data$v_SMDH, 
+                     random = list(~1|study, ~1|species, ~1|obs), test = "t", data = data)
+  robust_model1.3 <- robust(model1.3, cluster = data$study)
 
-  r2_SSD=r2_ml(model1.3)
+  # Use raw SSD for plotting, so we can ployt raw data, which is easier to interpret
+  model1.3_nonZ <- rma.mv(SMDH ~ SSD_lnRR, V = data$v_SMDH, 
+                     random = list(~1|study, ~1|species, ~1|obs), test = "t", data = data)
+  robust_model1.3_nonZ <- robust(model1.3_nonZ, cluster = data$study)
 
-  model1.4 <- rma.mv(SMDH ~ Harm_type-1, V = data$v_SMDH, 
+        r2_SSD = r2_ml(model1.3)
+
+  model1.4 <- rma.mv(SMDH ~ Harm_type, V = data$v_SMDH, 
                      random = list(~1|study, ~1|species, ~1|obs), test = "t", data = data)
@@
 
-  r2_ml(model1.4)
+  male_harm_r2 = r2_ml(model1.4)
 
   # Model that contains harm type and SSD. Harmtype appears to have different variances, so I'll check whether it is safe to assume homogeneity of variance across groups
-  model1.5 <- rma.mv(SMDH ~  Harm_type + scale(SSD_lnRR), V = data$v_SMDH, 
+  model1.5 <- rma.mv(SMDH ~  Harm_type + zSSD, V = data$v_SMDH, 
                      random = list(~1|study, ~1|obs, ~1|species), test = "t", data = data)
 
-  model1.6 <- rma.mv(SMDH ~ Harm_type + scale(SSD_lnRR), V = data$v_SMDH, 
+  model1.5_nonZ <- rma.mv(SMDH ~ Harm_type + SSD_lnRR, V = data$v_SMDH, 
+                     random = list(~1|study, ~1|species, ~1|obs), test = "t", data = data)
+  robust_model1.5_nonZ <- robust(model1.5_nonZ, cluster = data$study)
+
+  model1.6 <- rma.mv(SMDH ~ Harm_type + zSSD, V = data$v_SMDH, 
                      random = list(~1|study, ~(1 + Harm_type)|obs, ~1|species), 
@@
   robust_model1.5 <- robust(model1.5, cluster = data$study, vcov = "CR2")
-  predict(robust_model1.5)
 
   # Now reparameterize model
-  model1.5_2 <- rma.mv(SMDH ~ 0 + Harm_type + scale(SSD_lnRR), V = data$v_SMDH, 
+  model1.5_2 <- rma.mv(SMDH ~ 0 + Harm_type + zSSD, V = data$v_SMDH, 
                      random = list(~1|study, ~1|obs, ~1|species), test = "t", data = data)
@@
      robust_model1.5_2 <- robust(model1.5_2, cluster = data$study, vcov = "CR2")
+  robust_model1.5_2_PI <- pred_interval(model1.5_2, c(5.1796, -0.6908, 3.0189, 1.9679))
 
-  predict(robust_model1.5, newmods = newdata)
+  # Add N
+  n <- data %>% group_by(Harm_type) %>% summarise(n = n(), nstdy = length(unique(study)))
+  n[4,c(2,3)] <- t(c(dim(data)[1], with(data, length(unique(study)))))
+  robust_model1.5_2_PI$n <- n$n
+  robust_model1.5_2_PI$nstudy <- n$nstdy
 
@@
 # Methods
+#### Standardised Effect Size Measure
+We used the standardised mean difference with a small sample correction (i.e., Hedges' *g*) as our measure of effect size comparing female fitness measures across experimental treatments.
+To correct for the possibility that population variances in the two treatments differ, we made use of a corrected version of Hedges' *g* that controls for heteroscedastic population variances (hereafter called SMDH; [@Bonnet2008; @Bonnett2009]).
+Effect sizes were calculated by subtracting the control group mean from the treatment group mean and dividing by the pooled standard deviation.
+As such, positive effect sizes indicate that female 'fitness/traits' in control groups was higher than female 'fitness/traits' in treatment groups.
 
@@
 To estimate the overall effect of male-harm on female fitness we first fit multi-level meta-analytic models (intercept only) @nakagawa2012methodological.
+We plotted overall meta-analytic means using an orchard plot package @NakaOrchard.
 Overall, we collected between `r n_eff_study[1]` to `r n_eff_study[2]` effect sizes per study.
@@
 We also fit a model that included a species-level random effect with a phylogenetic correlation matrix derived using the Open Tree of Life Database @rotl.
-We used Grafen's method @Grafen to derive branch lengths using the R package *ape* @ape (vers 5.4.1).
+We used Grafen's method @Grafen to calculate branch lengths using the R package *ape* @ape (vers 5.4.1).
 Overall, a model containing only a species-level random effect variance was better supported than a model that estimated a phylogenetic variance ($\Delta_{AIC_{c}}$ = `r dAICc`).
 As such, we did not include phylogeny in our models.
-Study and species-level random effects cannot account for additional sources of within-study non-independence, such as effect sizes derived from common treatment groups or effect sizes derived from different traits measured on the same individuals @Noble2017.
-We therefore applied robust variance estimators (RVEs) to correct standard errors from our models and ensure that our results were robust.
+Study and species-level random effects cannot account for additional sources of within-study non-independence, such as effect sizes calculated from using common treatment groups or for different traits measured on the same individuals @Noble2017.
+We therefore applied robust variance estimators (RVEs) to correct standard errors from our models.
 RVEs have been shown to be robust estimators of standard errors from meta-analytic models when effect sizes within studies are correlated.
-In addition, one does not need to assume or specify how such effects are correlated @Song2021; @NakagawaEcology, making them easier to apply.
+In addition, one does not need to assume, or specify, how such effects are correlated [@Song2021; @NakagawaEcology], making them easier to apply.
 
-Using our MLMA models we estimated effect size heterogenity as $I^2$ @HigginsThompson; @nakagawa2012methodological.
+Using our MLMA models we estimated effect size heterogenity as $I^2$ [@HigginsThompson; @nakagawa2012methodological].
 $I^2_{study}$ and $I^2_{species}$ were the proportion of effect size variance over total variance as a result of between study and species effects, respectively.
@@
 Our models included fixed effects (i.e., moderators) that we *a priori* predicted would impact female fitness.
-More specifically, we predicted that the intensity of sexual selection and sexual conflict would impact how much harm males did to females.
+More specifically, we predicted that the intensity of sexual selection and sexual conflict would affect how much harm males did to females.
 To test these predictions, we included an index of sexual size dimorphism (SSD), which involved taking the log transfomed ratio between male body size to female body size for the species (i.e.,  $log \left( \frac{Male_{body size}}{Female_{bodysize}} \right)$, hereafter referred to as SSD).
@@
 In addition to SSD, we also categorised effect sizes as having come from species with different types of male harm.
-These include species with direct male harm (i.e., species with traumatic insemination) as well as species with indirect male harm (i.e., species that harm females through harrassment).
+These included species with direct male harm (i.e., species with traumatic insemination) as well as species with indirect male harm (i.e., species that harm females through harrassment).
 There are also a number of species where it is clear both direct and indirect forms of male harm exist.
@@
 We compared this model to a homogeneous variance model using $AIC_{c}$.
-Overall, the heterogeneous variance model did not improve overall fit ($\Delta_{AIC_{c}}$ = `r d_aicc_het`), and so, we report on the model assuming homogeneity of variance.
+Overall, the heterogeneous variance model did not improve overall fit ($\Delta_{AIC_{c}}$ = `r d_aicc_het`), and so, we report results from the homogeneity of variance model.
 
@@
 
-```{r funnel, fig.height=5, fig.width=16, fig.cap="A) Funnel plot of effect size as a function of precision (i.e., inverse of sampling standard error).
+```{r funnel, fig.height=7.62500, fig.width=14.90278, fig.cap="A) Funnel plot of effect size as a function of precision (i.e., inverse of sampling standard error).
 B) orchaRd plot of the overall meta-analytic mean efect size, 95% confidnece intervals (thick black bars) and 95% prediction intervals (whiskers)"}
@@
 
-p2 <- orchard_plot(model1.1, mod = "Int", xlab = "SMDH") + scale_colour_manual(values = "grey") + scale_fill_manual(values = "red")
+p2 <- orchard_plot(model1.1, mod = "Int", xlab = "SMDH") + 
+      scale_colour_manual(values = "grey") + 
+      scale_fill_manual(values = "red") +
+      labs(y = "Overall Meta-analytic Mean") +
+      scale_y_discrete(labels = "")
 
@@
 
-Male harm type impacted the overall magnitude of effects.
+Male harm type impacted the overall magnitude of effects explaining `r male_harm_r2[1]*100`% of effect size variance (Figure \@ref(fig:maleharm)).
+Species where mating results in both direct and indirect harm to females have males that significantly impact female fitness (overall meta-analytic mean: `r robust_model1.5_2$beta[1]`, 95% CI: `r robust_model1.5_2$ci.lb[1]` to `r robust_model1.5_2$ci.ub[1]`,  p = `r p_value(robust_model1.5_2$pval[1])`).
+Surprisingly, however, species with direct female harm only (i.e., traumatic insemination), showed a small and opposite effect on female fitness (overall meta-analytic mean: `r robust_model1.5_2$beta[2]`, 95% CI: `r robust_model1.5_2$ci.lb[2]` to `r robust_model1.5_2$ci.ub[2]`; Figure \@ref(fig:maleharm)), however, this effect did not differ significantly from zero (p = `r p_value(robust_model1.5_2$pval[2])`).
+While indirect male harm also resulted in a smaller overall meta-analytic mean relative to species with both, it was still significantly positive (overall meta-analytic mean: `r robust_model1.5_2$beta[3]`, 95% CI: `r robust_model1.5_2$ci.lb[3]` to `r robust_model1.5_2$ci.ub[3]`,  p = `r p_value(robust_model1.5_2$pval[3])`), and only marginally different than species with both direct and indirect male harm (Figure \@ref(fig:maleharm)).
 
-```{r maleharm, fig.width=6, fig.height=4.5}
+```{r maleharm, fig.width=11.56944, fig.height=7.62500, fig.cap="Distribution of effect sizes, overall meta-analytic mean estimates and 95% confidence intervals (CIs) across species with different types of male harm towards females.
+Total effect sizes (n) and total number of studies (k) are provided for each level of Male Harm Type.
+Relevant contrasts between meta-analytic means are provided, along with 95% CIs and significance of contrast."}
 
-ggplot(data, aes(x = Harm_type, y = SMDH, size = 1/sqrt(v_SMDH), fill = Harm_type, colour = Harm_type)) + geom_violin(alpha = 0.2) + geom_point() + 
-  geom_jitter(width = 0.1) + 
-   	#ggplot2::geom_errorbarh(aes(xmin = lowerPR, xmax = upperPR),  height = 0, show.legend = FALSE, size = 0.5, alpha = 0.6) +
-	  	# 95 %CI: branches
-	  #	ggplot2::geom_errorbarh(aes(xmin = lowerCL, xmax = upperCL),  height = 0, show.legend = FALSE, size = 1.2) +
-	  #	ggplot2::geom_vline(xintercept = 0, linetype = 2, colour = "black", alpha = alpha) + 
+# model results
+rownames(robust_model1.5_2_PI) <- 1:dim(robust_model1.5_2_PI)[1]
+robust_model1.5_2_PI$moderator <- c("both", "direct", "indirect", "SSD")
+# remove last row
+robust_model1.5_2_PI <- robust_model1.5_2_PI[1:3,]
+
+# We'll use the contrast model to get what we need to plot stats above comparison bars
+
+contrast1 <- paste0("$\\beta_{contrast}$ = ", round(robust_model1.5$beta[2], digit = 2), ", 95% CI:", round(robust_model1.5$ci.lb[2], digit = 2), " to ", round(robust_model1.5$ci.ub[2], digit = 2), ", $\\textbf{p ", p_value(robust_model1.5$pval[2]), "}$")
+
+contrast2 <- paste0("$\\beta_{contrast}$ = ", round(robust_model1.5$beta[3], digit = 2), ", 95% CI:", round(robust_model1.5$ci.lb[3], digit = 2), " to ", round(robust_model1.5$ci.ub[3], digit = 2), ", p = ", p_value(robust_model1.5$pval[3]))
+
+# When making this plot we are feeding in two different types of data.
+This can be a tad tricky because you need to understand how data is mapped.
+See nice explanation here:https://stackoverflow.com/questions/31069324/adding-points-from-other-dataset-to-ggplot2
+
+harm_plot <- ggplot(data, aes(x = Harm_type, y = SMDH)) + 
+              geom_violin(alpha = 0.2, aes(fill = Harm_type, colour = Harm_type)) + 
+              #geom_point() + don't need this because we have geom_jitter. It will otherwise double plot points
+              ylim(c(-2, 6.5)) + 
+              geom_jitter(aes(x = Harm_type, y = SMDH, fill = Harm_type, colour = Harm_type, size = 1/sqrt(v_SMDH)),
+                          width = 0.08, alpha = 0.2) + 
               theme_bw() + 
@@
 			                     legend.key = element_blank()) + 
-  labs(x = "Harm Type", y = "SMDH", size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$")) +
+              labs(x = "Harm Type", 
+                   y = "SMDH", 
+                   size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$")) +
               scale_x_discrete(labels = c("Both", "Direct", "Indirect")) +
@@
               scale_fill_discrete(guide = FALSE) + 
-  #ggplot2::annotate('text', x = (max(data$yi) + (max(data$yi)*0.10)), y = (seq(1, group_no, 1)+0.3), label= paste("italic(k)==", mod_table$K), parse = TRUE, hjust = "right", size = 3.5)
+              annotate('text', x = (seq(1, 3, 1)), y = 6.45, 
+                       label= paste0("italic(n)==", robust_model1.5_2_PI$n), parse = TRUE, size = 3.5) +     
+              annotate('text', x = (seq(1, 3, 1)), y = 6.15, 
+                       label= paste0("italic(k)==", robust_model1.5_2_PI$nstudy), parse = TRUE, size = 3.5) +     
+        	  	# 95 %CI: branches
+        	    geom_errorbar(data = robust_model1.5_2_PI,  aes(x = moderator, y = Est, ymin = lwr.CI, ymax = up.CI), 
+        	                  height = 0, show.legend = FALSE, size = 0.5, width = 0.05) +
+              geom_point(data = robust_model1.5_2_PI, aes(x = moderator, y = Est, colour= moderator), size = 5)+
+              geom_segment(aes(x = 1, y = 4.8, xend = 2, yend = 4.8), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both")) + 
+              geom_segment(aes(x = 1, y = 5.5, xend = 3, yend = 5.5), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both")) +
+              #geom_segment(aes(x = 2, y = -1, xend = 3, yend = -1), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both"))
+              annotate('text', x = 1 + ((2-1) / 2), y = 5, label = TeX(contrast1), size = 4) + 
+              annotate('text', x = 1 + ((3-1) / 2), y = 5.7, label = TeX(contrast2), size = 4) 
+              #annotate('text', x = 2 + ((2-1) / 2), y = -1, label = TeX(contrast3), size = 2.5)
+
+harm_plot
 ```
 
-#### Female fitness is less compromised in species with reversed sexual size dimorphism (SSD)
+#### Female fitness is less compromised when sexual size dimorphism is low
 
-Species where females are larger than males (i.e., negative SSD) are less impacted by sexual conflict compared to spcies where males and females are closer in size or males are larger (i.e., SSD > 0) (z-transformed $\beta_{SSD}$ = `r model1.3$beta[2]`, 95% CI = `r model1.3$ci.lb[2]` to `r model1.3$ci.ub[2]`, Figure \@ref(fig:SSD) , $R^2_{marginal}$ = `r r2_SSD[1]*100`% of effect size variation).
+As males and females of a species become more similar in size (i.e., increasing SSD index converging on 0) female fitness is more negatively impacted when increasing male harm (i.e., larger fitness decrease observed in treatmemt group or a more positive effect size) (unstandardised slope, $\beta_{SSD}$ = `r robust_model1.5_nonZ$beta[4]`, 95% CI = `r robust_model1.5_nonZ$ci.lb[4]` to `r robust_model1.5_nonZ$ci.ub[4]`,  $R^2_{marginal}$ = `r r2_SSD[1]*100`% of effect size variation; Figure \@ref(fig:SSD)).
+However, the magnitude of slope was marginally non-significant (p = `r p_value(robust_model1.5$pval[4])`).
+Interestingly, this pattern qualitatively appears to reverse in species where females are larger than males (i.e., SSD > 0; Figure \@ref(fig:SSD)), however, there is only one species where SSD is greater than 0 (i.e., *Idotea balthica*), making any broad conclusions quantitatively premature.
 
-```{r SSD, fig.width=6, fig.height=4.5, fig.cap="Sex dimorphism"}
-p3 = ggplot(data, aes(x = SSD_lnRR, y = SMDH, size = 1/sqrt(v_SMDH))) + 
-    geom_point() + 
+```{r SSD, fig.width=11.56944, fig.height=7.62500, fig.cap="Relationship between index of sexual size dimorphism for species (log(male/female)) and effect sizes (i.e., Heteroscedastic Standardised Mean Differences (SMDH)).
+Note that we provide an estimate of stndardised slope (from a model with z-transformed SSD index), along with 95% CIs and significance.
+A slope from a model using unstandardised SSD index is plotted along with raw data for ease of interpretation and is provided in text."}
+contrast3top <- paste0("Standardised $\\beta_{SSD}$ = ", round(robust_model1.5$beta[4], digit = 2)) 
+contrast3bottom <- paste0("95% CI: ", round(robust_model1.5$ci.lb[4], digit = 2), " to ", round(robust_model1.5$ci.ub[4], digit = 2))
+contrast3bottom2 <- paste0("p = ", p_value(robust_model1.5$pval[4]))
+
+p3 = ggplot(data, aes(x = SSD_lnRR, y = SMDH, size = 1/sqrt(v_SMDH), colour = Harm_type)) + 
+    geom_point(alpha = 0.6) + 
       theme_bw() + 
@@
 	     y = "SMDH",
-	  size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$")) +
-	guides(size = guide_legend(direction = "vertical"))
+	  size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$"),
+	  colour = "Male Harm Type") +
+  scale_colour_discrete(labels = c("Both", "Direct", "Indirect")) +
+	guides(size = guide_legend(direction = "vertical")) +
+  annotate('text', x = -0.4, y = 4.5, label = TeX(contrast3top), size = 5) +
+  annotate('text', x = -0.4, y = 4.2, label = TeX(contrast3bottom), size = 5) +
+  annotate('text', x = -0.4, y = 3.9, label = TeX(contrast3bottom2, italic = TRUE), size = 5) +
+  geom_abline(intercept = robust_model1.3_nonZ$beta[1], slope = robust_model1.3_nonZ$beta[2]) # Note using model1.3 for plotting because this is marginalised across Harm_type.
 

### 2021-05-03 ms.Rmd
MS edits

@@
 As such, we did not include phylogeny in our models.
-Study and species-level random effects cannot account for additional sources of within-study non-independence, such as effect sizes calculated from using common treatment groups or for different traits measured on the same individuals @Noble2017.
+Study and species-level random effects cannot account for additional sources of within-study non-independence, such as effect sizes calculated using common treatment groups or for different traits measured on the same individuals @Noble2017.
 We therefore applied robust variance estimators (RVEs) to correct standard errors from our models.
-RVEs have been shown to be robust estimators of standard errors from meta-analytic models when effect sizes within studies are correlated.
+RVEs have been shown to be excellent estimators of standard errors from meta-analytic models when effect sizes within studies are correlated.
 In addition, one does not need to assume, or specify, how such effects are correlated [@Song2021; @NakagawaEcology], making them easier to apply.
 
-Using our MLMA models we estimated effect size heterogenity as $I^2$ [@HigginsThompson; @nakagawa2012methodological].
-$I^2_{study}$ and $I^2_{species}$ were the proportion of effect size variance over total variance as a result of between study and species effects, respectively.
-$I^2_{total}$ was calculated as the proportion of total effect size variance after accounting for, or removing, total sampling variance.
+Using our MLMA models we also calculated effect size heterogenity using $I^2$ [@HigginsThompson; @nakagawa2012methodological].
+$I^2_{study}$ and $I^2_{species}$ are defined as the proportion of effect size variance over total variance as a result of between study and species effects, respectively.In contrast, $I^2_{total}$ was calculated as the proportion of total effect size variance after accounting for, or removing, total sampling variance.
 
@@
 To test these predictions, we included an index of sexual size dimorphism (SSD), which involved taking the log transfomed ratio between male body size to female body size for the species (i.e.,  $log \left( \frac{Male_{body size}}{Female_{bodysize}} \right)$, hereafter referred to as SSD).
-Positive SSD values indicate species with larger males compared to females, whereas negative SSD values indicate speceis where females are larger than males.
+Positive SSD values indicate species with larger males compared to females, whereas negative SSD values indicate species where females are larger than males.
 While this does not directly measure the intensity of sexual selection, it is a proxy for it, and has been used in numerous meta-analyses in the past (CITE).
@@
 Correcting for the possibility of missing studies resulted in the overall meta-analytic mean effect size being indistinguisable from zero (Corrected meta-analytic mean: `r model1.1_pub$beta[1]`, 95% CI: `r model1.1_pub$ci.lb[1]` to `r model1.1_pub$ci.ub[1]`).
-It is important recognise that the corrected meta-analytic mean is simply a sensitivity analysis.
-We cannot know for certain whether publication bias treuly exists, and if so, how many missing studies exist.
+These findings suggest that additional empirical studies may change the overall magnitude of effects, possibly showing weaker effects then what is currently published.
 
@@
 However, the magnitude of slope was marginally non-significant (p = `r p_value(robust_model1.5$pval[4])`).
-Interestingly, this pattern qualitatively appears to reverse in species where females are larger than males (i.e., SSD > 0; Figure \@ref(fig:SSD)), however, there is only one species where SSD is greater than 0 (i.e., *Idotea balthica*), making any broad conclusions quantitatively premature.
+Interestingly, this pattern qualitatively appears to reverse in species where females are larger than males (i.e., SSD > 0; Figure \@ref(fig:SSD)), however, there is only one species where SSD is greater than 0 (i.e., *Idotea balthica*), making any concrete conclusions premature.
 

### 2021-05-03 R/data_prep.R
Just changed plot variable

@@ -102,7 +102,7 @@ ggplot(data, aes(x = SSD_lnRR, y = SMDH, size = 1/sqrt(v_SMDH), colour = species
 	 size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$")) 
 
 # Sperm competition
-	ggplot(data, aes(x = Sperm.compet, y = SMDH, size = 1/sqrt(v_SMDH))) + geom_violin() + geom_point() + theme_bw() + labs(x = "Sperm Competition", 
+	ggplot(data, aes(x = SCR.SCI, y = SMDH, size = 1/sqrt(v_SMDH))) + geom_violin() + geom_point() + theme_bw() + labs(x = "Sperm Competition", 
 	 y = "SMDH",
 	 size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$")) 
 

### 2021-05-03 ms.Rmd
Small change
Added some new analyses to tackle Pau's predcitions

@@
 
+  # Marginalised Harmtype        
   model1.4 <- rma.mv(SMDH ~ Harm_type, V = data$v_SMDH, 
@@
   model1.5 <- rma.mv(SMDH ~  Harm_type + zSSD, V = data$v_SMDH, 
-                     random = list(~1|study, ~1|obs, ~1|species), test = "t", data = data)
+                     random = list(~1|study, ~1|obs, ~1|species), test = "t", 
+                     method = "ML", data = data)
 
+  model1.5_inter <- rma.mv(SMDH ~  Harm_type + zSSD + Harm_type:zSSD, V = data$v_SMDH, 
+                     random = list(~1|study, ~1|obs, ~1|species), test = "t", 
+                     method = "ML", data = data)
+
+  # Does SSD effect vary by harm type. No evidence for interaction
+   aicc_ssd_interact <- AICc(model1.5, model1.5_inter)
+  dAICc_ssd_interact <- max(aicc_ssd_interact$AICc) - min(aicc_ssd_interact$AICc)
+
+  # Update models with REML now
+        model1.5 <- update(model1.5, method = "REML" )
+
+  # Non Z transform
   model1.5_nonZ <- rma.mv(SMDH ~ Harm_type + SSD_lnRR, V = data$v_SMDH, 
@@
   robust_model1.5_2_PI$nstudy <- n$nstdy
+
+  # Sperm competition intensity. Use ML because comparing fixed effects. 
+  sperm_data <- data %>% filter(!SCR.SCI == "hermaphrodite" & !is.na(zSSD))
+
+  model1.7_inetr <- rma.mv(SMDH ~  SCR.SCI*zSSD, V = sperm_data$v_SMDH, 
+                     random = list(~1|study, ~1|obs, ~1|species), test = "t", 
+                     method = "ML", data = sperm_data)
+
+  model1.7 <- rma.mv(SMDH ~  SCR.SCI + zSSD, V = sperm_data$v_SMDH, 
+                     random = list(~1|study, ~1|obs, ~1|species), test = "t", 
+                     method = "ML", data = sperm_data)
+
+  # Check for interaction
+   # Compare AICc for each model
+    aicc_1.7 <- AICc(model1.7_inetr, model1.7)
+  d_aicc_1.7 <- max(aicc_1.7$AICc) - min(aicc_1.7$AICc) # Main effect model better supported
+
+  # Robust
+         model1.7 <- update(model1.7, method = "REML")
+  robust_model1.7 <- robust(model1.7, cluster = sperm_data$study, vcov = "CR2")
+
+  model1.7_reparam <- rma.mv(SMDH ~ 0 +  SCR.SCI + zSSD, V = sperm_data$v_SMDH, 
+                     random = list(~1|study, ~1|obs, ~1|species), test = "t", 
+                     method = "REML", data = sperm_data)
+  robust_model1.7_reparam <- robust(model1.7_reparam, cluster = sperm_data$study, vcov = "CR2")
+
+  # Tables
+                n1.7 <- sperm_data %>% group_by(SCR.SCI) %>% summarise(n = n(), nstdy = length(unique(study)), moderator = unique(SCR.SCI))
+      n1.7[3,c(2,3)] <- t(c(dim(data)[1], with(data, length(unique(study)))))
+  robust_model1.7_PI <- pred_interval(robust_model1.7_reparam, c(4.404, 1.88, 2.49)) # Ignore PIs not used and not correct
+  robust_model1.7_PI <- cbind(robust_model1.7_PI, n1.7)
 
@@
 However, the magnitude of slope was marginally non-significant (p = `r p_value(robust_model1.5$pval[4])`).
+In addition, there was no evidence that the effect of SSD varied according to the type of male harm exhibited (i.e., no interaction between Harm Type and SSD; $\Delta_{AIC_{c}}$ =`r dAICc_ssd_interact`, with the main effects model having the lowest $AIC_{c}$).
 Interestingly, this pattern qualitatively appears to reverse in species where females are larger than males (i.e., SSD > 0; Figure \@ref(fig:SSD)), however, there is only one species where SSD is greater than 0 (i.e., *Idotea balthica*), making any concrete conclusions premature.
@@
 
+#### Sperm competition intensity
+
+Species with higher sperm intensity had a tendeny to have significantly larger effect sizes overall (overall meta-analytic mean: `r robust_model1.7_reparam$beta[1]`, 95% CI: `r robust_model1.7_reparam$ci.lb[1]` to `r robust_model1.7_reparam$ci.ub[1]`, p = `r p_value(robust_model1.7_reparam$pval[1])`; Figure \@ref(fig:sperm)).
+
+```{r sperm, fig.width = 7.625, fig.height = 6.750, fig.cap="Species sperm competition intensity and the effect of changes in male harm on female fitness. }
+
+sperm_data <- data %>% filter(!SCR.SCI == "hermaphrodite")
+
+contrast_sperm <- paste0("$\\beta_{contrast}$ = ", round(robust_model1.7$beta[2], digit = 2))
+
+contrast_sperm2 <- paste0("95% CI:", round(robust_model1.7$ci.lb[2], digit = 2), " to ", round(robust_model1.7$ci.ub[2], digit = 2))
+
+contrast_sperm3 <- paste0("p = ", p_value(robust_model1.7$pval[2]))
+
+sperm_plot = ggplot(sperm_data, aes(x = SCR.SCI, y = SMDH)) + 
+              geom_violin(alpha = 0.1, aes(fill = SCR.SCI, colour = SCR.SCI)) + 
+              geom_jitter(aes(x = SCR.SCI, y = SMDH, fill = SCR.SCI, colour = SCR.SCI, size = 1/sqrt(v_SMDH)),
+                          width = 0.08, alpha = 0.1) + 
+              ylim(c(-1.5, 6))+
+              theme_bw() + 
+		          theme(legend.background = element_blank(),
+			                     legend.key = element_blank()) + 
+              labs(x = "Sperm Competition Intensity", 
+                   y = "SMDH", 
+                   size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{SMDH}}}\\right)$")) +
+              #scale_x_discrete(labels = c("Both", "Direct", "Indirect")) +
+              guides(size = guide_legend(override.aes = list(linetype = 0))) + 
+              scale_colour_discrete(guide = FALSE) +
+              scale_fill_discrete(guide = FALSE) + 
+              annotate('text', x = (seq(1, 2, 1)), y = 6, 
+                       label= paste0("italic(n)==", robust_model1.7_PI$n[1:2]), parse = TRUE, size = 3.5) +     
+              annotate('text', x = (seq(1, 2, 1)), y = 5.7, 
+                       label= paste0("italic(k)==", robust_model1.7_PI$nstdy[1:2]), parse = TRUE, size = 3.5) +     
+        	  	# 95 %CI: branches
+        	    geom_errorbar(data = robust_model1.7_PI,  aes(x = moderator, y = Est, ymin = lwr.CI, ymax = up.CI), 
+                            show.legend = FALSE, size = 0.5, width = 0.05) +
+              geom_point(data = robust_model1.7_PI, aes(x = moderator, y = Est, colour= moderator), size = 5) +
+              geom_segment(aes(x = 1, y = 5.3, xend = 2, yend = 5.3), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both")) + 
+  annotate('text', x = 1.5, y = 5, label = TeX(contrast_sperm), size = 3) + 
+    annotate('text', x = 1.5, y = 4.6, label = TeX(contrast_sperm2), size = 3) + 
+    annotate('text', x = 1.5, y = 4.2, label = TeX(contrast_sperm3), size = 3)
+
+sperm_plot
+
+```
 # References

### 2021-05-03 ms.Rmd
Results and methods updated with new analyses and more clarity on what was done

@@
 
+  # Fit het variance model
+  model1.7_het <- rma.mv(SMDH ~ SCR.SCI + zSSD, V = sperm_data$v_SMDH, 
+                     random = list(~1|study, ~(1 + SCR.SCI)|obs, ~1|species), 
+                     rho = 0, struc = "HCS", test = "t", data = sperm_data)
+
+  aicc_1.7_het <- AICc(model1.7_het, model1.7)
+   d_aicc_1.7_het <- max(aicc_1.7_het$AICc) - min(aicc_1.7_het$AICc)
+
   model1.7_reparam <- rma.mv(SMDH ~ 0 +  SCR.SCI + zSSD, V = sperm_data$v_SMDH, 
@@
 To estimate the overall effect of male-harm on female fitness we first fit multi-level meta-analytic models (intercept only) @nakagawa2012methodological.
-We plotted overall meta-analytic means using an orchard plot package @NakaOrchard.
+We plotted overall meta-analytic means using the orchard plot package @NakaOrchard.
 Overall, we collected between `r n_eff_study[1]` to `r n_eff_study[2]` effect sizes per study.
@@
 As such, we did not include phylogeny in our models.
+
 Study and species-level random effects cannot account for additional sources of within-study non-independence, such as effect sizes calculated using common treatment groups or for different traits measured on the same individuals @Noble2017.
@@
 
-In addition to SSD, we also categorised effect sizes as having come from species with different types of male harm.
+In addition to SSD, we also categorised effect sizes as having come from species with different types of male harm and sperm competition intensity (see moderators section).
 These included species with direct male harm (i.e., species with traumatic insemination) as well as species with indirect male harm (i.e., species that harm females through harrassment).
 There are also a number of species where it is clear both direct and indirect forms of male harm exist.
+We also fit seperate models to a two-level categorical moderator describing the sperm competition intensity of the species (i.e, "high" or "low").
+In both these models, we controlled for SSD index, but included z-transformed SSD, such that meta-analytic means in each categorical moderator are for species of average SSD.
+We also accounted for the possibility that SSD might vary dependeing on the specific harm type and sperm competition intensity (i.e., interaction between SSD and Harm type and Sperm competition intensity).
+We evaluated support for interactions by comparing a model including the interaction to a model without it, comparing $AIC_{c}$ between the two models.
+We chose the model with the lowest $AIC_{c}$ if they differed by greater than 2, otherwise, we choose the most parsimonious model.
+All models comparing fixed effects were fit with maximum likelihood for model comparison of fixed effect structure, and then subsequently re-fit with restricted maximum likelihood when the fixed effect structure was identified.
+
 Given that MLMR models assume homogeneity of variances across the levels of categorical moderators, and this assumption appeared to violated when visually inspecting the data (Figure \@ref(fig:maleharm)), we also fit a model that assumed heterogeneous residual variance across the different levels of male harm type moderator (i.e., different residual variance for 'Both', 'Direct' and 'Indirect' male harm type).
 We compared this model to a homogeneous variance model using $AIC_{c}$.
-Overall, the heterogeneous variance model did not improve overall fit ($\Delta_{AIC_{c}}$ = `r d_aicc_het`), and so, we report results from the homogeneity of variance model.
+Overall, the heterogeneous variance models did not improve overall fit (Harm Type: $\Delta_{AIC_{c}}$ = `r d_aicc_het`; Sperm Competition Intensity:  $\Delta_{AIC_{c}}$ = `r d_aicc_1.7_het`), and so, we report results from the homogeneity of variance models.
 
@@
 
-#### Sperm competition intensity
+#### Male harm in species with high sperm competition intensity does not result in radically reduced female fitness
 
-Species with higher sperm intensity had a tendeny to have significantly larger effect sizes overall (overall meta-analytic mean: `r robust_model1.7_reparam$beta[1]`, 95% CI: `r robust_model1.7_reparam$ci.lb[1]` to `r robust_model1.7_reparam$ci.ub[1]`, p = `r p_value(robust_model1.7_reparam$pval[1])`; Figure \@ref(fig:sperm)).
+Species with higher sperm intensity exhibited a significant reduction in female fitness with higher male harm (overall meta-analytic mean: `r robust_model1.7_reparam$beta[1]`, 95% CI: `r robust_model1.7_reparam$ci.lb[1]` to `r robust_model1.7_reparam$ci.ub[1]`, p = `r p_value(robust_model1.7_reparam$pval[1])`), wheras the same was not true of species with low sperm intensity (overall meta-analytic mean: `r robust_model1.7_reparam$beta[2]`, 95% CI: `r robust_model1.7_reparam$ci.lb[2]` to `r robust_model1.7_reparam$ci.ub[2]`, p = `r p_value(robust_model1.7_reparam$pval[2])`) (Figure \@ref(fig:sperm)).
+Overall, there was no significant difference between species deemed to have high sperm intensity compared to those with low sperm intensity (Figure \@ref(fig:sperm)).
 
-```{r sperm, fig.width = 7.625, fig.height = 6.750, fig.cap="Species sperm competition intensity and the effect of changes in male harm on female fitness. }
+```{r sperm, fig.width = 7.625, fig.height = 6.750, fig.cap="Species sperm competition intensity and the effect of changes in male harm on female fitness."}
 
@@
               geom_point(data = robust_model1.7_PI, aes(x = moderator, y = Est, colour= moderator), size = 5) +
-              geom_segment(aes(x = 1, y = 5.3, xend = 2, yend = 5.3), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both")) + 
+              geom_segment(aes(x = 1, y = 5.35, xend = 2, yend = 5.35), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both")) + 
   annotate('text', x = 1.5, y = 5, label = TeX(contrast_sperm), size = 3) + 
@@
 ```
+
 # References

### 2021-06-11 ms.Rmd
New predictions from Pau resulted in a couple more variables added to data, at the species level. A priori models fit

@@
               mutate(species2 = species, 
-                     zSSD = scale(SSD_lnRR))
+                     zSSD = scale(SSD_lnRR),
+                     sex_life = log(M_lifespan / F_lifespan))
 
@@
 
+  # Sex differences in lifespan
+    model1.8 <- rma.mv(SMDH ~ sex_life, V = data$v_SMDH, 
+                       random = list(~1|study, ~1|obs, ~1|species), test = "t", 
+                       method = "REML", data = data)
+    robust_model1.8 <- robust(model1.8, cluster = data$study, vcov = "CR2")
+
+    model1.9 <- rma.mv(SMDH ~ sex_life + zSSD + Harm_type, V = data$v_SMDH, 
+                       random = list(~1|study, ~1|obs, ~1|species), test = "t", 
+                       method = "REML", data = data)
+    robust_model1.9 <- robust(model1.8, cluster = data$study, vcov = "CR2")
+
+  # Female lifespan
+    model1.10 <- rma.mv(SMDH ~ scale(F_LRS), V = data$v_SMDH, 
+                       random = list(~1|study, ~1|obs, ~1|species), test = "t", 
+                       method = "REML", data = data)
+    robust_model1.10 <- robust(model1.9, cluster = data$study, vcov = "CR2")
+
+    model1.11 <- rma.mv(SMDH ~ scale(F_LRS) + Harm_type, V = data$v_SMDH, 
+                       random = list(~1|study, ~1|obs, ~1|species), test = "t", 
+                       method = "REML", data = data)
+    robust_model1.11 <- robust(model1.11, cluster = data$study, vcov = "CR2")
+
   # Tables
@@
 autonum <- officer::run_autonum(seq_id = "tab", pre_label = "Table 1", bkm_all = TRUE)
-ft <- flextable(table1)
-ft <- set_caption(ft,  caption = "Effect size", autonum = autonum)
+ft <- flextable::flextable(table1)
+ft <- flextable::set_caption(ft,  caption = "Effect size", autonum = autonum)
 ft %>%
-  compose(part = "header", j = "n", value = as_paragraph("n", as_sub("effects"))) %>%
-  compose(part = "header", j = "std", value = as_paragraph("n", as_sub("studies"))) %>%
-  compose(part = "header", j = "spp", value = as_paragraph("n", as_sub("species"))) %>%
-  compose(part = "header", j = "est", value = as_paragraph("Meta-analytic mean")) %>%
-  compose(part = "header", j = "CI", value = as_paragraph("95% CI")) %>%
-  compose(part = "header", j = "PI", value = as_paragraph("95% PI")) %>%
-  compose(part = "header", j = "i2_stdy", value = as_paragraph("I", as_sup("2"), as_sub("study"))) %>%
-  compose(part = "header", j = "i2_trait", value = as_paragraph("I", as_sup("2"), as_sub("trait"))) %>%
-  compose(part = "header", j = "i2_species", value = as_paragraph("I", as_sup("2"), as_sub("species"))) %>%
-  compose(part = "header", j = "i2_tot", value = as_paragraph("I", as_sup("2"), as_sub("total")))
+  flextable::compose(part = "header", j = "n", value = as_paragraph("n", as_sub("effects"))) %>%
+  flextable::compose(part = "header", j = "std", value = as_paragraph("n", as_sub("studies"))) %>%
+  flextable::compose(part = "header", j = "spp", value = as_paragraph("n", as_sub("species"))) %>%
+  flextable::compose(part = "header", j = "est", value = as_paragraph("Meta-analytic mean")) %>%
+  flextable::compose(part = "header", j = "CI", value = as_paragraph("95% CI")) %>%
+  flextable::compose(part = "header", j = "PI", value = as_paragraph("95% PI")) %>%
+  flextable::compose(part = "header", j = "i2_stdy", value = as_paragraph("I", as_sup("2"), as_sub("study"))) %>%
+  flextable::compose(part = "header", j = "i2_trait", value = as_paragraph("I", as_sup("2"), as_sub("trait"))) %>%
+  flextable::compose(part = "header", j = "i2_species", value = as_paragraph("I", as_sup("2"), as_sub("species"))) %>%
+  flextable::compose(part = "header", j = "i2_tot", value = as_paragraph("I", as_sup("2"), as_sub("total")))
 

### 2022-05-02 ms.Rmd
Cleaning up and updating code. Could use orchaRd now for much of it and I may instead change.

@@
 eval(metafor:::.MuMIn)
+```
 
-```
 ```{r loaddata, echo = FALSE, results = "hide"}
@@
 ###################
-# Multilevel Meta-analytic Models (intercept only), plus robust variace estimation test.
+# Multilevel Meta-analytic Models (intercept only), plus robust variance estimation test.
 ###################
@@
 
-# Table 1: Effect, confidemce intervals, prediction intervals, heterogenity
+# Table 1: Effect, confidence intervals, prediction intervals, heterogeneity
    hetero_table <- metaAidR::I2(model1.1, v = data$v_SMDH, obs = "obs") # Same as orchaRd::i2_ml(model1.1)    
@@
                               random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)
+   model1.1_pub_full_het <- rma.mv(SMDH ~ sqrt(inv_n_eff) + SSD_lnRR + Harm_type, V = data$v_SMDH, 
+                              random = list(~1|study, ~1|variable, ~1|species, ~Harm_type|obs), rho = 0, 
+                              str = "HCS", test = "t", data = data)
+      AICc(model1.1_pub_full, model1.1_pub_full_het) # Basically the same results so simplify model.
 
@@
 
-  # Use raw SSD for plotting, so we can ployt raw data, which is easier to interpret
+  # Use raw SSD for plotting, so we can plot raw data, which is easier to interpret
   model1.3_nonZ <- rma.mv(SMDH ~ SSD_lnRR, V = data$v_SMDH, 
@@
 
-  # Marginalised Harmtype        
+  # Marginalised Harm type        
   model1.4 <- rma.mv(SMDH ~ Harm_type, V = data$v_SMDH, 
@@
 
-  # Model that contains harm type and SSD. Harmtype appears to have different variances, so I'll check whether it is safe to assume homogeneity of variance across groups
+  # Model that contains harm type and SSD. Harm type appears to have different variances, so I'll check whether it is safe to assume homogeneity of variance across groups
   model1.5 <- rma.mv(SMDH ~  Harm_type + zSSD, V = data$v_SMDH, 
@@
 
-Using our MLMA models we also calculated effect size heterogenity using $I^2$ [@HigginsThompson; @nakagawa2012methodological].
+Using our MLMA models we also calculated effect size heterogeneity using $I^2$ [@HigginsThompson; @nakagawa2012methodological].
 $I^2_{study}$ and $I^2_{species}$ are defined as the proportion of effect size variance over total variance as a result of between study and species effects, respectively.In contrast, $I^2_{total}$ was calculated as the proportion of total effect size variance after accounting for, or removing, total sampling variance.
 
-We explored drivers of effect size heterogenity using multi-level meta-regression (MLMR) models.
+We explored drivers of effect size heterogeneity using multi-level meta-regression (MLMR) models.
 Our models included fixed effects (i.e., moderators) that we *a priori* predicted would impact female fitness.
 More specifically, we predicted that the intensity of sexual selection and sexual conflict would affect how much harm males did to females.
-To test these predictions, we included an index of sexual size dimorphism (SSD), which involved taking the log transfomed ratio between male body size to female body size for the species (i.e.,  $log \left( \frac{Male_{body size}}{Female_{bodysize}} \right)$, hereafter referred to as SSD).
+To test these predictions, we included an index of sexual size dimorphism (SSD), which involved taking the log transformed ratio between male body size to female body size for the species (i.e.,  $log \left( \frac{Male_{body size}}{Female_{bodysize}} \right)$, hereafter referred to as SSD).
 Positive SSD values indicate species with larger males compared to females, whereas negative SSD values indicate species where females are larger than males.
@@
 In addition to SSD, we also categorised effect sizes as having come from species with different types of male harm and sperm competition intensity (see moderators section).
-These included species with direct male harm (i.e., species with traumatic insemination) as well as species with indirect male harm (i.e., species that harm females through harrassment).
+These included species with direct male harm (i.e., species with traumatic insemination) as well as species with indirect male harm (i.e., species that harm females through harassment).
 There are also a number of species where it is clear both direct and indirect forms of male harm exist.
-We also fit seperate models to a two-level categorical moderator describing the sperm competition intensity of the species (i.e, "high" or "low").
+We also fit separate models to a two-level categorical moderator describing the sperm competition intensity of the species (i.e, "high" or "low").
 In both these models, we controlled for SSD index, but included z-transformed SSD, such that meta-analytic means in each categorical moderator are for species of average SSD.
-We also accounted for the possibility that SSD might vary dependeing on the specific harm type and sperm competition intensity (i.e., interaction between SSD and Harm type and Sperm competition intensity).
+We also accounted for the possibility that SSD might vary depending on the specific harm type and sperm competition intensity (i.e., interaction between SSD and Harm type and Sperm competition intensity).
 We evaluated support for interactions by comparing a model including the interaction to a model without it, comparing $AIC_{c}$ between the two models.
@@
 p1 <- ggplot(data, aes(x = SMDH, y = 1 / sqrt(v_SMDH), xmin = -6, xmax = 6)) +
-geom_point(aes(colour = class)) +
+geom_point(aes(colour = class), size = 3) +
 labs(x = "SMDH", 
@@
 
-p2 <- orchard_plot(model1.1, mod = "Int", xlab = "SMDH") + 
+p2 <- orchard_plot(model1.1, mod = "1", group = "species", data = data, xlab = "SMDH") + 
       scale_colour_manual(values = "grey") + 
       scale_fill_manual(values = "red") +
-      labs(y = "Overall Meta-analytic Mean") +
       scale_y_discrete(labels = "")
 
-p1 + p2 + plot_annotation(tag_levels = c('A', 'B'))
-
+p3 <- p1 + p2 + plot_annotation(tag_levels = c('A', 'B'))
+p3
+ggsave(plot = p3, filename = "fig1.png", width = 12, height= 5, path = "./output/figs", units = "in", device="png", dpi = 600)
 ```
 
-```{r pretty_table}
+```{r pretty_table, tab.cap = "Number of effect sizes, studies and species along with overall meta-analytic mean (average SMDH) and 95% confidence (CI) and prediction intervals (PI).
+Heterogeneity estimates and 95% CI's are also provided for study, trait, species and total heterogeneity (excluding sampling variance)"}
 
@@
 ft <- flextable::flextable(table1)
-ft <- flextable::set_caption(ft,  caption = "Effect size", autonum = autonum)
 ft %>%

### 2022-05-02 ms.Rmd
Coding in version numbers so it's autoupdated, remove autochache and ggsave all figures. Small spelling mistakes corrected.

@@
 ```{r setup, include=FALSE}
-  knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
+  knitr::opts_chunk$set(echo = FALSE, cache = FALSE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
   ## numbers >= 10^5 will be denoted in scientific notation,      ## numbers >= 10^5 will be denoted in scientific notation,
@@
   model1.5_2 <- rma.mv(SMDH ~ 0 + Harm_type + zSSD, V = data$v_SMDH, 
-                     random = list(~1|study, ~1|obs, ~1|species), test = "t", data = data)
+                     random = list(~1|study, ~1|obs, ~1|species), dfs = "contain", test = "t", data = data)
 
-     robust_model1.5_2 <- robust(model1.5_2, cluster = data$study, vcov = "CR2")
+     robust_model1.5_2 <- robust(model1.5_2, cluster = data$study)
+
   robust_model1.5_2_PI <- pred_interval(model1.5_2, c(5.1796, -0.6908, 3.0189, 1.9679))
@@
 #### Meta-analysis
-We analysed effect size data using the *metafor* @Metafor (vers 2.4.0) package in R @R (vers 4.0.5).
+We analysed effect size data using the *metafor* @Metafor (vers `utils::packageVersion("metafor")`) package in R @R (vers `r paste0(R.Version()$major, ".", R.Version()$minor)`).
 To estimate the overall effect of male-harm on female fitness we first fit multi-level meta-analytic models (intercept only) @nakagawa2012methodological.
@@
 To control for sources of non-independence, we included study and species-level random effects @Noble2017.
-We also fit a model that included a species-level random effect with a phylogenetic correlation matrix derived using the Open Tree of Life Database @rotl.
-We used Grafen's method @Grafen to calculate branch lengths using the R package *ape* @ape (vers 5.4.1).
+We also fit a model that included a species-level random effect with a phylogenetic correlation matrix derived using the Open Tree of Life Database @rotl (vers `r utils::packageVersion("rotl")`.
+We used Grafen's method @Grafen to calculate branch lengths using the R package *ape* @ape (vers `r utils::packageVersion("ape")`).
 Overall, a model containing only a species-level random effect variance was better supported than a model that estimated a phylogenetic variance ($\Delta_{AIC_{c}}$ = `r dAICc`).
@@
 This strong effect held even when accounting for within-study non-independence (Meta-analytic mean using Robust Variance Estimator: `r robust$beta`, 95% CI: `r robust$ci.lb` to `r robust$ci.ub`).
-However, visual inspection of funnel plot asymmetry suggested evidence for publication bias (i.e., missed effects sizes with low precision when female harm was worse in control treatments) (Figure \@ref(fig:funnel)).
-Evidence for publication bias was confirmed through the identification of a significant slope between effect size and effective sample size ($\beta$ = `r model1.1_pub$beta[2]`, 95% CI: `r model1.1_pub$ci.lb[2]` to `r model1.1_pub$ci.ub[2]`), and this held true when accounting for heterogenity using meta-regression models ($\beta$ =`r model1.1_pub_full$beta[2]`, 95% CI: `r model1.1_pub_full$ci.lb[2]` to `r model1.1_pub_full$ci.ub[2]`).
-Correcting for the possibility of missing studies resulted in the overall meta-analytic mean effect size being indistinguisable from zero (Corrected meta-analytic mean: `r model1.1_pub$beta[1]`, 95% CI: `r model1.1_pub$ci.lb[1]` to `r model1.1_pub$ci.ub[1]`).
-These findings suggest that additional empirical studies may change the overall magnitude of effects, possibly showing weaker effects then what is currently published.
+Visual inspection of funnel plot asymmetry suggested evidence for publication bias (i.e., missed effects sizes with low precision when female harm was worse in control treatments) (Figure \@ref(fig:funnel)), which was confirmed through the identification of a significant slope between effect size and effective sample size ($\beta$ = `r model1.1_pub$beta[2]`, 95% CI: `r model1.1_pub$ci.lb[2]` to `r model1.1_pub$ci.ub[2]`).
+This result held true when accounting for heterogeneity using meta-regression models ($\beta$ =`r model1.1_pub_full$beta[2]`, 95% CI: `r model1.1_pub_full$ci.lb[2]` to `r model1.1_pub_full$ci.ub[2]`).
+Correcting for the possibility of missing studies resulted in the overall meta-analytic mean effect size being indistinguishable from zero (Corrected meta-analytic mean: `r model1.1_pub$beta[1]`, 95% CI: `r model1.1_pub$ci.lb[1]` to `r model1.1_pub$ci.ub[1]`).
+These findings suggest that additional empirical studies may change the overall magnitude of effects, possibly showing weaker effects then what is currently published, however, it is important to recognise that we cannot know for sure what (if anything) is generating such a bias.
 
 When accounting for sampling variance there was high effect size heterogeneity ($I^2_{Total}$ = `r hetero_table$I2_Est.[nrow(hetero_table)]`, 95% CI: `r hetero_table[nrow(hetero_table), "2.5% CI"]` to `r hetero_table[nrow(hetero_table), "97.5% CI"]`) with most variance being the result of between study ($I^2_{Study}$ = `r hetero_table$I2_Est.[1]`, 95% CI: `r hetero_table[1, "2.5% CI"]` to `r hetero_table[1, "97.5% CI"]`) and between species ($I^2_{Species}$ = `r hetero_table$I2_Est.[3]`, 95% CI: `r hetero_table[3, "2.5% CI"]` to `r hetero_table[3, "97.5% CI"]`) effects.
-The trait type and phylogeny explained much less variation overall ($I^2_{Trait}$ = `r hetero_table$I2_Est.[2]`, 95% CI: `r hetero_table[2, "2.5% CI"]` to `r hetero_table[2, "97.5% CI"]`; $I^2_{Phylogeny}$ = `r hetero_table_phylo$I2_Est.[5]`, 95% CI: `r hetero_table_phylo[5, "2.5% CI"]` to `r hetero_table_phylo[5, "97.5% CI"]`).
+The trait type and phylogeny explained much less variation overall ($I^2_{Trait}$ = `r hetero_table$I2_Est.[2]`, 95% CI: `r hetero_table[2, "2.5% CI"]` to `r hetero_table[2, "97.5% CI"]`; $I^2_{Phylogeny}$ = `r hetero_table_phylo$I2_Est.[5]`, 95% CI: `r hetero_table_phylo[5, "2.5% CI"]` to `r hetero_table_phylo[5, "97.5% CI"]`)(Table \@ref(tab:pretty_table).
 
@@
               #annotate('text', x = 2 + ((2-1) / 2), y = -1, label = TeX(contrast3), size = 2.5)
-
+ggsave(plot = harm_plot, filename = "fig2.png", path = "./output/figs", height = 7.416667, width = 13.805556, device = "png", dpi = 600)
 harm_plot
@@
 
+ggsave(plot = p3, filename = "fig3.png", path = "./output/figs", height = 7, width = 10, device = "png", dpi = 600)
 p3
@@
 
-Species with higher sperm intensity exhibited a significant reduction in female fitness with higher male harm (overall meta-analytic mean: `r robust_model1.7_reparam$beta[1]`, 95% CI: `r robust_model1.7_reparam$ci.lb[1]` to `r robust_model1.7_reparam$ci.ub[1]`, p = `r p_value(robust_model1.7_reparam$pval[1])`), wheras the same was not true of species with low sperm intensity (overall meta-analytic mean: `r robust_model1.7_reparam$beta[2]`, 95% CI: `r robust_model1.7_reparam$ci.lb[2]` to `r robust_model1.7_reparam$ci.ub[2]`, p = `r p_value(robust_model1.7_reparam$pval[2])`) (Figure \@ref(fig:sperm)).
+Species with higher sperm intensity exhibited a significant reduction in female fitness with higher male harm (overall meta-analytic mean: `r robust_model1.7_reparam$beta[1]`, 95% CI: `r robust_model1.7_reparam$ci.lb[1]` to `r robust_model1.7_reparam$ci.ub[1]`, p = `r p_value(robust_model1.7_reparam$pval[1])`), whereas the same was not true of species with low sperm intensity (overall meta-analytic mean: `r robust_model1.7_reparam$beta[2]`, 95% CI: `r robust_model1.7_reparam$ci.lb[2]` to `r robust_model1.7_reparam$ci.ub[2]`, p = `r p_value(robust_model1.7_reparam$pval[2])`) (Figure \@ref(fig:sperm)).
 Overall, there was no significant difference between species deemed to have high sperm intensity compared to those with low sperm intensity (Figure \@ref(fig:sperm)).
@@
 
+ggsave(plot = sperm_plot, filename = "fig4.png", path = "./output/figs", height = 7, width = 10, device = "png", dpi = 600)
 sperm_plot

### 2022-05-02 ms.Rmd
Fixing up table rendering. Very odd, but it didn't like the 'pretty_table' chunk label. Or maybe needed a space between caption and tab.cap, but now working.

@@
       number_sections: false
+      tab_caption: yes
+      fig_caption: yes
       reference_docx: template.docx
@@
 ```{r setup, include=FALSE}
-  knitr::opts_chunk$set(echo = FALSE, cache = FALSE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
+  knitr::opts_chunk$set(echo = FALSE, cache = FALSE, message = FALSE, warning = FALSE)
   ## numbers >= 10^5 will be denoted in scientific notation,      ## numbers >= 10^5 will be denoted in scientific notation,
@@
 #### Meta-analysis
-We analysed effect size data using the *metafor* @Metafor (vers `utils::packageVersion("metafor")`) package in R @R (vers `r paste0(R.Version()$major, ".", R.Version()$minor)`).
+We analysed effect size data using the *metafor* @Metafor (vers `r utils::packageVersion("metafor")`) package in R @R (vers `r paste0(R.Version()$major, ".", R.Version()$minor)`).
 To estimate the overall effect of male-harm on female fitness we first fit multi-level meta-analytic models (intercept only) @nakagawa2012methodological.
@@
 When accounting for sampling variance there was high effect size heterogeneity ($I^2_{Total}$ = `r hetero_table$I2_Est.[nrow(hetero_table)]`, 95% CI: `r hetero_table[nrow(hetero_table), "2.5% CI"]` to `r hetero_table[nrow(hetero_table), "97.5% CI"]`) with most variance being the result of between study ($I^2_{Study}$ = `r hetero_table$I2_Est.[1]`, 95% CI: `r hetero_table[1, "2.5% CI"]` to `r hetero_table[1, "97.5% CI"]`) and between species ($I^2_{Species}$ = `r hetero_table$I2_Est.[3]`, 95% CI: `r hetero_table[3, "2.5% CI"]` to `r hetero_table[3, "97.5% CI"]`) effects.
-The trait type and phylogeny explained much less variation overall ($I^2_{Trait}$ = `r hetero_table$I2_Est.[2]`, 95% CI: `r hetero_table[2, "2.5% CI"]` to `r hetero_table[2, "97.5% CI"]`; $I^2_{Phylogeny}$ = `r hetero_table_phylo$I2_Est.[5]`, 95% CI: `r hetero_table_phylo[5, "2.5% CI"]` to `r hetero_table_phylo[5, "97.5% CI"]`)(Table \@ref(tab:pretty_table).
+The trait type and phylogeny explained much less variation overall ($I^2_{Trait}$ = `r hetero_table$I2_Est.[2]`, 95% CI: `r hetero_table[2, "2.5% CI"]` to `r hetero_table[2, "97.5% CI"]`; $I^2_{Phylogeny}$ = `r hetero_table_phylo$I2_Est.[5]`, 95% CI: `r hetero_table_phylo[5, "2.5% CI"]` to `r hetero_table_phylo[5, "97.5% CI"]`) (Table \@ref(tab:table1)).
 
@@
 
-```{r pretty_table, tab.cap = "Number of effect sizes, studies and species along with overall meta-analytic mean (average SMDH) and 95% confidence (CI) and prediction intervals (PI).
+```{r table1, tab.cap = "Number of effect sizes, studies and species along with overall meta-analytic mean (average SMDH) and 95% confidence (CI) and prediction intervals (PI).
 Heterogeneity estimates and 95% CI's are also provided for study, trait, species and total heterogeneity (excluding sampling variance)"}
 
-autonum <- officer::run_autonum(seq_id = "tab", pre_label = "Table 1", bkm_all = TRUE)
+#autonum <- officer::run_autonum(seq_id = "tab", pre_label = "Table 1", bkm_all = TRUE)
 ft <- flextable::flextable(table1)
@@
   flextable::compose(part = "header", j = "i2_species", value = as_paragraph("I", as_sup("2"), as_sub("species"))) %>%
-  flextable::compose(part = "header", j = "i2_tot", value = as_paragraph("I", as_sup("2"), as_sub("total")))
+  flextable::compose(part = "header", j = "i2_tot", value = as_paragraph("I", as_sup("2"), as_sub("total"))) %>% 
+  flextable::font(part = "header", font = "Times") %>% 
+  flextable::font(part = "body", font = "Times") %>% 
+  flextable::fit_to_width(max_width = 8)
 

### 2022-05-02 R/data_prep.R
Remove unneeded code. Update figs

@@ -48,7 +48,6 @@ pacman::p_load(tidyverse, metafor, brms, latex2exp)
 
 # Generate Effect Sizes - Going to use SMDH (Hedges g with heteroscedasticity correction)
 data <- escalc(m1i = X_C, sd1i =sd_C, n1i = N_C, m2i= X_T, sd2i= sd_T, n2i= N_T, data = data, append = TRUE, measure = "SMDH", var.names=c("SMDH","v_SMDH"))
-data <- escalc(m1i = X_C, sd1i =sd_C, n1i = N_C, m2i= X_T, sd2i= sd_T, n2i= N_T, data = data, append = TRUE, measure = "ROM", var.names=c("lnRR","v_lnRR"))
 
 # Clean data up a bit. We don't need all columns
 data <- data %>% 

### 2022-05-02 ms.Rmd
Adding in headers

@@
 ###################
-
+  ###############
+      # SSD
+  ################
   # Marginalised model. Just easier to get slope
@@
 
+  ###############
+      # Harm type
+  ################
   # Marginalised Harm type        
@@
 
+  ###############
+      # Harm type & SSD
+  ################
   # Model that contains harm type and SSD. Harm type appears to have different variances, so I'll check whether it is safe to assume homogeneity of variance across groups
@@
                      method = "ML", data = data)
-
   model1.5_inter <- rma.mv(SMDH ~  Harm_type + zSSD + Harm_type:zSSD, V = data$v_SMDH, 
@@
 
+  ###############
+      # Sperm Intensity
+  ################
   # Sperm competition intensity. Use ML because comparing fixed effects. 
@@
 
+  ###############
+      # Lifespan
+  ################
   # Sex differences in lifespan
@@
 
+  ###############
+      # Final tables
+  ################
   # Tables
@@
 #### Meta-analysis
-We analysed effect size data using the *metafor* @Metafor (vers `r utils::packageVersion("metafor")`) package in R @R (vers `r paste0(R.Version()$major, ".", R.Version()$minor)`).
+We analysed effect size data using the *metafor* @Metafor (vers.
+`r utils::packageVersion("metafor")`) package in R @R (vers.
+`r paste0(R.Version()$major, ".", R.Version()$minor)`).
 To estimate the overall effect of male-harm on female fitness we first fit multi-level meta-analytic models (intercept only) @nakagawa2012methodological.
-We plotted overall meta-analytic means using the orchard plot package @NakaOrchard.
+We plotted overall meta-analytic means using the orchard plot package @NakaOrchard (vers.
+`r utils::packageVersion("orchard")`).
 Overall, we collected between `r n_eff_study[1]` to `r n_eff_study[2]` effect sizes per study.
 To control for sources of non-independence, we included study and species-level random effects @Noble2017.
-We also fit a model that included a species-level random effect with a phylogenetic correlation matrix derived using the Open Tree of Life Database @rotl (vers `r utils::packageVersion("rotl")`.
-We used Grafen's method @Grafen to calculate branch lengths using the R package *ape* @ape (vers `r utils::packageVersion("ape")`).
+We also fit a model that included a species-level random effect with a phylogenetic correlation matrix derived using the Open Tree of Life Database @rotl (vers.
+`r utils::packageVersion("rotl")`).
+We used Grafen's method @Grafen to calculate branch lengths using the R package *ape* @ape (vers.
+`r utils::packageVersion("ape")`).
 Overall, a model containing only a species-level random effect variance was better supported than a model that estimated a phylogenetic variance ($\Delta_{AIC_{c}}$ = `r dAICc`).
@@
 Positive SSD values indicate species with larger males compared to females, whereas negative SSD values indicate species where females are larger than males.
-While this does not directly measure the intensity of sexual selection, it is a proxy for it, and has been used in numerous meta-analyses in the past (CITE).
+While this does not directly measure the intensity of sexual selection it is an intuitive, interpretable metric that is normally distributed around zero [@Harrison2022; @Lovitch1992].
 
@@
 
-#### Female fitness is less compromised when sexual size dimorphism is low
+#### Female fitness is more compromised when sexual size dimorphism is low
 
-As males and females of a species become more similar in size (i.e., increasing SSD index converging on 0) female fitness is more negatively impacted when increasing male harm (i.e., larger fitness decrease observed in treatmemt group or a more positive effect size) (unstandardised slope, $\beta_{SSD}$ = `r robust_model1.5_nonZ$beta[4]`, 95% CI = `r robust_model1.5_nonZ$ci.lb[4]` to `r robust_model1.5_nonZ$ci.ub[4]`,  $R^2_{marginal}$ = `r r2_SSD[1]*100`% of effect size variation; Figure \@ref(fig:SSD)).
+As males and females of a species become more similar in size (i.e., increasing SSD index converging on 0) female fitness is more negatively impacted when increasing male harm (i.e., larger fitness decrease observed in treatment group or a more positive effect size) (unstandardised slope, $\beta_{SSD}$ = `r robust_model1.5_nonZ$beta[4]`, 95% CI = `r robust_model1.5_nonZ$ci.lb[4]` to `r robust_model1.5_nonZ$ci.ub[4]`,  $R^2_{marginal}$ = `r r2_SSD[1]*100`% of effect size variation; Figure \@ref(fig:SSD)).
 However, the magnitude of slope was marginally non-significant (p = `r p_value(robust_model1.5$pval[4])`).

### 2022-05-02 R/func.R
Wrote a plotting function fo Cooks distance

@@ -66,3 +66,12 @@ p_value <- function(x){
   if(x >= 0.01) {tmp = round(x, digits =2)}
   return(tmp)
 }
+
+
+plot.cook <- function(cooksD, model, vals, data){
+  plot(cooksD, xlab = "Effect", ylab = "Cook's Distance")
+  abline(h = 4/model$k.all, col = "red", lty = 4)
+  text(data[as.vector(which(cooksD > 4/model$k.all)), vals], 
+       x = c(1:model$k.all)[which(cooksD > 4/model$k.all)]+5, 
+       y = cooksD[as.vector(which(cooksD > 4/model$k.all))])
+}

### 2022-05-02 ms.Rmd
Adding in some model checks for potential outliers

@@
 
+        # Just some model checks
+         checks = FALSE
+
+         if(checks){
+           hist(residuals(model1.1))
+
+           cd.model1.1 <- cooks.distance(model1.1)
+           plot(cd.model1.1, xlab = "Effect", ylab = "Cook's Distance")
+           abline(h = 4/model1.1$k.all, col = "red", lty = 4)
+        }
 ###################
@@
 
+  # Just some model checks.
+    if(checks){
+           hist(residuals(model1.3))
+
+           cd.model1.3 <- cooks.distance(model1.3)
+           plot.cook(cd.model1.3, model1.3, "obs", data = data)
+        }
   ###############

### 2022-05-03 R/func.R
Fixed function to add values or plot Cook's distance

@@ -68,10 +68,24 @@ p_value <- function(x){
 }
 
 
-plot.cook <- function(cooksD, model, vals, data){
+plot.cook <- function(cooksD, model, vals, type = c("plot", "vals")){
+  type <- match.arg(type)
+  data <- model$data
+  
+  # check data size and Cooks D size match
+  if(dim(data)[1] != length(cooksD)){
+    stop("Rows in data do not match length of Cook's D vector")
+  }
+  
+  if(type == "plot"){
   plot(cooksD, xlab = "Effect", ylab = "Cook's Distance")
   abline(h = 4/model$k.all, col = "red", lty = 4)
-  text(data[as.vector(which(cooksD > 4/model$k.all)), vals], 
+  text(data[which(cooksD > 4/model$k.all), vals], 
        x = c(1:model$k.all)[which(cooksD > 4/model$k.all)]+5, 
        y = cooksD[as.vector(which(cooksD > 4/model$k.all))])
+  }
+  
+  if(type == "vals"){
+    return(data[as.vector(which(cooksD > 4/model$k.all)), vals])
+  }
 }

### 2022-05-03 ms.Rmd
Updated paper woth diagnostic checks and some more nuanced results base don those checks as there appears to be a big outlier in one model at least.

--- 2022-05-02 ms.Rmd
@@
   model1.1 <- rma.mv(SMDH ~ 1, V = data$v_SMDH, 
-                     random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)
+                     random = list(~1|study, ~1|variable, ~1|species, ~1|obs),  dfs = "contain", test = "t", data = data)
     robust <- robust(model1.1, cluster = data$study, vcov = "CR2")
@@
   model1.2 <- rma.mv(SMDH ~ 1, V = data$v_SMDH, 
-                     random = list(~1|study, ~1|variable, ~1|species, ~1|species2, ~1|obs), R = list(species2 = phylogeny), test = "t", data = data)
+                     random = list(~1|study, ~1|variable, ~1|species, ~1|species2, ~1|obs), R = list(species2 = phylogeny),  dfs = "contain", test = "t", data = data)
 
@@
 
+        # Just some model checks
+         checks = FALSE
+
+         if(checks){
+           hist(residuals(model1.1))
+
+           cd.model1.1 <- cooks.distance(model1.1)
+           plot.cook(cd.model1.1, model1.1, vals = "obs")
+
+           vals <- plot.cook(cd.model1.1, model1.1, vals = "obs", type = "vals")
+
+           # results highly robust to outliers removed. Effect size strength increases
+           model1.1_refit <- rma.mv(SMDH ~ 1, V = data$v_SMDH, 
+                     random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data[!data$obs %in% vals,])
+         }
+
 ###################
@@
        model1.1_pub <- rma.mv(SMDH ~ sqrt(inv_n_eff), V = data$v_SMDH, 
-                              random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)
+                              random = list(~1|study, ~1|variable, ~1|species, ~1|obs),  dfs = "contain", test = "t", data = data)
 
   model1.1_pub_full <- rma.mv(SMDH ~ sqrt(inv_n_eff) + SSD_lnRR + Harm_type, V = data$v_SMDH, 
-                              random = list(~1|study, ~1|variable, ~1|species, ~1|obs), test = "t", data = data)
+                              random = list(~1|study, ~1|variable, ~1|species, ~1|obs), dfs = "contain", test = "t", data = data)
    model1.1_pub_full_het <- rma.mv(SMDH ~ sqrt(inv_n_eff) + SSD_lnRR + Harm_type, V = data$v_SMDH, 
                               random = list(~1|study, ~1|variable, ~1|species, ~Harm_type|obs), rho = 0, 
-                              str = "HCS", test = "t", data = data)
+                              str = "HCS",  dfs = "contain", test = "t", data = data)
       AICc(model1.1_pub_full, model1.1_pub_full_het) # Basically the same results so simplify model.
@@
   model1.3 <- rma.mv(SMDH ~ zSSD, V = data$v_SMDH, 
-                     random = list(~1|study, ~1|species, ~1|obs), test = "t", data = data)
-  robust_model1.3 <- robust(model1.3, cluster = data$study)
+                     random = list(~1|study, ~1|species, ~1|obs),  dfs = "contain", test = "t", data = data[complete.cases(data$zSSD),])
+  robust_model1.3 <- robust(model1.3, cluster = data[complete.cases(data$zSSD),"study"])
 
@@
   model1.3_nonZ <- rma.mv(SMDH ~ SSD_lnRR, V = data$v_SMDH, 
-                     random = list(~1|study, ~1|species, ~1|obs), test = "t", data = data)
+                     random = list(~1|study, ~1|species, ~1|obs),  dfs = "contain", test = "t", data = data)
   robust_model1.3_nonZ <- robust(model1.3_nonZ, cluster = data$study)
@@
         r2_SSD = r2_ml(model1.3)
+
+  # Just some model checks.
+    if(checks){
+           hist(residuals(model1.3))
+
+           cd.model1.3 <- cooks.distance(model1.3)
+           plot.cook(cd.model1.3, model1.3, vals = "obs")
+           vals <- plot.cook(cd.model1.3, model1.3, vals = "obs", type = "vals")
+
+           # Removing outliers decrease zSSD effect by 0.10, but still non-significant/
+           model1.3_refit <- rma.mv(SMDH ~ zSSD, V = data$v_SMDH, 
+                     random = list(~1|study, ~1|species, ~1|obs), test = "t", data = data[!data$obs %in% vals,])
+    }
 
@@
   model1.4 <- rma.mv(SMDH ~ Harm_type, V = data$v_SMDH, 
-                     random = list(~1|study, ~1|species, ~1|obs), test = "t", data = data)
-  robust(model1.4, cluster = data$study)
+                     random = list(~1|study, ~1|species, ~1|obs),  dfs = "contain", test = "t", data = data[complete.cases(data$Harm_type),])
+  robust(model1.4, cluster = data[complete.cases(data$Harm_type),"study"])
 
@@
 
+  # Just some model checks.
+    if(checks){
+           hist(residuals(model1.4))
+
+           cd.model1.4 <- cooks.distance(model1.4)
+           plot.cook(cd.model1.4, model1.4, "obs")
+           vals <- plot.cook(cd.model1.4, model1.4, "obs", type = "vals")
+
+         model1.4_refit <- rma.mv(SMDH ~ Harm_type, V = data$v_SMDH, 
+                     random = list(~1|study, ~1|species, ~1|obs),  dfs = "contain", test = "t", data = data[!data$obs %in% vals,])
+
+        }
   ###############
@@
   model1.5 <- rma.mv(SMDH ~  Harm_type + zSSD, V = data$v_SMDH, 
-                     random = list(~1|study, ~1|obs, ~1|species), test = "t", 
-                     method = "ML", data = data)
+                     random = list(~1|study, ~1|obs, ~1|species),  dfs = "contain", test = "t", 
+                     method = "ML", data = data[complete.cases(data$Harm_type, data$zSSD),])
   model1.5_inter <- rma.mv(SMDH ~  Harm_type + zSSD + Harm_type:zSSD, V = data$v_SMDH, 
-                     random = list(~1|study, ~1|obs, ~1|species), test = "t", 
+                     random = list(~1|study, ~1|obs, ~1|species),  dfs = "contain", test = "t", 
                      method = "ML", data = data)
@@
   model1.5_nonZ <- rma.mv(SMDH ~ Harm_type + SSD_lnRR, V = data$v_SMDH, 
-                     random = list(~1|study, ~1|species, ~1|obs), test = "t", data = data)
+                     random = list(~1|study, ~1|species, ~1|obs), dfs = "contain", test = "t", data = data)
   robust_model1.5_nonZ <- robust(model1.5_nonZ, cluster = data$study)
@@
                      random = list(~1|study, ~(1 + Harm_type)|obs, ~1|species), 
-                     rho = 0, struc = "HCS", test = "t", data = data)
+                     rho = 0, struc = "HCS",  dfs = "contain", test = "t", data = data)
 
@@
   # Check robustness of results using sandwich estimator
-  robust_model1.5 <- robust(model1.5, cluster = data$study, vcov = "CR2")
+  robust_model1.5 <- robust(model1.5, cluster = data[complete.cases(data$Harm_type, data$zSSD),"study"], vcov = "CR2")
+
+  # Just some model checks.
+   if(checks){
+           hist(residuals(model1.5))
+
+           cd.model1.5 <- cooks.distance(robust_model1.5)
+           plot.cook(cd.model1.5, robust_model1.5, "obs")
+           vals <- plot.cook(cd.model1.5, robust_model1.5, "obs", type = "vals")
+
+         model1.5_refit <- rma.mv(SMDH ~ Harm_type + zSSD, V = data$v_SMDH, 
+                     random = list(~1|study, ~1|species, ~1|obs), test = "t", data = data[!data$obs %in% vals,])    
+         # But very clear outlier is 136 so remove this first
+         model1.5_refit <- rma.mv(SMDH ~ Harm_type + zSSD, V = data$v_SMDH, 
+                     random = list(~1|study, ~1|species, ~1|obs), test = "t", data = data[!data$obs %in% 136,])    
+   }
 
@@
   model1.7_inetr <- rma.mv(SMDH ~  SCR.SCI*zSSD, V = sperm_data$v_SMDH, 
-                     random = list(~1|study, ~1|obs, ~1|species), test = "t", 
+                     random = list(~1|study, ~1|obs, ~1|species), dfs = "contain", test = "t", 
                      method = "ML", data = sperm_data)
@@
   model1.7 <- rma.mv(SMDH ~  SCR.SCI + zSSD, V = sperm_data$v_SMDH, 
-                     random = list(~1|study, ~1|obs, ~1|species), test = "t", 
+                     random = list(~1|study, ~1|obs, ~1|species), dfs = "contain", test = "t", 
                      method = "ML", data = sperm_data)
@@
 
+  # Just some model checks.
+    if(checks){
+           hist(residuals(model1.7))
+
+           cd.model1.7 <- cooks.distance(model1.7)
+           plot.cook(cd.model1.7, model1.7, "obs")
+           obs <- plot.cook(cd.model1.7, model1.7, "obs",type = "vals")
+
+      # Results are pretty similar without these rows with high Cooks D
+      model1.7_refit <- rma.mv(SMDH ~  SCR.SCI + zSSD, V = sperm_data$v_SMDH, 
+                     random = list(~1|study, ~1|obs, ~1|species), dfs = "contain", test = "t", 
+                     method = "ML", data = sperm_data[!sperm_data$obs %in% obs,])
+        }
+
   model1.7_reparam <- rma.mv(SMDH ~ 0 +  SCR.SCI + zSSD, V = sperm_data$v_SMDH, 
@@
     model1.8 <- rma.mv(SMDH ~ sex_life, V = data$v_SMDH, 
-                       random = list(~1|study, ~1|obs, ~1|species), test = "t", 
+                       random = list(~1|study, ~1|obs, ~1|species), dfs = "contain", test = "t", 
                        method = "REML", data = data)
@@
     model1.9 <- rma.mv(SMDH ~ sex_life + zSSD + Harm_type, V = data$v_SMDH, 
-                       random = list(~1|study, ~1|obs, ~1|species), test = "t", 
+                       random = list(~1|study, ~1|obs, ~1|species), dfs = "contain", test = "t", 
                        method = "REML", data = data)
-    robust_model1.9 <- robust(model1.8, cluster = data$study, vcov = "CR2")
+    robust_model1.9 <- robust(model1.9, cluster = data$study, vcov = "CR2")
 
@@
     model1.10 <- rma.mv(SMDH ~ scale(F_LRS), V = data$v_SMDH, 
-                       random = list(~1|study, ~1|obs, ~1|species), test = "t", 
+                       random = list(~1|study, ~1|obs, ~1|species), dfs = "contain", test = "t", 
                        method = "REML", data = data)
-    robust_model1.10 <- robust(model1.9, cluster = data$study, vcov = "CR2")
+    robust_model1.10 <- robust(model1.10, cluster = data$study, vcov = "CR2")
 
-    model1.11 <- rma.mv(SMDH ~ scale(F_LRS) + Harm_type, V = data$v_SMDH, 
-                       random = list(~1|study, ~1|obs, ~1|species), test = "t", 
+    model1.11 <- rma.mv(SMDH ~ scale(F_LRS) + Harm_type + zSSD, V = data$v_SMDH, 
+                       random = list(~1|study, ~1|obs, ~1|species), dfs = "contain", test = "t", 
                        method = "REML", data = data)
@@
 Experimentally manipulating female harm resulted in a strong decrease in female fitness overall (i.e., positive effect size with control group females having higher fitness than treatment groups: `r model1.1$beta`, 95% CI: `r model1.1$ci.lb` to `r model1.1$ci.ub`, $n_{effects}$ = `r model1.1$k.all`, $n_{study}$ = `r model1.1$s.nlevels[1]`).
-This strong effect held even when accounting for within-study non-independence (Meta-analytic mean using Robust Variance Estimator: `r robust$beta`, 95% CI: `r robust$ci.lb` to `r robust$ci.ub`).
+This effect held even when accounting for within-study non-independence (meta-analytic mean using Robust Variance Estimator: `r robust$beta`, 95% CI: `r robust$ci.lb` to `r robust$ci.ub`).
 Visual inspection of funnel plot asymmetry suggested evidence for publication bias (i.e., missed effects sizes with low precision when female harm was worse in control treatments) (Figure \@ref(fig:funnel)), which was confirmed through the identification of a significant slope between effect size and effective sample size ($\beta$ = `r model1.1_pub$beta[2]`, 95% CI: `r model1.1_pub$ci.lb[2]` to `r model1.1_pub$ci.ub[2]`).
@@
 Correcting for the possibility of missing studies resulted in the overall meta-analytic mean effect size being indistinguishable from zero (Corrected meta-analytic mean: `r model1.1_pub$beta[1]`, 95% CI: `r model1.1_pub$ci.lb[1]` to `r model1.1_pub$ci.ub[1]`).
-These findings suggest that additional empirical studies may change the overall magnitude of effects, possibly showing weaker effects then what is currently published, however, it is important to recognise that we cannot know for sure what (if anything) is generating such a bias.
+These findings suggest that additional empirical studies may change the overall magnitude of effects, possibly showing weaker effects then what is currently published, but our current state of knowledge suggests that female fitness is indeed compromised overall by male harm.
 
@@
 
-#### Negative effects on fitness depend on the type of harm done to females
+#### Negative effects on fitness and the type of harm done to females
 
-Male harm type impacted the overall magnitude of effects explaining `r male_harm_r2[1]*100`% of effect size variance (Figure \@ref(fig:maleharm)).
+Male harm type appeared to impact the overall magnitude of effects explaining `r male_harm_r2[1]*100`% of effect size variance (Figure \@ref(fig:maleharm)).
 Species where mating results in both direct and indirect harm to females have males that significantly impact female fitness (overall meta-analytic mean: `r robust_model1.5_2$beta[1]`, 95% CI: `r robust_model1.5_2$ci.lb[1]` to `r robust_model1.5_2$ci.ub[1]`,  p = `r p_value(robust_model1.5_2$pval[1])`).
@@
 While indirect male harm also resulted in a smaller overall meta-analytic mean relative to species with both, it was still significantly positive (overall meta-analytic mean: `r robust_model1.5_2$beta[3]`, 95% CI: `r robust_model1.5_2$ci.lb[3]` to `r robust_model1.5_2$ci.ub[3]`,  p = `r p_value(robust_model1.5_2$pval[3])`), and only marginally different than species with both direct and indirect male harm (Figure \@ref(fig:maleharm)).
+Regardless, differences among species exhibiting different types of female harm seemed to be driven primarily by
+a single study (Taylor, 2008) on *Drosophila melanogaster* (very high Cook's distance). Removing this effect resulted in no significant difference between harm type categories.
 
@@
 Total effect sizes (n) and total number of studies (k) are provided for each level of Male Harm Type.
-Relevant contrasts between meta-analytic means are provided, along with 95% CIs and significance of contrast."}
+Relevant contrasts between meta-analytic means are provided, along with 95% CIs and significance of contrast.
+Note that this includes all data.
+Removing outlier point from single study results in no different between harm type categories.
+"}
 
@@
 
+#### Species lifespan does not explain patterns in female harm
+Female lifespan or the difference in lifespan between males and females of a species did not explain significant variation in female harm in treatments after controlling for sexual size dimorphism and harm type ($\beta_{lifespan_{f}}$ = `r robust_model1.9$b[2]`, 95% CI: `r robust_model1.9$ci.lb[2]` to `r robust_model1.9$ci.ub[2]`, t = `r robust_model1.9$zval[2]`, df = `r robust_model1.9$dfs`, p = `r robust_model1.9$pval[2]`; $\beta_{lifespan_{\Delta_{m-f}}}$ = `r robust_model1.11$b[2]`, 95% CI: `r robust_model1.11$ci.lb[2]` to `r robust_model1.11$ci.ub[2]`, t = `r robust_model1.11$zval[2]`, df = `r robust_model1.11$dfs`, p = `r robust_model1.11$pval[2]`)
+
 # References

### 2022-06-16 ms.Rmd
Just some re-checks

@@
 ```{r loadpackages, echo = FALSE, results = "hide"}
-  pacman::p_load(tidyverse, metafor, brms, metaAidR, ape, phytools, metaAidR, orchaRd, gt, kableExtra, flextable, patchwork, latex2exp, MuMIn, equatiomatic, magrittr, data.table)
+devtools::install_github("daniel1noble/orchaRd", force = TRUE)
+devtools::install_github("daniel1noble/metaAidR", force = TRUE)
+
+  pacman::p_load(tidyverse, metafor, brms, orchaRd, ape, phytools, metaAidR, orchaRd, gt, kableExtra, flextable, patchwork, latex2exp, MuMIn, equatiomatic, magrittr, data.table)
 eval(metafor:::.MuMIn)
@@
                               str = "HCS",  dfs = "contain", test = "t", data = data)
-      AICc(model1.1_pub_full, model1.1_pub_full_het) # Basically the same results so simplify model.
+      AICc(model1.1_pub_full, model1.1_pub_full_het) # Checked that k = 120 for both models, using same dataset. Basically the same results so simplify model.
 

### 2022-09-19 R/data_prep.R
Updated processing script. is.character instead as it they brought in as characetr now in R by default

@@ -26,8 +26,8 @@ pacman::p_load(tidyverse, metafor, brms, latex2exp)
 
 # Explore a bit more of how much data we have across various moderators
 	data %>% 
-	select_if(is.factor) %>% 
-	select(-c(notes, Dependency_decisions, journal, pg, author, estimated.increase.in.harm, Err_C_Type, Err_T_Type, C_flipped, source)) %>% 
+	select_if(is.character) %>% 
+	dplyr::select(-c(Dependency_decisions, journal, pg, author, estimated.increase.in.harm, Err_C_Type, Err_T_Type, C_flipped, source)) %>% 
 	glimpse %>% summary(.)
 
 # From this it is quite clear that there is not too much use in Parental Care as most don't have care. Most of the data is a direct measure of fitness, which is good. Most data are from oviparous, but sensible split possibly. We can actually reclassify ovoviviparous to oviparous
@@ -110,3 +110,4 @@ ggplot(data, aes(x = SSD_lnRR, y = SMDH, size = 1/sqrt(v_SMDH), colour = species
 ## How that we've had an explore of the data, cleaned up the messiness and checked effect size data we are ready to analyse. Will export final data
 
 	write.csv(data, "./data/meta_data.csv", row.names=FALSE)
+	

### 2022-09-19 R/data_prep.R
Add lifespan to data. Don't want to drop it out

@@ -53,7 +53,7 @@ data <- escalc(m1i = X_C, sd1i =sd_C, n1i = N_C, m2i= X_T, sd2i= sd_T, n2i= N_T,
 
 # Clean data up a bit. We don't need all columns
 data <- data %>% 
-select(obs, study, author, year, class, order, family, genus, species, variable, fitness.estimate, treatment, estimated.increase.in.harm, X_C, sd_C, N_C, X_T, sd_T, N_T, SMDH, v_SMDH, SME_index, Male.measure, Female.measure, SCR.SCI, Sperm.compet, Harm_type, Parental.care , Gestation, depend, shared.control, source)
+select(obs, study, author, year, class, order, family, genus, species, variable, fitness.estimate, treatment, estimated.increase.in.harm, X_C, sd_C, N_C, X_T, sd_T, N_T, SMDH, v_SMDH, SME_index, Male.measure, Female.measure, SCR.SCI, Sperm.compet, Harm_type, Parental.care , Gestation, depend, shared.control, source, M_lifespan, F_lifespan)
 
 # Have a look. Does look like clear evidence for publication bias. 
 ggplot(data, aes(x = SMDH, y = 1 / sqrt(v_SMDH), xmin = -6, xmax = 6)) +

### 2022-09-19 R/data_prep.R
Added sourec to phylo.R

@@ -7,6 +7,7 @@
 pacman::p_load(tidyverse, metafor, brms, latex2exp)
 
 # Load data written from phylogeny script. 
+  source("./R/phylogeny.R")
 	data <- read.csv("./data/meta_data.csv")
 	str(data)
 

### 2022-09-20 R/data_prep.R
Made sure to keep new effect sizes...duh, also got rid of outlier because it was incorrect data so annotated out irrelavant code.

@@ -54,7 +54,7 @@ data <- escalc(m1i = X_C, sd1i =sd_C, n1i = N_C, m2i= X_T, sd2i= sd_T, n2i= N_T,
 
 # Clean data up a bit. We don't need all columns
 data <- data %>% 
-select(obs, study, author, year, class, order, family, genus, species, variable, fitness.estimate, treatment, estimated.increase.in.harm, X_C, sd_C, N_C, X_T, sd_T, N_T, SMDH, v_SMDH, SME_index, Male.measure, Female.measure, SCR.SCI, Sperm.compet, Harm_type, Parental.care , Gestation, depend, shared.control, source, M_lifespan, F_lifespan)
+select(obs, study, author, year, class, order, family, genus, species, variable, fitness.estimate, treatment, estimated.increase.in.harm, X_C, sd_C, N_C, X_T, sd_T, N_T, SMDH, v_SMDH, logCVR,v_logCVR, logVR,v_logVR, SME_index, Male.measure, Female.measure, SCR.SCI, Sperm.compet, Harm_type, Parental.care , Gestation, depend, shared.control, source, M_lifespan, F_lifespan)
 
 # Have a look. Does look like clear evidence for publication bias. 
 ggplot(data, aes(x = SMDH, y = 1 / sqrt(v_SMDH), xmin = -6, xmax = 6)) +
@@ -67,7 +67,7 @@ scale_color_grey() +
 theme_bw() 
 
 # Find outlier data.There is a clear outlier, which is study 047. I've got to the original paper and noticed data was extracted from boxplot. SD values were very small for the mean data, suggesting data entry. I re-extracted from raw data which was also presented and SD's are much more sensible and way different from original extraction and conversion from box plot.
-data %>% filter(SMDH >=10) # NOTE: Outlier fixed. Raw data re-extracted as it was not correct.
+#data %>% filter(SMDH >=10) # NOTE: Outlier fixed. Raw data re-extracted as it was not correct.
 
 # What is the correspondence between study and species
 stdy_spp <- data.frame(data %>% group_by(species) %>% summarise(n_stdy = length(unique(study))))

### 2022-09-20 ms.Rmd
Adding section on variation
MLMA Variance analysis added for CVR and VR

@@
 
+#### Variation in female fitness
+
+```{r, variation}
+
+  ###############
+      # Variance in female fitness in harm and control treatment. Use lnCVR and lnVR (Nakagawa et al. 2015). On request of reviewer
+  ################
+
+    ## Overall intercept only models. Note that, for lnCVR, 3 effect sizes are based on non-ratio data so are not defined and are excluded.
+    model1_lnCVR <- rma.mv(logCVR ~ 1, V = v_logCVR, 
+                       random = list(~1|study, ~1|obs, ~1|species), dfs = "contain", test = "t", 
+                       method = "REML", data = data)
+    robust_model1_lnCVR <- robust(model1_lnCVR, cluster = data$study, vcov = "CR2")
+
+    model1_lnVR <- rma.mv(logVR ~ 1, V = v_logVR, 
+                       random = list(~1|study, ~1|obs, ~1|species), dfs = "contain", test = "t", 
+                       method = "REML", data = data)
+    robust_model1_lnVR <- robust(model1_lnVR, cluster = data$study, vcov = "CR2")
+
+    orchard_plot(model1_lnCVR, group = "study", data = data, 
+                 xlab = "log Coefficient of Variation (lnCVR)") + 
+    labs(x = "Overall Mean Estimate")
+  ###############
+      # Final tables
+  ################
+  # Tables
+                n1.7 <- sperm_data %>% group_by(SCR.SCI) %>% summarise(n = n(), nstdy = length(unique(study)), moderator = unique(SCR.SCI))
+      n1.7[3,c(2,3)] <- t(c(dim(data)[1], with(data, length(unique(study)))))
+  robust_model1.7_PI <- pred_interval(robust_model1.7_reparam, c(4.404, 1.88, 2.49)) # Ignore PIs not used and not correct
+  robust_model1.7_PI <- cbind(robust_model1.7_PI, n1.7)
+
+```
+
 # References

### 2022-09-26 ms.Rmd
Update ms.Rmd

@@
   ################
+   ## First, have a look at mean-variance relationships. Pretty strong relationship in both Treatment and Control group, as expected. 
+    ggplot(data, aes(x = log(X_T), y = log(sd_T))) + 
+      geom_point(size = 2, col = "black") + 
+      geom_point(aes(x = log(X_C), y = log(sd_C)), col = "grey", size = 2) + 
+      geom_abline() + 
+      labs(x = "log Mean", y = "log SD") + theme_bw()
 

### 2022-10-03 R/func.R
Add Geary's test

@@ -89,3 +89,9 @@ plot.cook <- function(cooksD, model, vals, type = c("plot", "vals")){
     return(data[as.vector(which(cooksD > 4/model$k.all)), vals])
   }
 }
+
+
+# Function to calculate Geary's "number"
+geary <- function(mean, sd, n){
+  (1 / (sd / mean)) * ((4*n)^(3/2) / (1 + 4*n))
+}

### 2022-10-03 ms.Rmd
Add in a Geary's test check that data for logCVR/VR are behaving as assumed

@@
 
+## Geary's test to check normality assumptions
+data <- data %>% 
+         mutate(geary_control = geary(X_C, sd_C, N_C),
+                    geary_trt = geary(X_T, sd_T, N_T),
+                   geary_test = ifelse(geary_control >= 3 & geary_trt >= 3, "pass", "fail"))
+# How many fail?
+    geary_res <- data %>% group_by(geary_test) %>% summarise(n = n()) %>%  data.frame()
+
     ## Overall intercept only models. Note that, for lnCVR, 3 effect sizes are based on non-ratio data so are not defined and are excluded.

### 2022-10-04 ms.Rmd
Adding new plot with lnCVR and lnVR

@@
 
+# Exclude 4 studies that fail test. 3 effects are not defined in anycase
+    data_cvr <- data %>% filter(geary_test == "pass")
+
     ## Overall intercept only models. Note that, for lnCVR, 3 effect sizes are based on non-ratio data so are not defined and are excluded.
     model1_lnCVR <- rma.mv(logCVR ~ 1, V = v_logCVR, 
-                       random = list(~1|study, ~1|obs, ~1|species), dfs = "contain", test = "t", 
-                       method = "REML", data = data)
-    robust_model1_lnCVR <- robust(model1_lnCVR, cluster = data$study, vcov = "CR2")
+                       random = list(~1|study, 
+                                     ~1|obs, 
+                                     ~1|species), 
+                       dfs = "contain", test = "t", 
+                       method = "REML", data = data_cvr)
+    robust_model1_lnCVR <- robust(model1_lnCVR, cluster = data_cvr$study, vcov = "CR2")
 
     model1_lnVR <- rma.mv(logVR ~ 1, V = v_logVR, 
-                       random = list(~1|study, ~1|obs, ~1|species), dfs = "contain", test = "t", 
-                       method = "REML", data = data)
-    robust_model1_lnVR <- robust(model1_lnVR, cluster = data$study, vcov = "CR2")
+                       random = list(~1|study, 
+                                     ~1|obs, 
+                                     ~1|species), 
+                       dfs = "contain", test = "t", 
+                       method = "REML", data = data_cvr)
+    robust_model1_lnVR <- robust(model1_lnVR, cluster = data_cvr$study, vcov = "CR2")
 
-    orchard_plot(model1_lnCVR, group = "study", data = data, 
-                 xlab = "log Coefficient of Variation (lnCVR)") + 
-    labs(x = "Overall Mean Estimate")
+   p1 <-  orchard_plot(model1_lnCVR, group = "study", data = data_cvr, 
+                 xlab = "log Coefficient of Variation Ratio (lnCVR)") + 
+          labs(x = "Overall Mean Estimate") +
+          theme(axis.text.y = element_blank(),
+                legend.position = 'none')
+   p2 <-  orchard_plot(model1_lnVR, group = "study", data = data_cvr, 
+                 xlab = "log Variance Ratio (lnVR)") + 
+          labs(x = element_blank()) +
+          theme(axis.text.y = element_blank())
+
+   (p1 | p2) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+
   ###############

### 2022-10-04 ms.Rmd
Long dataset

@@
    ## First, have a look at mean-variance relationships. Pretty strong relationship in both Treatment and Control group, as expected. 
-    ggplot(data, aes(x = log(X_T), y = log(sd_T))) + 
+p1_1 <-   ggplot(data, aes(x = log(X_T), y = log(sd_T))) + 
       geom_point(size = 2, col = "black") + 
@@
       labs(x = "log Mean", y = "log SD") + theme_bw()
+
+p2_2 <-ggplot(data, aes(x = X_T, y = sd_T)) + 
+      geom_point(size = 2, col = "black") + 
+      geom_point(aes(x = X_C, y = sd_C), col = "grey", size = 2) + 
+      geom_abline() + 
+      labs(x = "Mean", y = "SD") + theme_bw()
+
+(p1_1 | p2_2) + plot_annotation(tag_levels = "A", tag_suffix = ")")
 
@@
 
-# Exclude 4 studies that fail test. 3 effects are not defined in anycase
+# Exclude 4 studies that fail test. 3 effects are not defined in any case
     data_cvr <- data %>% filter(geary_test == "pass")
@@
 
+  # We have a clear relationship bw SD and Mean, especially so on log scale, but raw scale not so much. We should check assumptions of lnCVR analysis
+
+    # First, we need to reorganise the data in long format
+
+    data_long <- data %>% pivot_longer(cols = c(14:19), values_to = "value") %>% 
+                pivot_wider(names_from = grep(name, "sd"), values_from = value, ) %>% data.frame()
+
+    data_long_mean <- data_long %>% filter(grepl("X_", name)) %>% mutate(obs = 1:n())
+      data_long_sd <- data_long %>% filter(grepl("sd_", name)) %>% mutate(obs = 1:n()) %>% select(obs, name, value)
+       data_long_n <- data_long %>% filter(grepl("N_", name)) %>% mutate(obs = 1:n()) %>% select(obs, name, value)
+
+    # Now, merge data sets together.
+
+       final_long1 <- left_join(data_long_mean, data_long_sd, by = "obs")
+        final_long <- left_join(final_long1, data_long_n, by = "obs")
+
    p1 <-  orchard_plot(model1_lnCVR, group = "study", data = data_cvr, 
@@
   ################
-  # Tables
-                n1.7 <- sperm_data %>% group_by(SCR.SCI) %>% summarise(n = n(), nstdy = length(unique(study)), moderator = unique(SCR.SCI))
-      n1.7[3,c(2,3)] <- t(c(dim(data)[1], with(data, length(unique(study)))))
-  robust_model1.7_PI <- pred_interval(robust_model1.7_reparam, c(4.404, 1.88, 2.49)) # Ignore PIs not used and not correct
-  robust_model1.7_PI <- cbind(robust_model1.7_PI, n1.7)
 

### 2022-10-04 ms.Rmd
getting lnSD model up

@@
 
-    data_long <- data %>% pivot_longer(cols = c(14:19), values_to = "value") %>% 
-                pivot_wider(names_from = grep(name, "sd"), values_from = value, ) %>% data.frame()
+    data_long <- data %>% filter(geary_test == "pass") %>%  
+                pivot_longer(cols = c(14:19), values_to = "value", names_to = "name") %>% 
+                data.frame()
 
@@
        final_long1 <- left_join(data_long_mean, data_long_sd, by = "obs")
-        final_long <- left_join(final_long1, data_long_n, by = "obs")
+        final_long <- left_join(final_long1, data_long_n, by = "obs") %>% 
+                      rename("sd" = value.y,
+                             "mean" = value.x,
+                             "n"  = value,
+                             "trt" = name.x) %>% 
+                      mutate(trt = factor(trt))
+
+    # Now that we have it in long format, we can calculate lnSD and lnX and their associated SE's
+
+        final_long <- escalc(sdi = value.y, ni = value,  
+                             measure = "SDLN", data = final_long, 
+                             append = TRUE, var.names=c("lnSD","v_lnSD"))
+
+         final_long <- escalc(mi = value.x, sdi = value.y, ni = value,  
+                              measure = "MNLN", data = final_long, 
+                              append = TRUE, var.names=c("lnX","v_lnX"))
+
+    # Fit a MLMA model with metafor
+        model1_lnSD <- rma.mv(lnSD ~ 1 + name.x + lnX, V = v_lnSD, 
+                       random = list(~1 + name.x|study, 
+                                     ~1|obs, 
+                                     ~1|species), 
+                       dfs = "contain", test = "t", 
+                       method = "REML", data = final_long)
 

### 2022-10-05 ms.Rmd
Fixed lnSD and Al double checked. As I figured, we need to reverse ref level. Slightly confusing, but makes sense

--- 2022-10-04 ms.Rmd
@@
 # Methods
-#### Standardised Effect Size Measure
+#### Standardised Effect Size Measures
 We used the standardised mean difference with a small sample correction (i.e., Hedges' *g*) as our measure of effect size comparing female fitness measures across experimental treatments.
 To correct for the possibility that population variances in the two treatments differ, we made use of a corrected version of Hedges' *g* that controls for heteroscedastic population variances (hereafter called SMDH; [@Bonnet2008; @Bonnett2009]).
-Effect sizes were calculated by subtracting the control group mean from the treatment group mean and dividing by the pooled standard deviation.
+Effect sizes were calculated by subtracting the treatment group mean from the control group mean and dividing by the pooled standard deviation.
 As such, positive effect sizes indicate that female 'fitness/traits' in control groups was higher than female 'fitness/traits' in treatment groups.
+
+We also tested whether the variability in female fitness between the control and treatment group differed.
+To test this question, we used two effect size measures, the log Coefficient of Variation Ratio (lnCVR) that compared the coefficient of variation between control and treatment groups (contrast-based effect size), and the log standard deviation (lnSD), controlling for the log mean (lnX) using an arm-based approach [@nakagawa2015meta].
+Both methods assume a mean-variance relationship, which was clearly evident in our data (see Supp Fig.
+SX).
+However, lnCVR assumes a linear relationship on the natural scale (SD-Mean), whereas lnSD fit using an arm-based approach assumes they are linear on the log scale, but relaxes assumptions about how the mean and variance scale.
 
@@
     # First, we need to reorganise the data in long format
+    data_long <- data %>% filter(geary_test == "pass") %>%  
+                pivot_longer(cols = c(14:19), values_to = "value", names_to = "name") %>% 
+                data.frame()
 
-    data_long <- data %>% pivot_longer(cols = c(14:19), values_to = "value") %>% 
-                pivot_wider(names_from = grep(name, "sd"), values_from = value, ) %>% data.frame()
-
-    data_long_mean <- data_long %>% filter(grepl("X_", name)) %>% mutate(obs = 1:n())
-      data_long_sd <- data_long %>% filter(grepl("sd_", name)) %>% mutate(obs = 1:n()) %>% select(obs, name, value)
-       data_long_n <- data_long %>% filter(grepl("N_", name)) %>% mutate(obs = 1:n()) %>% select(obs, name, value)
+    data_long_mean <- data_long %>% filter(grepl("X_", name))  %>% 
+                      mutate(obs2 = 1:n())
+      data_long_sd <- data_long %>% filter(grepl("sd_", name)) %>% 
+                      mutate(obs2 = 1:n()) %>% 
+                      select(obs2, name, value)
+       data_long_n <- data_long %>% filter(grepl("N_", name))  %>% 
+                      mutate(obs2 = 1:n()) %>% 
+                      select(obs2, name, value)
 
     # Now, merge data sets together.
+Note that, we want to do some renaming and we need to remember that lnCVR is subtracting the CONTROL - TREATMENT, but we need to flip this around in lnSD model because it's TREATMENT - CONTROL.
 
-       final_long1 <- left_join(data_long_mean, data_long_sd, by = "obs")
-        final_long <- left_join(final_long1, data_long_n, by = "obs")
+       final_long1 <- left_join(data_long_mean, data_long_sd, by = "obs2")
+        final_long <- left_join(final_long1, data_long_n, by = "obs2") %>% 
+                      rename("sd" = value.y,
+                             "mean" = value.x,
+                             "n"  = value,
+                             "trt" = name.x) %>% 
+                      mutate(trt = relevel(as.factor(trt), ref = "X_T"),
+                             study.obs = paste0(obs, "_", study))
+
+    # Now that we have it in long format, we can calculate lnSD and lnX and associated SE's for lnSD which can be accounted for in meta-analysis
+
+        final_long <- escalc(sdi = sd, ni = n,  
+                             measure = "SDLN", data = final_long, 
+                             append = TRUE, var.names=c("lnSD","v_lnSD"))
+
+         final_long <- escalc(mi = mean, sdi = sd, ni = n,  
+                              measure = "MNLN", data = final_long, 
+                              append = TRUE, var.names=c("lnX","v_lnX"))
+        # write long_data for checking
+         write.csv(final_long, file = "./data/meta_dat_long.csv", row.names = FALSE)
+
+    # Fit a MLMA model with metafor
+        model1_lnSD <- rma.mv(lnSD ~ 1 + trt + lnX, V = v_lnSD, 
+                       random = list(~1 + trt|study.obs, 
+                                     ~1 | study,
+                                     ~1|obs2, 
+                                     ~1|species), 
+                       dfs = "contain", test = "t", 
+                       method = "REML", data = final_long)
+robust_model1_lnSD <- robust(model1_lnSD, cluster = final_long$study, vcov = "CR2")
 
@@
 
+  data_cvr %>% ggplot(aes(y = 1/ sqrt(v_logCVR), x = mean(logCVR))) + geom_point()
+
 ```

### 2022-10-05 ms.Rmd
Add supp here and MS analysis with lnCVR

@@
 
-We also tested whether the variability in female fitness between the control and treatment group differed.
-To test this question, we used two effect size measures, the log Coefficient of Variation Ratio (lnCVR) that compared the coefficient of variation between control and treatment groups (contrast-based effect size), and the log standard deviation (lnSD), controlling for the log mean (lnX) using an arm-based approach [@nakagawa2015meta].
-Both methods assume a mean-variance relationship, which was clearly evident in our data (see Supp Fig.
-SX).
-However, lnCVR assumes a linear relationship on the natural scale (SD-Mean), whereas lnSD fit using an arm-based approach assumes they are linear on the log scale, but relaxes assumptions about how the mean and variance scale.
+We also tested whether the variability in female fitness between the control and treatment group differed using the log Coefficient of Variation Ratio (lnCVR) that compared the coefficient of variation between control and treatment groups [@nakagawa2015meta].
+Given lnCVR makes certain assumptions about mean-variance relationships which are not always upheld [see @nakagawa2015meta], we also ran an arm-based analysis using the log of the standard deviation (lnSD) in a multilevel meta-analytic model.
+See Supplement.
+Both results provided similar conclusions about the change in variability between control and treatment groups so we only present lnCVR.
+Again, the CV of the control group was subtracted from the CV of the treatment group such that positive effect sizes suggest greater variance in the control group and negative effect sizes greater variability in the treatment group (after controlling for the mean).
 
@@
    ## First, have a look at mean-variance relationships. Pretty strong relationship in both Treatment and Control group, as expected.
-p1_1 <-   ggplot(data, aes(x = log(X_T), y = log(sd_T))) + 
-      geom_point(size = 2, col = "black") + 
-      geom_point(aes(x = log(X_C), y = log(sd_C)), col = "grey", size = 2) + 
-      geom_abline() + 
-      labs(x = "log Mean", y = "log SD") + theme_bw()
-
-p2_2 <-ggplot(data, aes(x = X_T, y = sd_T)) + 
-      geom_point(size = 2, col = "black") + 
-      geom_point(aes(x = X_C, y = sd_C), col = "grey", size = 2) + 
-      geom_abline() + 
-      labs(x = "Mean", y = "SD") + theme_bw()
-
-(p1_1 | p2_2) + plot_annotation(tag_levels = "A", tag_suffix = ")")
 
@@
 
-  data_cvr %>% ggplot(aes(y = 1/ sqrt(v_logCVR), x = mean(logCVR))) + geom_point()
+```
 
+# Supplemental Analysis using lnSD
+
+A number of effect size measures have been proposed to compare changes in variability between two groups.
+@nakagawa2015meta introduced the log Coefficient of Variation Ratio (lnCVR) and log Variance ratio (lnVR) as two key measures.
+lnVR makes no assumptions about mean-variance relationships, however, lnCVR assumes the relationship is linear on the natural scale [@nakagawa2015meta; @Senior2017; @Senior2016].
+It was clear from our data that there was a strong mean-variance relationship (Fig.
+S\@ref(fig:sfig)), as such, we resorted to using lnCVR, particularly because treatments also had a strong effect on the mean (see main analysis).
+
+The lnCVR effect size does have limitations which are not always upheld in practice [@nakagawa2015meta].
+As such, we tested whether these assumptions impacted our inferences by re-running analyses using the log Standard Deviation (lnSD) as our effect size while controlling for log Mean (lnX) using a multilevel meta-regression model using *metafor* (version `r utils::packageVersion("metafor")`) that included lnX along with a two level categorical predictor for treatment (Control vs Treatment) as fixed effects to both control for mean-variance relationship and estimate the effect contrast between control and treatment groups.
+The effect contrast should approximate lnCVR if assumptions are upheld.
+As random effects, we included study, species, and a residual variance (given *metafor* does not include this by default).
+We also included a random slope effects for each control and treatment comparison within a study to model variation across studies in effects.
+
+```{r, fig.align='center', fig.cap= "Mean-variance relationships between the standard deviation (SD) and mean in the control ('grey' points) and treatment groups ('black' points).
+A) Mean-variance relationship on the log scale and B) natural scale."}
+p1_1 <-   ggplot(data, aes(x = log(X_T), y = log(sd_T))) + 
+      geom_point(size = 2, col = "black") + 
+      geom_point(aes(x = log(X_C), y = log(sd_C)), col = "grey", size = 2) + 
+      geom_abline() + 
+      labs(x = "log Mean", y = "log SD") + theme_bw()
+
+p2_2 <-ggplot(data, aes(x = X_T, y = sd_T)) + 
+      geom_point(size = 2, col = "black") + 
+      geom_point(aes(x = X_C, y = sd_C), col = "grey", size = 2) + 
+      geom_abline() + 
+      labs(x = "Mean", y = "SD") + theme_bw()
+
+(p1_1 | p2_2) + plot_annotation(tag_levels = "A", tag_suffix = ")")
 ```

### 2022-10-05 ms.Rmd
Methods on Geary's test

@@
 We also tested whether the variability in female fitness between the control and treatment group differed using the log Coefficient of Variation Ratio (lnCVR) that compared the coefficient of variation between control and treatment groups [@nakagawa2015meta].
-Given lnCVR makes certain assumptions about mean-variance relationships which are not always upheld [see @nakagawa2015meta], we also ran an arm-based analysis using the log of the standard deviation (lnSD) in a multilevel meta-analytic model.
-See Supplement.
+Given lnCVR makes certain assumptions about mean-variance relationships, which are not always upheld [see @nakagawa2015meta], we also ran an 'arm-based' analysis using the log of the standard deviation (lnSD) in a multilevel meta-analytic model.
+See Supplemental Materials for full details.
 Both results provided similar conclusions about the change in variability between control and treatment groups so we only present lnCVR.
-Again, the CV of the control group was subtracted from the CV of the treatment group such that positive effect sizes suggest greater variance in the control group and negative effect sizes greater variability in the treatment group (after controlling for the mean).
+Given lnCVR is a log ratio, we can only use ratio scale data to compute the effect size [@nakagawa2015meta].
+In addition, data is assumed to be normally distributed; we tested this assumption using a modified Geary's test proposed by @laj2011.
+Only 6 effect sizes failed the test, and three of these were not ratio scale data.
+As such, we excluded this from our analysis.
+In all cases, the CV of the control group was subtracted from the CV of the treatment group such that positive effect sizes suggest greater variance in the control group and negative effect sizes greater variability in the treatment group (after controlling for the mean).
 

### 2022-10-05 ms.Rmd
Update MS with models for lnCVR and some new written text.

@@
 ```{r loadpackages, echo = FALSE, results = "hide"}
-devtools::install_github("daniel1noble/orchaRd", force = TRUE)
-devtools::install_github("daniel1noble/metaAidR", force = TRUE)
+#devtools::install_github("daniel1noble/orchaRd", force = TRUE)
+#devtools::install_github("daniel1noble/metaAidR", force = TRUE)
 
@@
   # Female lifespan
-    model1.10 <- rma.mv(SMDH ~ scale(F_LRS), V = data$v_SMDH, 
+    model1.10 <- rma.mv(SMDH ~ scale(F_lifespan), V = data$v_SMDH, 
                        random = list(~1|study, ~1|obs, ~1|species), dfs = "contain", test = "t", 
@@
 
-    model1.11 <- rma.mv(SMDH ~ scale(F_LRS) + Harm_type + zSSD, V = data$v_SMDH, 
+    model1.11 <- rma.mv(SMDH ~ scale(F_lifespan) + Harm_type + zSSD, V = data$v_SMDH, 
                        random = list(~1|study, ~1|obs, ~1|species), dfs = "contain", test = "t", 
@@
 Only 6 effect sizes failed the test, and three of these were not ratio scale data.
-As such, we excluded this from our analysis.
+As such, we excluded these size effect size data from our lnCVR (and lnSD) analysis.
 In all cases, the CV of the control group was subtracted from the CV of the treatment group such that positive effect sizes suggest greater variance in the control group and negative effect sizes greater variability in the treatment group (after controlling for the mean).
@@
 
-Publication bias results when studies with lower statistical power that find opposite patterns to the predicted effects (i.e., male harm increases female fitnes) go unpublished.
+Publication bias results when studies with lower statistical power that find opposite patterns to the predicted effects (i.e., male harm increases female fitness) go unpublished.
 This can result in effects being upwardly biased overall.
 Evidence for publication bias can be roughly detected by inspecting a funnel plot for funnel asymmetry.
-However, any asymmetry identified may simply be the result of high effect size heterogenity.
+However, any asymmetry identified may simply be the result of high effect size heterogeneity.
 As such, to more formally test for publication bias we used a new method that relies on fitting a MLMR model accounting for all the moderators available to explain variation in effects (i.e., all random and fixed effects).
 Using this model, we also include effect size sampling variance as a moderator @NakagawaPubBias.
-This apporach has the benefit of being a formal way to both statistically test for publication bias (while accounting for as much effect size heterogeneity as possible) and correcting for it; providing a sensitivity analysis on how the effect is expected to change if we were to hypothetically observe the missing effects @NakagawaPubBias.
+This approach has the benefit of being a formal way to both statistically test for publication bias (while accounting for as much effect size heterogeneity as possible) and correcting for it; providing a sensitivity analysis on how the effect is expected to change if we were to hypothetically observe the missing effects @NakagawaPubBias.
 It is still important to note that this corrected overall mean should be interpreted with caution.
 We can never know exactly how many studies, if any, are missing.
-As such, these shoud be viewed as a sensitivity analysis.
+As such, these should be viewed as a sensitivity analysis.
+
+```{r, variationanalysis}
+
+  ###############
+      # Variance in female fitness in harm and control treatment. Use lnCVR and lnVR (Nakagawa et al. 2015). On request of reviewer
+  ################
+   ## First, have a look at mean-variance relationships. Pretty strong relationship in both Treatment and Control group, as expected.
+
+## Geary's test to check normality assumptions
+data <- data %>% 
+         mutate(geary_control = geary(X_C, sd_C, N_C),
+                    geary_trt = geary(X_T, sd_T, N_T),
+                   geary_test = ifelse(geary_control >= 3 & geary_trt >= 3, "pass", "fail"))
+# How many fail?
+    geary_res <- data %>% group_by(geary_test) %>% summarise(n = n()) %>%  data.frame()
+
+# Exclude 4 studies that fail test. 3 effects are not defined in any case
+    data_cvr <- data %>% filter(geary_test == "pass")
+
+## Overall intercept only models. Note that, for lnCVR, 3 effect sizes are based on non-ratio data so are not defined and are excluded.
+    model1_lnCVR <- rma.mv(logCVR ~ 1, V = v_logCVR, 
+                       random = list(~1|study, 
+                                     ~1|obs, 
+                                     ~1|species), 
+                       dfs = "contain", test = "t", 
+                       method = "REML", data = data_cvr)
+    robust_model1_lnCVR <- robust(model1_lnCVR, cluster = data_cvr$study, vcov = "CR2")
+
+    model1_lnVR <- rma.mv(logVR ~ 1, V = v_logVR, 
+                       random = list(~1|study, 
+                                     ~1|obs, 
+                                     ~1|species), 
+                       dfs = "contain", test = "t", 
+                       method = "REML", data = data_cvr)
+    robust_model1_lnVR <- robust(model1_lnVR, cluster = data_cvr$study, vcov = "CR2")
+
+  # We have a clear relationship bw SD and Mean, especially so on log scale, but raw scale not so much. We should check assumptions of lnCVR analysis
+
+    # First, we need to reorganise the data in long format
+    data_long <- data %>% filter(geary_test == "pass") %>%  
+                pivot_longer(cols = c(14:19), values_to = "value", names_to = "name") %>% 
+                data.frame()
+
+    data_long_mean <- data_long %>% filter(grepl("X_", name))  %>% 
+                      mutate(obs2 = 1:n())
+      data_long_sd <- data_long %>% filter(grepl("sd_", name)) %>% 
+                      mutate(obs2 = 1:n()) %>% 
+                      select(obs2, name, value)
+       data_long_n <- data_long %>% filter(grepl("N_", name))  %>% 
+                      mutate(obs2 = 1:n()) %>% 
+                      select(obs2, name, value)
+
+    # Now, merge data sets together.
+Note that, we want to do some renaming and we need to remember that lnCVR is subtracting the CONTROL - TREATMENT, but we need to flip this around in lnSD model because it's TREATMENT - CONTROL.
+
+       final_long1 <- left_join(data_long_mean, data_long_sd, by = "obs2")
+        final_long <- left_join(final_long1, data_long_n, by = "obs2") %>% 
+                      rename("sd" = value.y,
+                             "mean" = value.x,
+                             "n"  = value,
+                             "trt" = name.x) %>% 
+                      mutate(trt = relevel(as.factor(trt), ref = "X_T"),
+                             study.obs = paste0(obs, "_", study))
+
+    # Now that we have it in long format, we can calculate lnSD and lnX and associated SE's for lnSD which can be accounted for in meta-analysis
+
+        final_long <- escalc(sdi = sd, ni = n,  
+                             measure = "SDLN", data = final_long, 
+                             append = TRUE, var.names=c("lnSD","v_lnSD"))
+
+         final_long <- escalc(mi = mean, sdi = sd, ni = n,  
+                              measure = "MNLN", data = final_long, 
+                              append = TRUE, var.names=c("lnX","v_lnX"))
+        # write long_data for checking
+         write.csv(final_long, file = "./data/meta_dat_long.csv", row.names = FALSE)
+
+    # Fit a MLMA model with metafor
+        model1_lnSD <- rma.mv(lnSD ~ 1 + trt + lnX, V = v_lnSD, 
+                       random = list(~1 + trt|study.obs, 
+                                     ~1 | study,
+                                     ~1|obs2, 
+                                     ~1|species), 
+                       dfs = "contain", test = "t", 
+                       method = "REML", data = final_long)
+robust_model1_lnSD <- robust(model1_lnSD, cluster = final_long$study, vcov = "CR2")
+
+  ###############
+      # Final tables
+  ################
+
+```
 
@@
 #scale_color_manual(values=c("#999999", "#E69F00", "#56B4E9")) + 
-theme_bw()
+theme_classic()
 
 p2 <- orchard_plot(model1.1, mod = "1", group = "species", data = data, xlab = "SMDH") + 
+      labs(x = "Overall Mean Estimate") +
       scale_colour_manual(values = "grey") + 
       scale_fill_manual(values = "red") +
-      scale_y_discrete(labels = "")
+      scale_y_discrete(labels = "") +
+      theme_classic() +
+      theme(axis.text.y = element_blank())
 
-p3 <- p1 + p2 + plot_annotation(tag_levels = c('A', 'B'))
-p3
-ggsave(plot = p3, filename = "fig1.png", width = 12, height= 5, path = "./output/figs", units = "in", device="png", dpi = 600)
+p3 <-  orchard_plot(model1_lnCVR, group = "species", data = data_cvr, 
+                 xlab = "log Coefficient of Variation Ratio (lnCVR)") + 
+          labs(x = "Overall Mean Estimate") +
+            theme_classic() +
+          theme(axis.text.y = element_blank(),
+                legend.position = 'none')
+
+p4 <- (p1 + (p2 / p3)) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+p4
+ggsave(plot = p4, filename = "fig1.png", width = 12, height= 5, path = "./output/figs", units = "in", device="png", dpi = 600)
 ```
@@
 
-#### Variation in female fitness
-
-```{r, variation}
-
-  ###############
-      # Variance in female fitness in harm and control treatment. Use lnCVR and lnVR (Nakagawa et al. 2015). On request of reviewer
-  ################
-   ## First, have a look at mean-variance relationships. Pretty strong relationship in both Treatment and Control group, as expected.
-
-## Geary's test to check normality assumptions
-data <- data %>% 
-         mutate(geary_control = geary(X_C, sd_C, N_C),
-                    geary_trt = geary(X_T, sd_T, N_T),
-                   geary_test = ifelse(geary_control >= 3 & geary_trt >= 3, "pass", "fail"))
-# How many fail?
-    geary_res <- data %>% group_by(geary_test) %>% summarise(n = n()) %>%  data.frame()
-
-# Exclude 4 studies that fail test. 3 effects are not defined in any case
-    data_cvr <- data %>% filter(geary_test == "pass")
-
-## Overall intercept only models. Note that, for lnCVR, 3 effect sizes are based on non-ratio data so are not defined and are excluded.
-    model1_lnCVR <- rma.mv(logCVR ~ 1, V = v_logCVR, 
-                       random = list(~1|study, 
-                                     ~1|obs, 
-                                     ~1|species), 
-                       dfs = "contain", test = "t", 
-                       method = "REML", data = data_cvr)
-    robust_model1_lnCVR <- robust(model1_lnCVR, cluster = data_cvr$study, vcov = "CR2")
-
-    model1_lnVR <- rma.mv(logVR ~ 1, V = v_logVR, 
-                       random = list(~1|study, 
-                                     ~1|obs, 
-                                     ~1|species), 
-                       dfs = "contain", test = "t", 
-                       method = "REML", data = data_cvr)
-    robust_model1_lnVR <- robust(model1_lnVR, cluster = data_cvr$study, vcov = "CR2")
-
-  # We have a clear relationship bw SD and Mean, especially so on log scale, but raw scale not so much. We should check assumptions of lnCVR analysis
-
-    # First, we need to reorganise the data in long format
-    data_long <- data %>% filter(geary_test == "pass") %>%  
-                pivot_longer(cols = c(14:19), values_to = "value", names_to = "name") %>% 
-                data.frame()
-
-    data_long_mean <- data_long %>% filter(grepl("X_", name))  %>% 
-                      mutate(obs2 = 1:n())
-      data_long_sd <- data_long %>% filter(grepl("sd_", name)) %>% 
-                      mutate(obs2 = 1:n()) %>% 
-                      select(obs2, name, value)
-       data_long_n <- data_long %>% filter(grepl("N_", name))  %>% 
-                      mutate(obs2 = 1:n()) %>% 
-                      select(obs2, name, value)
-
-    # Now, merge data sets together.
-Note that, we want to do some renaming and we need to remember that lnCVR is subtracting the CONTROL - TREATMENT, but we need to flip this around in lnSD model because it's TREATMENT - CONTROL.
-
-       final_long1 <- left_join(data_long_mean, data_long_sd, by = "obs2")
-        final_long <- left_join(final_long1, data_long_n, by = "obs2") %>% 
-                      rename("sd" = value.y,
-                             "mean" = value.x,
-                             "n"  = value,
-                             "trt" = name.x) %>% 
-                      mutate(trt = relevel(as.factor(trt), ref = "X_T"),
-                             study.obs = paste0(obs, "_", study))
-
-    # Now that we have it in long format, we can calculate lnSD and lnX and associated SE's for lnSD which can be accounted for in meta-analysis
-
-        final_long <- escalc(sdi = sd, ni = n,  
-                             measure = "SDLN", data = final_long, 
-                             append = TRUE, var.names=c("lnSD","v_lnSD"))
-
-         final_long <- escalc(mi = mean, sdi = sd, ni = n,  
-                              measure = "MNLN", data = final_long, 
-                              append = TRUE, var.names=c("lnX","v_lnX"))
-        # write long_data for checking
-         write.csv(final_long, file = "./data/meta_dat_long.csv", row.names = FALSE)
-
-    # Fit a MLMA model with metafor
-        model1_lnSD <- rma.mv(lnSD ~ 1 + trt + lnX, V = v_lnSD, 
-                       random = list(~1 + trt|study.obs, 
-                                     ~1 | study,
-                                     ~1|obs2, 
-                                     ~1|species), 
-                       dfs = "contain", test = "t", 
-                       method = "REML", data = final_long)
-robust_model1_lnSD <- robust(model1_lnSD, cluster = final_long$study, vcov = "CR2")
-
-   p1 <-  orchard_plot(model1_lnCVR, group = "study", data = data_cvr, 
-                 xlab = "log Coefficient of Variation Ratio (lnCVR)") + 
-          labs(x = "Overall Mean Estimate") +
-          theme(axis.text.y = element_blank(),
-                legend.position = 'none')
-   p2 <-  orchard_plot(model1_lnVR, group = "study", data = data_cvr, 
-                 xlab = "log Variance Ratio (lnVR)") + 
-          labs(x = element_blank()) +
-          theme(axis.text.y = element_blank())
-
-   (p1 | p2) + plot_annotation(tag_levels = "A", tag_suffix = ")")
-
-  ###############
-      # Final tables
-  ################
-
-```
-
 # Supplemental Analysis using lnSD
@@
 It was clear from our data that there was a strong mean-variance relationship (Fig.
-S\@ref(fig:sfig)), as such, we resorted to using lnCVR, particularly because treatments also had a strong effect on the mean (see main analysis).
+S\@ref(fig:figs1)), as such, we resorted to using lnCVR, particularly because treatments also had a strong effect on the mean (see main analysis).
 
@@
 As random effects, we included study, species, and a residual variance (given *metafor* does not include this by default).
-We also included a random slope effects for each control and treatment comparison within a study to model variation across studies in effects.
+We also included a random slope for each control and treatment comparison within a study to model variation in effects across studies.
 
-```{r, fig.align='center', fig.cap= "Mean-variance relationships between the standard deviation (SD) and mean in the control ('grey' points) and treatment groups ('black' points).
+```{r, figs1, fig.align='center', fig.cap= "Mean-variance relationships between the standard deviation (SD) and mean in the control ('grey' points) and treatment groups ('black' points).
 A) Mean-variance relationship on the log scale and B) natural scale."}

### 2022-10-05 ms.Rmd
Final update for the day

@@
 Only 6 effect sizes failed the test, and three of these were not ratio scale data.
-As such, we excluded these size effect size data from our lnCVR (and lnSD) analysis.
+As such, we excluded these effect size data from our lnCVR (and lnSD) analysis.
 In all cases, the CV of the control group was subtracted from the CV of the treatment group such that positive effect sizes suggest greater variance in the control group and negative effect sizes greater variability in the treatment group (after controlling for the mean).
@@
 
-Experimentally manipulating female harm resulted in a strong decrease in female fitness overall (i.e., positive effect size with control group females having higher fitness than treatment groups: `r model1.1$beta`, 95% CI: `r model1.1$ci.lb` to `r model1.1$ci.ub`, $n_{effects}$ = `r model1.1$k.all`, $n_{study}$ = `r model1.1$s.nlevels[1]`).
+Experimentally manipulating female harm resulted in a strong decrease in female fitness overall (i.e., positive effect size with control group females having higher fitness than treatment groups: `r model1.1$beta`, 95% CI: `r model1.1$ci.lb` to `r model1.1$ci.ub`, $n_{effects}$ = `r model1.1$k.all`, $n_{study}$ = `r model1.1$s.nlevels[1]`) (Figure \@ref(fig:funnel)B).
 This effect held even when accounting for within-study non-independence (meta-analytic mean using Robust Variance Estimator: `r robust$beta`, 95% CI: `r robust$ci.lb` to `r robust$ci.ub`).
+Increased female harm also resulted in significantly higher variance in female fitness (Figure \@ref(fig:funnel)C) with females in treatment groups having an approximately `r (1-predict(model1_lnCVR, transf=exp)$pred)*100`% higher variance in fitness when controlling for the mean (`r model1_lnCVR$beta`, 95% CI: `r model1_lnCVR$ci.lb` to `r model1_lnCVR$ci.ub`, $n_{effects}$ = `r model1_lnCVR$k.all`, $n_{study}$ = `r model1_lnCVR$s.nlevels[1]`).
+
 Visual inspection of funnel plot asymmetry suggested evidence for publication bias (i.e., missed effects sizes with low precision when female harm was worse in control treatments) (Figure \@ref(fig:funnel)), which was confirmed through the identification of a significant slope between effect size and effective sample size ($\beta$ = `r model1.1_pub$beta[2]`, 95% CI: `r model1.1_pub$ci.lb[2]` to `r model1.1_pub$ci.ub[2]`).

### 2022-10-06 ms.Rmd
Add table for lnSD coefs for supplement
Flextbale

@@
 
+ coefs_lnSD <- coef(model1_lnSD)
+ ci.lb_lnSD <- model1_lnSD$ci.lb
+ ci.ub_lnSD <- model1_lnSD$ci.ub
+ randef <- confint(model1_lnSD)
+
+  table_fixed <- data.frame( name = c("Intercept", "Treatment (Control)", "ln Mean"), 
+                            Estimates = coefs_lnSD,
+                       `Upper 95% CI` = ci.ub_lnSD,
+                       `Lower 95% CI` = ci.lb_lnSD, check.names = FALSE, row.names = NULL)
+
+dat <- data.frame()
+
+  for(i in 1:(length(randef)-1)){
+    tmp <- randef[[i]][1]$random[1,]
+    dat <- rbind(dat, tmp)
+  }
+  names(dat) <- c("est", "lb", "up")
+
+  table_rand <- data.frame(     Name = c("Study", "Residual", "Species", "tau^2", "rho"), 
+                                Estimate = dat$est, 
+                           `Upper 95% CI` = dat$lb,
+                           `Lower 95% CI` = dat$up,check.names = FALSE, row.names = NULL)
 ```
@@
 
+```{r, tables1, tab.cap = "Multi-level meta-regression model with log standard deviation (lnSD)"}
+flextable(table_fixed) %>% 
+      add_header_row(values = "Fixed Effects", colwidths = 4) %>% 
+      bold(part = "header", i = 1) %>% 
+      width(j = c(3,4))
+```
+
 # References

### 2022-10-06 ms.Rmd
Added supp table

--- 2022-10-05 ms.Rmd
@@
 
+ coefs_lnSD <- coef(model1_lnSD)
+ ci.lb_lnSD <- model1_lnSD$ci.lb
+ ci.ub_lnSD <- model1_lnSD$ci.ub
+ randef <- confint(model1_lnSD)
+
+  table_fixed <- data.frame( Parameter = c("Intercept", "Treatment (Control)", "ln Mean", ""), 
+                            Estimates = c(coefs_lnSD, ""),
+                       `Upper 95% CI` = c(ci.ub_lnSD, ""),
+                       `Lower 95% CI` = c(ci.lb_lnSD, ""), check.names = FALSE, row.names = NULL)
+
+dat <- data.frame()
+
+  for(i in 1:(length(randef)-1)){
+    tmp <- randef[[i]][1]$random[1,]
+    dat <- rbind(dat, tmp)
+  }
+  names(dat) <- c("est", "lb", "up")
+
+  table_rand <- data.frame(     Parameter = c("Study", "Residual", "Species", "tau^2", "rho"), 
+                                Estimates = dat$est, 
+                           `Upper 95% CI` = dat$lb,
+                           `Lower 95% CI` = dat$up,check.names = FALSE, row.names = NULL)
 ```
@@
 
+```{r, tables1, tab.cap = "Multi-level meta-regression model with log standard deviation (lnSD)"}
+flextable(rbind(table_fixed,table_rand)) %>% 
+      add_header_row(values = "Fixed Effects", colwidths = 3) %>% 
+      bold(part = "header", i = 1) %>% 
+      width(j = c(2,3,4), width = c(5, 2, 2)) %>%
+      align(align = "center", part = "all") %>% 
+      compose(i = 4, j = 3, value = as_paragraph(as_b("Random Effects")))
+
+```
+
 # References

### 2022-10-06 ms.Rmd
Render updates

@@
 flextable(rbind(table_fixed,table_rand)) %>% 
-      add_header_row(values = "Fixed Effects", colwidths = 3) %>% 
+      add_header_row(values = "Fixed Effects", colwidths = 4) %>% 
       bold(part = "header", i = 1) %>% 
@@
       align(align = "center", part = "all") %>% 
-      compose(i = 4, j = 3, value = as_paragraph(as_b("Random Effects")))
+      compose(i = 4, j = 3, value = as_paragraph(as_b("Random Effects"))) %>%
+
+      autofit()
 

### 2022-10-06 ms.Rmd
Ronding data frame

@@
 
-  pacman::p_load(tidyverse, metafor, brms, orchaRd, ape, phytools, metaAidR, orchaRd, gt, kableExtra, flextable, patchwork, latex2exp, MuMIn, equatiomatic, magrittr, data.table)
+  pacman::p_load(tidyverse, metafor, brms, orchaRd, ape, phytools, metaAidR, orchaRd, gt, kableExtra, flextable, patchwork, latex2exp, MuMIn, equatiomatic, magrittr, data.table, forestmangr)
 eval(metafor:::.MuMIn)
@@
 
-  table_fixed <- data.frame( Parameter = c("Intercept", "Treatment (Control)", "ln Mean", ""), 
-                            Estimates = c(coefs_lnSD, ""),
-                       `Upper 95% CI` = c(ci.ub_lnSD, ""),
-                       `Lower 95% CI` = c(ci.lb_lnSD, ""), check.names = FALSE, row.names = NULL)
+  table_fixed <- forestmangr::round_df(data.frame( Parameter = c("Intercept", "Treatment (Control)", "ln Mean", ""), 
+                            Estimates = as.numeric(c(coefs_lnSD, "")),
+                       `Upper 95% CI` = as.numeric(c(ci.ub_lnSD, "")),
+                       `Lower 95% CI` = as.numeric(c(ci.lb_lnSD, "")), check.names = FALSE, row.names = NULL), digits = 3)
 
@@
 
-  table_rand <- data.frame(     Parameter = c("Study", "Residual", "Species", "tau^2", "rho"), 
+  table_rand <- forestmangr::round_df(data.frame(     Parameter = c("Study", "Residual", "Species", "tau^2", "rho"), 
                                 Estimates = dat$est, 
                            `Upper 95% CI` = dat$lb,
-                           `Lower 95% CI` = dat$up,check.names = FALSE, row.names = NULL)
+                           `Lower 95% CI` = dat$up,check.names = FALSE, row.names = NULL), digits = 3)
 ```
@@
 
+Overall, our results were largely consistent with our analysis using lnCVR, with average variability differences being estimated to be approximately similar (See Table S\@ref(tab:tables1)).
+
 ```{r, figs1, fig.align='center', fig.cap= "Mean-variance relationships between the standard deviation (SD) and mean in the control ('grey' points) and treatment groups ('black' points).

### 2022-10-11 ms.Rmd
ms update
Added harmtype model
Adding new lnCVR plot for harmtype

@@
 
+#####################
+# Harm Type Analysis
+#####################
+
+    model1_lnCVR_harm <- rma.mv(logCVR ~ Harm_type, V = v_logCVR, 
+                       random = list(~1|study, 
+                                     ~1|obs, 
+                                     ~1|species), 
+                       dfs = "contain", test = "t", 
+                       method = "REML", data = data_cvr)
+    robust_model1_lnCVR <- robust(model1_lnCVR_harm, cluster = data_cvr$study, vcov = "CR2")
+
+    lncvr_results <- mod_results(robust_model1_lnCVR, mod = "Harm_type", data = data_cvr, group = "species")$mod_table
+
+  # Add N
+  n <- data_cvr %>% group_by(Harm_type) %>% summarise(n = n(), nstdy = length(unique(study)))
+  lncvr_results$n <- n$n
+  lncvr_results$nstudy <- n$nstdy
+  names(lncvr_results)[1] <- "moderator"
   ###############
@@
 This effect held even when accounting for within-study non-independence (meta-analytic mean using Robust Variance Estimator: `r robust$beta`, 95% CI: `r robust$ci.lb` to `r robust$ci.ub`).
+
 Increased female harm also resulted in significantly higher variance in female fitness (Figure \@ref(fig:funnel)C) with females in treatment groups having an approximately `r (1-predict(model1_lnCVR, transf=exp)$pred)*100`% higher variance in fitness when controlling for the mean (`r model1_lnCVR$beta`, 95% CI: `r model1_lnCVR$ci.lb` to `r model1_lnCVR$ci.ub`, $n_{effects}$ = `r model1_lnCVR$k.all`, $n_{study}$ = `r model1_lnCVR$s.nlevels[1]`).
@@
 While indirect male harm also resulted in a smaller overall meta-analytic mean relative to species with both, it was still significantly positive (overall meta-analytic mean: `r robust_model1.5_2$beta[3]`, 95% CI: `r robust_model1.5_2$ci.lb[3]` to `r robust_model1.5_2$ci.ub[3]`,  p = `r p_value(robust_model1.5_2$pval[3])`), and only marginally different than species with both direct and indirect male harm (Figure \@ref(fig:maleharm)).
-Regardless, differences among species exhibiting different types of female harm seemed to be driven primarily by
-a single study (Taylor, 2008) on *Drosophila melanogaster* (very high Cook's distance). Removing this effect resulted in no significant difference between harm type categories.
+Regardless, differences among species exhibiting different types of female harm seemed to be driven primarily by a single study (Taylor, 2008) on *Drosophila melanogaster* (very high Cook's distance).
+Removing this effect resulted in no significant difference between harm type categories.
+
+Harm type did not impact the overall variance in female fitness between control and treatment groups ($F_{2,140}$ = `r model1_lnCVR_harm$QM`, p = `r model1_lnCVR_harm$QMp` - Figure \@ref(fig:maleharm)).
 
@@
               #annotate('text', x = 2 + ((2-1) / 2), y = -1, label = TeX(contrast3), size = 2.5)
+
+harm_plotvar <- ggplot(data_cvr, aes(x = Harm_type, y = logCVR)) + 
+              geom_violin(alpha = 0.2, aes(fill = Harm_type, colour = Harm_type)) + 
+              #geom_point() + don't need this because we have geom_jitter. It will otherwise double plot points
+              ylim(c(-2, 2.5)) + 
+              geom_jitter(aes(x = Harm_type, y = logCVR, fill = Harm_type, colour = Harm_type, size = 1/sqrt(v_logCVR)),
+                          width = 0.08, alpha = 0.2) + 
+              theme_bw() + 
+		          theme(legend.background = element_blank(),
+			                     legend.key = element_blank()) + 
+              labs(x = "Harm Type", 
+                   y = "ln CVR", 
+                   size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{lnCVR}}}\\right)$")) +
+              scale_x_discrete(labels = c("Both", "Direct", "Indirect")) +
+              guides(size = guide_legend(override.aes = list(linetype = 0))) + 
+              scale_colour_discrete(guide = FALSE) +
+              scale_fill_discrete(guide = FALSE) + 
+              annotate('text', x = (seq(1, 3, 1)), y = 2, 
+                       label= paste0("italic(n)==", lncvr_results$n), parse = TRUE, size = 3.5) +     
+              annotate('text', x = (seq(1, 3, 1)), y = 1.8, 
+                       label= paste0("italic(k)==", lncvr_results$nstudy), parse = TRUE, size = 3.5) +     
+        	  	# 95 %CI: branches
+        	    geom_errorbar(data = lncvr_results,  aes(x = moderator, y = estimate, ymin = lowerCL, ymax = upperCL), 
+        	                  height = 0, show.legend = FALSE, size = 0.5, width = 0.05) +
+              geom_point(data = lncvr_results, aes(x = moderator, y = estimate, colour= moderator), size = 5)+
+              geom_segment(aes(x = 1, y = 4.8, xend = 2, yend = 4.8), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both")) + 
+              geom_segment(aes(x = 1, y = 5.5, xend = 3, yend = 5.5), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both")) +
+              #geom_segment(aes(x = 2, y = -1, xend = 3, yend = -1), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both"))
+              annotate('text', x = 1 + ((2-1) / 2), y = 5, label = TeX(contrast1), size = 4) + 
+              annotate('text', x = 1 + ((3-1) / 2), y = 5.7, label = TeX(contrast2), size = 4) 
+              #annotate('text', x = 2 + ((2-1) / 2), y = -1, label = TeX(contrast3), size = 2.5)
+
 ggsave(plot = harm_plot, filename = "fig2.png", path = "./output/figs", height = 7.416667, width = 13.805556, device = "png", dpi = 600)

### 2022-10-12 ms.Rmd
Code annotation a bit better and added fix to lnCVR plot

@@
 
-  ###############
+###################
       # Variance in female fitness in harm and control treatment. Use lnCVR and lnVR (Nakagawa et al. 2015). On request of reviewer
-  ################
+####################
    ## First, have a look at mean-variance relationships. Pretty strong relationship in both Treatment and Control group, as expected.
@@
 
+########################
+    # Overall MLMA model
+#########################    
 ## Overall intercept only models. Note that, for lnCVR, 3 effect sizes are based on non-ratio data so are not defined and are excluded.
@@
 
+########################
+    # Arm-based model
+#########################    
      # We have a clear relationship bw SD and Mean, especially so on log scale, but raw scale not so much. We should check assumptions of lnCVR analysis
@@
                        method = "REML", data = data_cvr)
-    robust_model1_lnCVR <- robust(model1_lnCVR_harm, cluster = data_cvr$study, vcov = "CR2")
+    robust_model1_lnCVR_harm <- robust(model1_lnCVR_harm, cluster = data_cvr$study, vcov = "CR2")
 
-    lncvr_results <- mod_results(robust_model1_lnCVR, mod = "Harm_type", data = data_cvr, group = "species")$mod_table
+    lncvr_results <- mod_results(robust_model1_lnCVR_harm, mod = "Harm_type", data = data_cvr, group = "species")$mod_table
 
@@
   names(lncvr_results)[1] <- "moderator"
+  lncvr_results$loc <- 1:dim(lncvr_results)[1]
+
 ###############
@@
         	  	# 95 %CI: branches
-        	    geom_errorbar(data = lncvr_results,  aes(x = moderator, y = estimate, ymin = lowerCL, ymax = upperCL), 
+        	    geom_errorbar(data = lncvr_results,  aes(x = loc, y = estimate, ymin = lowerCL, ymax = upperCL), 
         	                  height = 0, show.legend = FALSE, size = 0.5, width = 0.05) +
-              geom_point(data = lncvr_results, aes(x = moderator, y = estimate, colour= moderator), size = 5)+
-              geom_segment(aes(x = 1, y = 4.8, xend = 2, yend = 4.8), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both")) + 
-              geom_segment(aes(x = 1, y = 5.5, xend = 3, yend = 5.5), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both")) +
-              #geom_segment(aes(x = 2, y = -1, xend = 3, yend = -1), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both"))
-              annotate('text', x = 1 + ((2-1) / 2), y = 5, label = TeX(contrast1), size = 4) + 
-              annotate('text', x = 1 + ((3-1) / 2), y = 5.7, label = TeX(contrast2), size = 4) 
-              #annotate('text', x = 2 + ((2-1) / 2), y = -1, label = TeX(contrast3), size = 2.5)
+              geom_point(data = lncvr_results, aes(x = loc, y = estimate), size = 5)
 
-ggsave(plot = harm_plot, filename = "fig2.png", path = "./output/figs", height = 7.416667, width = 13.805556, device = "png", dpi = 600)
-harm_plot
+plot <- (harm_plot + harm_plotvar) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+
+ggsave(plot = plot, filename = "fig2.png", path = "./output/figs", height = 7.416667, width = 13.805556, device = "png", dpi = 600)
+plot
 ```

### 2022-10-12 ms.Rmd
Added in contrasts on figure for consistency

@@
 
-```{r maleharm, fig.width=11.56944, fig.height=7.62500, fig.cap="Distribution of effect sizes, overall meta-analytic mean estimates and 95% confidence intervals (CIs) across species with different types of male harm towards females.
+```{r maleharm, fig.width=20.8, fig.height=7.4, fig.cap="Distribution of effect sizes, overall meta-analytic mean estimates and 95% confidence intervals (CIs) across species with different types of male harm towards females.
+A) Standardised Mean Difference with Heteroscedasticity correction (SMDH) and B) the log Coefficient of Variation (lnCVR).
 Total effect sizes (n) and total number of studies (k) are provided for each level of Male Harm Type.
@@
 
-contrast1 <- paste0("$\\beta_{contrast}$ = ", round(robust_model1.5$beta[2], digit = 2), ", 95% CI:", round(robust_model1.5$ci.lb[2], digit = 2), " to ", round(robust_model1.5$ci.ub[2], digit = 2), ", $\\textbf{p ", p_value(robust_model1.5$pval[2]), "}$")
+contrast1 <- paste0("$\\beta_{contrast}$ = ", round(robust_model1.5$beta[2], digit = 2), ", 95% CI:", round(robust_model1.5$ci.lb[2], digit = 2), " to ", round(robust_model1.5$ci.ub[2], digit = 2), ", $\\textbf{p =", p_value(robust_model1.5$pval[2]), "}$")
 
 contrast2 <- paste0("$\\beta_{contrast}$ = ", round(robust_model1.5$beta[3], digit = 2), ", 95% CI:", round(robust_model1.5$ci.lb[3], digit = 2), " to ", round(robust_model1.5$ci.ub[3], digit = 2), ", p = ", p_value(robust_model1.5$pval[3]))
+
+contrast1v <- paste0("$\\beta_{contrast}$ = ", round(robust_model1_lnCVR_harm$beta[2], digit = 2), ", 95% CI:", round(robust_model1_lnCVR_harm$ci.lb[2], digit = 2), " to ", round(robust_model1_lnCVR_harm$ci.ub[2], digit = 2), ", $p =", p_value(robust_model1_lnCVR_harm$pval[2]), "$")
+
+contrast2v <- paste0("$\\beta_{contrast}$ = ", round(robust_model1_lnCVR_harm$beta[3], digit = 2), ", 95% CI:", round(robust_model1.5$ci.lb[3], digit = 2), " to ", round(robust_model1_lnCVR_harm$ci.ub[3], digit = 2), ", p = ", p_value(robust_model1_lnCVR_harm$pval[3]))
 
@@
                           width = 0.08, alpha = 0.2) + 
-              theme_bw() + 
+              theme_classic() + 
 		          theme(legend.background = element_blank(),
@@
 
+lncvr_results$moderator <- c("both", "direct", "indirect")
+
 harm_plotvar <- ggplot(data_cvr, aes(x = Harm_type, y = logCVR)) + 
@@
               labs(x = "Harm Type", 
-                   y = "ln CVR", 
+                   y = "log Coefficient of Variation (lnCVR)", 
                    size = TeX("Precision $\\left(\\frac{1}{\\sqrt{v_{lnCVR}}}\\right)$")) +
@@
         	                  height = 0, show.legend = FALSE, size = 0.5, width = 0.05) +
-              geom_point(data = lncvr_results, aes(x = loc, y = estimate), size = 5)
+              geom_point(data = lncvr_results, aes(x = loc, y = estimate, colour= moderator), size = 5) +
+              geom_segment(aes(x = 1, y = 1, xend = 2, yend = 1), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both")) + 
+              geom_segment(aes(x = 1, y = 1.3, xend = 3, yend = 1.3), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both")) +
+              #geom_segment(aes(x = 2, y = -1, xend = 3, yend = -1), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both"))
+              annotate('text', x = 1 + ((2-1) / 2), y = 1.1, label = TeX(contrast1v), size = 4) + 
+              annotate('text', x = 1 + ((3-1) / 2), y = 1.4, label = TeX(contrast2v), size = 4)
 
@@
     geom_point(alpha = 0.6) + 
-      theme_bw() + 
+      theme_classic() + 
   labs(x = "Sexual Size Dimorphism (SSD) Index", 
@@
               ylim(c(-1.5, 6))+
-              theme_bw() + 
+              theme_classic() + 
 		          theme(legend.background = element_blank(),

### 2022-10-12 ms.Rmd
Revised MS for Pau et al

@@
 `r paste0(R.Version()$major, ".", R.Version()$minor)`).
-To estimate the overall effect of male-harm on female fitness we first fit multi-level meta-analytic models (intercept only) @nakagawa2012methodological.
+To estimate the overall effect of male-harm on female fitness (for both mean and variance) we first fit multi-level meta-analytic models (intercept only) @nakagawa2012methodological.
 We plotted overall meta-analytic means using the orchard plot package @NakaOrchard (vers.
@@
 Using our MLMA models we also calculated effect size heterogeneity using $I^2$ [@HigginsThompson; @nakagawa2012methodological].
-$I^2_{study}$ and $I^2_{species}$ are defined as the proportion of effect size variance over total variance as a result of between study and species effects, respectively.In contrast, $I^2_{total}$ was calculated as the proportion of total effect size variance after accounting for, or removing, total sampling variance.
+$I^2_{study}$ and $I^2_{species}$ are defined as the proportion of effect size variance over total variance as a result of between study and species effects, respectively.
+In contrast, $I^2_{total}$ was calculated as the proportion of total effect size variance after accounting for, or removing, total sampling variance.
 
 We explored drivers of effect size heterogeneity using multi-level meta-regression (MLMR) models.
-Our models included fixed effects (i.e., moderators) that we *a priori* predicted would impact female fitness.
-More specifically, we predicted that the intensity of sexual selection and sexual conflict would affect how much harm males did to females.
+Our models included fixed effects (i.e., moderators) that we *a priori* predicted would impact female fitness or variance in female fitness.
+More specifically, we predicted that the intensity of sexual selection and sexual conflict would affect how much harm males did to females (mean fitness only).
 To test these predictions, we included an index of sexual size dimorphism (SSD), which involved taking the log transformed ratio between male body size to female body size for the species (i.e.,  $log \left( \frac{Male_{body size}}{Female_{bodysize}} \right)$, hereafter referred to as SSD).
@@
 We also accounted for the possibility that SSD might vary depending on the specific harm type and sperm competition intensity (i.e., interaction between SSD and Harm type and Sperm competition intensity).
+We fit models with all of the above moderators for SMDH, but only included the harm type moderator in lnCVR models because we had no clear *a priori* predictions about how variance in female fitness should be affected by SSD and sperm competition intensity.
 We evaluated support for interactions by comparing a model including the interaction to a model without it, comparing $AIC_{c}$ between the two models.
@@
 ```{r funnel, fig.height=7.62500, fig.width=14.90278, fig.cap="A) Funnel plot of effect size as a function of precision (i.e., inverse of sampling standard error).
-B) orchaRd plot of the overall meta-analytic mean efect size, 95% confidnece intervals (thick black bars) and 95% prediction intervals (whiskers)"}
+B) orchaRd plot of the overall meta-analytic mean SMDH.
+C) orchard plot of overall meta-analytic mean for lnCVR.
+In B & C the mean is presented with 95% confidence intervals (thick black bars) and 95% prediction intervals (whiskers)."}
 p1 <- ggplot(data, aes(x = SMDH, y = 1 / sqrt(v_SMDH), xmin = -6, xmax = 6)) +
@@
 Removing this effect resulted in no significant difference between harm type categories.
-
 Harm type did not impact the overall variance in female fitness between control and treatment groups ($F_{2,140}$ = `r model1_lnCVR_harm$QM`, p = `r model1_lnCVR_harm$QMp` - Figure \@ref(fig:maleharm)).
@@
 The lnCVR effect size does have limitations which are not always upheld in practice [@nakagawa2015meta].
-As such, we tested whether these assumptions impacted our inferences by re-running analyses using the log Standard Deviation (lnSD) as our effect size while controlling for log Mean (lnX) using a multilevel meta-regression model using *metafor* (version `r utils::packageVersion("metafor")`) that included lnX along with a two level categorical predictor for treatment (Control vs Treatment) as fixed effects to both control for mean-variance relationship and estimate the effect contrast between control and treatment groups.
+As such, we tested whether these assumptions impacted our inferences by re-running analyses using the log Standard Deviation (lnSD) as our effect size while controlling for log Mean (lnX) using a multilevel meta-regression model using *metafor* (version `r utils::packageVersion("metafor")`) that included lnX along with a two-level categorical predictor for treatment (Control vs Treatment) as fixed effects to both control for mean-variance relationship and estimate the effect contrast between control and treatment groups.
 The effect contrast should approximate lnCVR if assumptions are upheld.

### 2022-10-15 ms.Rmd
Updated ggsave width and height
Added fix axis text and legend text adjustments. Funnelled through all figures. Printed out Supp fig.

@@
 ggsave(plot = p4, filename = "fig1.png", width = 12, height= 5, path = "./output/figs", units = "in", device="png", dpi = 600)
+ggsave(plot = p4, filename = "fig1.pdf", path = "./output/figs", height = 7, width = 10, device = "pdf")
+
 ```
@@
 
+axis_size <- theme(axis.title = element_text(size = 20), 
+                    axis.text = element_text(size = 14),
+                   legend.text = element_text(size = 14),
+                   legend.title = element_text(size = 14))
+
 harm_plot <- ggplot(data, aes(x = Harm_type, y = SMDH)) + 
@@
               annotate('text', x = (seq(1, 3, 1)), y = 6.45, 
-                       label= paste0("italic(n)==", robust_model1.5_2_PI$n), parse = TRUE, size = 3.5) +     
+                       label= paste0("italic(n)==", robust_model1.5_2_PI$n), parse = TRUE, size = 5) +     
               annotate('text', x = (seq(1, 3, 1)), y = 6.15, 
-                       label= paste0("italic(k)==", robust_model1.5_2_PI$nstudy), parse = TRUE, size = 3.5) +     
+                       label= paste0("italic(k)==", robust_model1.5_2_PI$nstudy), parse = TRUE, size = 5) +     
         	  	# 95 %CI: branches
@@
               #geom_segment(aes(x = 2, y = -1, xend = 3, yend = -1), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both"))
-              annotate('text', x = 1 + ((2-1) / 2), y = 5, label = TeX(contrast1), size = 4) + 
-              annotate('text', x = 1 + ((3-1) / 2), y = 5.7, label = TeX(contrast2), size = 4) 
+              annotate('text', x = 1 + ((2-1) / 2), y = 5, label = TeX(contrast1), size = 5) + 
+              annotate('text', x = 1 + ((3-1) / 2), y = 5.7, label = TeX(contrast2), size = 5) +
+              axis_size
               #annotate('text', x = 2 + ((2-1) / 2), y = -1, label = TeX(contrast3), size = 2.5)
@@
               annotate('text', x = (seq(1, 3, 1)), y = 2, 
-                       label= paste0("italic(n)==", lncvr_results$n), parse = TRUE, size = 3.5) +     
+                       label= paste0("italic(n)==", lncvr_results$n), parse = TRUE, size = 5) +     
               annotate('text', x = (seq(1, 3, 1)), y = 1.8, 
-                       label= paste0("italic(k)==", lncvr_results$nstudy), parse = TRUE, size = 3.5) +     
+                       label= paste0("italic(k)==", lncvr_results$nstudy), parse = TRUE, size = 5) +     
         	  	# 95 %CI: branches
@@
               #geom_segment(aes(x = 2, y = -1, xend = 3, yend = -1), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both"))
-              annotate('text', x = 1 + ((2-1) / 2), y = 1.1, label = TeX(contrast1v), size = 4) + 
-              annotate('text', x = 1 + ((3-1) / 2), y = 1.4, label = TeX(contrast2v), size = 4)
+              annotate('text', x = 1 + ((2-1) / 2), y = 1.1, label = TeX(contrast1v), size = 5) + 
+              annotate('text', x = 1 + ((3-1) / 2), y = 1.4, label = TeX(contrast2v), size = 5) +
+              axis_size
 
-plot <- (harm_plot + harm_plotvar) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+plot <- (harm_plot + harm_plotvar) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 24))
 
-ggsave(plot = plot, filename = "fig2.png", path = "./output/figs", height = 7.416667, width = 13.805556, device = "png", dpi = 600)
+ggsave(plot = plot, filename = "fig2.png", path = "./output/figs", height = 7.4, width = 20.8, device = "png", dpi = 600)
+ggsave(plot = plot, filename = "fig2.pdf", path = "./output/figs", height = 7, width = 10, device = "pdf")
 plot
@@
   annotate('text', x = -0.4, y = 3.9, label = TeX(contrast3bottom2, italic = TRUE), size = 5) +
-  geom_abline(intercept = robust_model1.3_nonZ$beta[1], slope = robust_model1.3_nonZ$beta[2]) # Note using model1.3 for plotting because this is marginalised across Harm_type.
+  geom_abline(intercept = robust_model1.3_nonZ$beta[1], slope = robust_model1.3_nonZ$beta[2]) + axis_size# Note using model1.3 for plotting because this is marginalised across Harm_type.
 
 ggsave(plot = p3, filename = "fig3.png", path = "./output/figs", height = 7, width = 10, device = "png", dpi = 600)
+ggsave(plot = p3, filename = "fig3.pdf", path = "./output/figs", height = 7, width = 10, device = "pdf")
 p3
@@
               annotate('text', x = (seq(1, 2, 1)), y = 6, 
-                       label= paste0("italic(n)==", robust_model1.7_PI$n[1:2]), parse = TRUE, size = 3.5) +     
+                       label= paste0("italic(n)==", robust_model1.7_PI$n[1:2]), parse = TRUE, size = 5) +     
               annotate('text', x = (seq(1, 2, 1)), y = 5.7, 
-                       label= paste0("italic(k)==", robust_model1.7_PI$nstdy[1:2]), parse = TRUE, size = 3.5) +     
+                       label= paste0("italic(k)==", robust_model1.7_PI$nstdy[1:2]), parse = TRUE, size = 5) +     
         	  	# 95 %CI: branches
@@
               geom_segment(aes(x = 1, y = 5.35, xend = 2, yend = 5.35), arrow = arrow(length = unit(0.1, "cm"), angle = 90, end = "both")) + 
-  annotate('text', x = 1.5, y = 5, label = TeX(contrast_sperm), size = 3) + 
-    annotate('text', x = 1.5, y = 4.6, label = TeX(contrast_sperm2), size = 3) + 
-    annotate('text', x = 1.5, y = 4.2, label = TeX(contrast_sperm3), size = 3)
+  annotate('text', x = 1.5, y = 5, label = TeX(contrast_sperm), size = 5) + 
+    annotate('text', x = 1.5, y = 4.6, label = TeX(contrast_sperm2), size = 5) + 
+    annotate('text', x = 1.5, y = 4.2, label = TeX(contrast_sperm3), size = 5) + axis_size
 
 ggsave(plot = sperm_plot, filename = "fig4.png", path = "./output/figs", height = 7, width = 10, device = "png", dpi = 600)
+ggsave(plot = sperm_plot, filename = "fig4.pdf", path = "./output/figs", height = 7, width = 10, device = "pdf")
 sperm_plot
@@
       geom_abline() + 
-      labs(x = "log Mean", y = "log SD") + theme_bw()
+      labs(x = "log Mean", y = "log SD") + theme_bw() + axis_size
 
@@
       geom_abline() + 
-      labs(x = "Mean", y = "SD") + theme_bw()
+      labs(x = "Mean", y = "SD") + theme_bw() +  axis_size
 
-(p1_1 | p2_2) + plot_annotation(tag_levels = "A", tag_suffix = ")")
+supp_plot <- (p1_1 | p2_2) + plot_annotation(tag_levels = "A", tag_suffix = ")") & theme(plot.tag = element_text(size = 24))
+ggsave(plot = supp_plot , filename = "figS1.png", path = "./output/figs", height = 7, width = 10, device = "png", dpi = 600)
+ggsave(plot = supp_plot, filename = "figS1.pdf", path = "./output/figs", height = 7, width = 10, device = "pdf")
 ```

### 2022-10-15 ms.Rmd
Fixed a few small size issues and re-export figs

@@
 ggsave(plot = p4, filename = "fig1.png", width = 12, height= 5, path = "./output/figs", units = "in", device="png", dpi = 600)
-ggsave(plot = p4, filename = "fig1.pdf", path = "./output/figs", height = 7, width = 10, device = "pdf")
+ggsave(plot = p4, filename = "fig1.pdf", path = "./output/figs", height = 5, width = 12, device = "pdf")
 
@@
 ggsave(plot = plot, filename = "fig2.png", path = "./output/figs", height = 7.4, width = 20.8, device = "png", dpi = 600)
-ggsave(plot = plot, filename = "fig2.pdf", path = "./output/figs", height = 7, width = 10, device = "pdf")
+ggsave(plot = plot, filename = "fig2.pdf", path = "./output/figs", height = 7.4, width = 20.8, device = "pdf")
 plot

### 2022-10-15 ms.Rmd
Trying to see if we can get 95% ci on fig

@@
   annotate('text', x = -0.4, y = 3.9, label = TeX(contrast3bottom2, italic = TRUE), size = 5) +
+  #geom_smooth(aes(x = SSD_lnRR, y = robust_model1.3_nonZ$ci.lb[1]), method =  "lm", formula = y~x,se = FALSE,lty = "dashed") +
+  #geom_smooth(aes(x = SSD_lnRR, y = robust_model1.3_nonZ$ci.ub[1]), method =  "lm", formula = y~x,se = FALSE, lty ="dashed")
+  #geom_smooth(aes(x = SSD_lnRR, y = robust_model1.3_nonZ$beta[1] + robust_model1.3_nonZ$beta[2]*SSD_lnRR), method =  "lm", formula = y~x, se = FALSE)
   geom_abline(intercept = robust_model1.3_nonZ$beta[1], slope = robust_model1.3_nonZ$beta[2]) + axis_size# Note using model1.3 for plotting because this is marginalised across Harm_type.

### 2022-10-18 ms.Rmd
Trying to sort out CI plots
Finally figured out pred. By default it doesn't require the intercept to be specified in the newmods argument. So, you can ignore this when making design matrix

--- 2022-10-15 ms.Rmd
@@
 
-p3 = ggplot(data, aes(x = SSD_lnRR, y = SMDH, size = 1/sqrt(v_SMDH), colour = Harm_type)) + 
-    geom_point(alpha = 0.6) + 
+predDat <- data.frame(predict(model1.5_nonZ , newmods = cbind(0, 0, seq(from = min(data$SSD_lnRR, na.rm = T), to = max(data$SSD_lnRR, na.rm = T), length.out = 100)), addx = TRUE))
+
+p3 = ggplot(data, aes(x = SSD_lnRR, y = SMDH)) + 
+    geom_point(aes(size = 1/sqrt(v_SMDH), colour = Harm_type), alpha = 0.6) + 
       theme_classic() + 
@@
   annotate('text', x = -0.4, y = 3.9, label = TeX(contrast3bottom2, italic = TRUE), size = 5) +
-  geom_abline(intercept = robust_model1.3_nonZ$beta[1], slope = robust_model1.3_nonZ$beta[2]) + axis_size# Note using model1.3 for plotting because this is marginalised across Harm_type.
+  geom_smooth(data = predDat, aes(x = X.SSD_lnRR , y = ci.ub), method =  "lm", formula = y~x,se = FALSE,lty = "dashed", color = "black") +
+  geom_smooth(data = predDat, aes(x = X.SSD_lnRR , y = ci.lb), method =  "lm", formula = y~x,se = FALSE, lty ="dashed", color = "black") +
+  geom_smooth(data = predDat, aes(x = X.SSD_lnRR , y = pred), method =  "lm", formula = y~x, se = FALSE, color = "black")
+  #geom_abline(intercept = robust_model1.3_nonZ$beta[1], slope = robust_model1.3_nonZ$beta[2]) + axis_size# Note using model1.3 for plotting because this is marginalised across Harm_type.
 
